<Game> *beep, beep* 
<Geo> {13}{EC}! 
It's the Satella Police! 
1This is a message for all active members of the Satella Police. 
The out of control Wizards have caused a great deal of damage to Electopia. 
All out of control Wizards must be stopped in order to prevent further damage! 
<Geo> It really is a country-wide incident! 
<Mega> Nice! The more bad guys, the more butt we get to kick! 
1We have confirmed three areas of insurrection within <Spica.Mall>. 
<Geo> Three areas!? We better get moving! 
<Mega> Weird... 
<Geo> What is it, Mega? 
<Mega> It looks like you've given up on always whining about how 
you don't like battling and how you don't want to stand out! 
Have you finally realized how fun battling is!? 
<Geo> No, that's not it. 
I still don't like battling, and I don't want to stand out. 
<Mega> So what is it then? 
<Geo> I don't really understand it completely, myself... 
But when I see Ace doing what he does, it makes me 
feel like I need to be doing the same thing. 
He's sacrificing his body, and risking his life, so that 
he can fight for everyone's peace and safety. 
And he fights to protect the people that he loves. 
I want to protect the people that I love, too! 
And I'm willing to fight, if that's what it takes! 
<Mega> {13}{EC}... 
Humans really are complicated creatures, aren't they? 
You have people in this world who want to protect 
the world, but then there are others in this world who just want to see it burn. 
I just get so angry when I think about the people who want to ruin everything! 
We are totally going to kick their sorry butts! 
<Geo> Haha! You never change, Mega! 
<Mega> {13}{EC}??? 
I-I guess. 
I guess it's hard for someone who's awesome to stop being awesome! 
<Geo> Haha, I suppose you're right! 
<Geo> ...Alright! It's time to go stop those crazy Wizards! 
<Mega> I'm game! 
