0Everyone is here. 
Whenever you are ready, Chief. 
4Then we'll begin immediately. 
Let's hear from the research team first. 
Aaron Boreal has some findings to report. 
<Mr.Boreal> We've come upon some new discoveries regarding Crimson. 
Even though Crimson is a body of crystallized Noise, 
no Noise is released from Crimson whatsoever. 
Which means that Crimson has a Noise absorbing nature. 
<Ace> It absorbs Noise... 
0That means that it could be useful to us, right? 
<Mr.Boreal> Exactly... 
It could quite well prove to be a beneficial item for us. 
However, if Dealer were to make use of it, they could 
easily turn it into a terrifying weapon. 
{12}{E2}<(Queen)Tia> {01}{00} 
<Mr.Boreal> When Crimson reaches capacity for the amount of Noise that it can hold... 
It emits a huge quantity of dense Noise. 
The amount of Noise that is emitted is actually dozens 
of times the amount that was absorbed. 
The reason that Meteor G is being pulled toward Earth may be the fact that the 
Noise level has been on the rise due to Crimson emitting so much Noise. 
<Mega> Hmm... Crimson kind of seems like a bomb, doesn't it? 
I guess... More like a Noise bomb, huh? 
<Mr.Boreal> There are other ways to use Crimson than as a bomb, Omega-Xis. 
I believe that Crimson was used as energy to make 
Noise clusters, like the ones you saw at your school. 
If applied correctly, we could freely control the output of Noise with Crimson. 
<Ace> {13}{EC}...! 
<Geo-2> Control... Noise? 
3To think that Crimson would have such uses... 
<Mr.Boreal> {13}{EC}... 
<Dr.Goodall> ...Heehee! 
Go on, Aaron. You can tell us. 
You look like you've found something else out, too. 
<Mr.Boreal> What!?{15}{E1} Oh... That's true, Doctor... 
Upon researching exactly how the Noise that's on the planet is attracting Meteor 
G, I found that there is "strange Noise" being emitted from Meteor G itself. 
4What kind of Noise could that be exactly? 
<Mr.Boreal> I'm sorry, but I haven't discovered that yet... 
However... 
When I first noticed the strange Noise, it was as if I heard Meteor G's "voice". 
Whether it is trying to say something... Or call someone... Or answer someone... 
I just don't know. 
<Dr.Goodall> Heehee! That could prove to be a very interesting lead! 
We must look into that voice. 
Would you be so kind as to let this old lady help you out, Aaron? 
<Mr.Boreal> Of course! 
Well, that concludes my report. 
<Ace> {13}{EC}... 
4Thank you, Boreal. 
Next up, we will discuss the incidents of out of control Wizards around the country. 
0Yes, sir! 
It is believed that the cause of the incidents was the high Noise levels in those areas. 
We still have not discovered any Noise Cards, program viruses, or anything else 
that would place Dealer as the culprit. 
<Ace> ...Still... It has to be their doing. 
Even without evidence it's clear. 
There's no one else that would or could pull off such a large-scale event. 
0Ace... 
1B-But... 
How could they cause so many Wizards at once to- 
<Ace> With Crimson. 
They must have found out that Noise can be controlled with Crimson. 
They just figured it out way before we did. 
4And now they've already learned how to use it as a weapon. 
<Ace> The situation could get even worse... 
King doesn't just want to control ordinary Noise... 
He wants to control a gigantic cluster of Noise... 
0A gigantic cluster of it!? W-What do you mean!? 
<Ace> Isn't it fairly obvious? 
I mean that ominous ball in the sky that's causing people to lose sleep at night. 
...The red star that is falling from the heavens upon us. 
<Geo-2> {13}{EC}...!! 
<Geo-2> I-I get it!! 
The gigantic Noise cluster that Dealer wants to control is... 
<Geo-2> Meteor G!! 
4{13}{EC}!? 
0W-What!? 
2Is that... Could that really be true...!? 
<Acid> Actually, Dealer has already taken some control of Meteor G. 
<Ace> Their whole reasoning behind making Wizards go out of 
control is to collect the Crimson that is emitted. 
0W-Wait a second...! 
When we stop an out of control Wizard, Crimson is released... 
And then Dealer collects the Crimson. 
So then why are we risking our lives across the country to fight the Wizards!? 
<Ace> It looks like... 
...It's to help Dealer out. 
1Th-That can't be...! 
<Ace> Yet, if we don't stop the out of control Wizards, then 
many people will be hurt or worse. 
We are doing the right thing. 
*sigh* ...King's plan is working just as he expected it to. 
<Game> ...Ho ho ho ho! 
<Ace> {13}{EC}!! 
0W-Who is that!? 
4What's going on!? 
{98}{00}We have an emergency! 
{98}{00}Something has infiltrated the WAZA computer network! 
4What...!? 
<Game> Ho ho ho... 
It is nice to meet you...{15}{E1} Well... 
I mean everyone except Ace! 
<Ace> {13}{EC}!! 
<Ace> {15}{E1}...King!! 
<Geo> King!? 
{13}{EC}(That's the leader of Dealer!) 
{12}{E2}{15}{00}{01}{00} 
<Mr.King-2> Hello, Ace...{15}{E1} And everyone at WAZA! 
I figured I would drop you a line, as it appears that you 
are very close to figuring out what Dealer is up to! 
...How is everyone doing, by the way? 
2It's an air display! 
He hacked the computer network so that he could transmit to us! 
0Y-You... Are you having fun!? 
<Mr.King-2> This is no game to me at all, good sir! 
In fact, I have never been more serious in my life! 
If I was playing around... 
I would not have been able to gain control of Meteor G! 
<Dr.Goodall> {13}{EC}...! 
<Ace> So you're...! 
<Mr.King-2> Listen well, ladies and gentlemen! 
Dealer has taken complete control of Meteor G! 
And we are going to use its tremendous power to rule the planet! 
However... 
In order to do so, I require all of your assistance. 
4Are you insane!? Why would we help you!? 
<Mr.King-2> You will help me. 
You do not have any other choice, really! 
{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1}You do understand why you must, right? 
{13}{E2}{01}{00} 
4You... mean..!? 
{98}{00}...!! 
There's a distress call from the <Stage.Evento> at <Studi.WBG>! 
{12}{E2}<Zack> {00}{00} 
{98}{00}Out of control Wizards have been spotted there! 
Th-This... This is the biggest group of them we've seen yet!! 
<Mr.King-2> So, everyone! 
Go out and stop all of those Wizards! 
And... 
Make more Crimson for us! 
Ho ho ho ho ho!! 
4I-I...!! 
<Ace> It's time to get to work, Mega Man. 
<Geo> What...!? 
<Geo> B-But... 
<Mega> ...Are you serious? 
You're really going to walk willingly into their trap!? 
<Ace> There's no point in us debating what we should do... 
It's already been decided for us, hasn't it? 
You do understand don't you, Geo? 
<Geo> {13}{EC}...! 
<Ace> We'll worry about what to do next, later. 
We'll figure something out. 
After all, they don't have their most powerful card anymore. 
<Geo> Their most powerful card? 
<Ace> The Ace Card...{15}{E1} I will never let them get their hands on it again... 
Letting them gather all the cards is not an option. 
<Geo> Ace... 
<Ace> Come on. 
We've got to stop those out of control Wizards! 
