<Ace> They're really causing a fuss this time, eh? 
<Ace> So... Geo. 
Are you ready for this? 
<Geo-2> Never been more ready! 
{0A}{E1}{62}{02} 
<Ace> Then let's cause a bit of a fuss ourselves, shall we? 
Transcode 001! 
<Geo> Transcode! Mega Man! 
<Acid.Ace> ...Try not to fall behind, Mega Man! 
<Megaman> Don't overdo it, yourself, old man! 
<Acid.Ace> Haha. Not bad, not bad. 
Let's do this! 
<Acid.Ace> Phew... 
<Megaman> It looks like we stopped them. 
<Megaman> A-Ace... All that Crimson... 
<Acid.Ace> There's nothing we can do. 
Darn it... 
<Megaman> ...Huh? 
<Megaman> Usually, the Crimson flies away, but... 
<Acid> Ace! Mega Man! Up above! 
<Acid.Ace> {13}{EC}!! 
<Megaman> J-Joker!! 
<Joker> {13}{EC}... 
<Megaman> Whoa...! 
<Acid.Ace> {13}{EC}... 
<Megaman> Ace! 
<Acid.Ace> Thanks for coming all the way to see me... 
You saved me the trouble of having to find you. 
<Joker> Hah...! 
<Joker> What were you planning on doing once you found me? 
<Acid.Ace> Stopping you, of course. 
<Joker> ...I see. 
<Acid.Ace> You're dangerous. 
And on top of that...{15}{E1} You're a member of Dealer. 
You disgust me. 
<Joker> {13}{EC}... 
<Acid.Ace> That's why I'm going to stop you for good! 
<Acid.Ace> {13}{EC}!? 
<Joker> Hah! 
Is this the extent of your power? 
<Joker> Apparently it is... What a pity. 
<Acid.Ace> {13}{EC}...!? 
What are you doing? 
<Acid> Ungh{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1}!! 
A{16}{E1}-Ace...!! 
<Acid.Ace> I-I can't move! 
Tell me, Acid!!{15}{E1} What's going on!? 
<Acid> I... don't... know. 
A...c...e{16}{E1} It... hurts{15}{E1}.{15}{E1}.{15}{E1}.{15}{E1} 
<Acid.Ace> Acid!! 
...Joker... What have you done!? 
<Joker> ...Ha! 
It is not a matter of what I have done. 
I have simply called Acid to me. 
And...{15}{E1} he is simply responding to my call. 
There's nothing more to it. 
We are of the same "shooting star power", after all, right? 
<Acid.Ace> {13}{EC}...! 
You... You knew!? 
<Joker> Of course. 
Since we are linked together, it would be impossible for me not to know! 
<Acid> A{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} ce{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
<Acid.Ace> Stop this, Joker!! 
If you keep this up, Acid will... 
<Joker> {13}{EC}... 
I have{16}{E1}... no problem with that. 
<Joker> The Noise Level has reached 200%! 
{15}{E1}.{15}{E1}.{15}{E1}.{15}{E1}Finalize!! 
<Acid> Ungh... 
{AE}{00}Aaaaaargh! 
<Ace> Ac...{16}{E1}id... 
{13}{EC}...! 
{13}{EC}... 
<Joker> Re-awaken, Acid!! 
Re-awaken as your true self!! 
Prove our existence to the world!! 
{AD}{00}{13}{EC}{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
<Joker> Hah... 
Hah hah hah! 
{A0}{E1}{04}{00}<(Queen)Tia> 
<Joker> Hah hah hah!! 
How are you feeling, Acid? Wonderful, I bet! 
Go on, do as you please. 
{AD}{00}{13}{EC}... 
<Joker> Bah! 
{13}{EC}(Something is preventing  him from fully Finalizing.) 
{13}{EC}(Darn Satella Police...  They must have altered  Acid, so he can't Finalize!!) 
Listen to me, Acid! It is that destructive urge, 
and that alone, which confirms our existence! 
Never forget that. 
And it is that red shooting star that is our bond... 
We are one... 
<Megaman> Ace!! 
<Megaman> A... Ace!? 
{AD}{00}{13}{EC}{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
<Mega> Hey... 
This really, really, really doesn't look good. 
<Megaman> What's wrong, Ace!? 
Where's Joker? 
And{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} Why do you look different...? 
{AD}{00}{13}{EC}... 
<Megaman> Ace!! 
Snap out of it, Ace!! 
<Mega> I don't think he understands anything you're saying... 
You better be ready, kid! 
<Megaman> No way! 
Are you saying that we're going to have to fight Ace!? 
<Mega> Do you see any other option!? 
Can you honestly tell me that you can watch him be 
like this, and not think that you should stop him!? 
<Megaman> {13}{EC}!! 
<Mega> He's completely out of control! 
I don't have a clue what happened, but... 
But we can't let him go on like this!! 
Let's beat him up, and knock some sense into him!! 
<Megaman> Mega... 
<Megaman> {14}{E1}.{14}{E1}.{14}{E1}.{14}{E1}You're right, Mega... 
There's no way that Ace and Acid would ever want to be like this... 
Who knows how bad they must be suffering... 
And the only people that can help them...{15}{E1} Are us! 
<Mega> That's my boy! 
But stay frosty, kid! You know they're pretty tough! 
<Megaman> Yeah...! 
{13}{EC}(But...) 
{13}{EC}(Even if I fight them  with everything I've got...) 
{13}{EC}(I don't know if  I can beat them...) 
{13}{EC}(But Ace said that  he can't stay EM Wave  Changed for very long...) 
{13}{EC}(If I can just hold out  and waste some time...) 
<Mega> {13}{EC}!! 
This is it, kid! 
