<Geo> Dr. Goodall... 
How are Ace and Acid doing? 
<Dr.Goodall> {13}{EC}... 
As far as Acid goes... 
I've reinstalled his main program, and he is in the middle of restarting, now. 
Arthur is... 
Not doing well. 
Deep sections of his consciousness were torn to 
pieces by Acid when he was out of control... 
And also staying EM Wave Changed for so long pushed 
him to his physical limits, and strained him mentally. 
<Dr.Goodall> I'm surprised that he even made it back here alive. 
<Geo> {13}{EC}... 
Umm... Dr. Goodall... 
What happened to Acid? 
Normally Acid would never hurt Ace... 
<Dr.Goodall> {13}{EC}... 
That is true. 
I suppose that it's best for you to know. 
<Ace> Dr. Goodall... 
It won't make any difference whether he knows or not. 
<Dr.Goodall> {13}{EC}! 
<Dr.Goodall> ...Arthur! 
<Geo> Ace! 
Are you alright!? 
<Ace> ...About as "alright" as I look. 
<Dr.Goodall> What... 
What are you doing out of bed!? 
{12}{E2}!{01}{00} 
<Dr.Goodall> You shouldn't be up and about yet. 
Don't push yourself too hard so soon. 
<Ace> Doc... I'm sorry. 
But, I can't just sit around and do nothing. 
Even now, Dealer is busy enacting their plans... 
At this rate, we will lose the world to them. 
I'll do anything it takes to stop that from happening! 
<Geo> A-Ace!! 
<Ace> How does this sound, Geo... 
We're going to go find Dealer's base... 
And then bring them down with our own hands! 
We'll make...! 
The world...! 
And the future...! Safe... again...! 
<Dr.Goodall> Arthur!! 
<Geo> Ace!! 
4If we continue to keep only reacting to Dealer's 
actions, we will never be successful in stopping them. 
So our next mission is... 
{12}{E2}{11}{00}{01}{00} 
4To directly attack Dealer! 
0{13}{EC}!! 
1{13}{EC}!! 
4All WAZA staff will now focus on locating Dealer's base! 
We will need every lead and every scrap of information to locate them! 
Leave no stone unturned! 
2Yes, sir! 
3Yes, sir! 
4All Satella Police officers will perform investigations at all 
areas that have had recent Dealer related incidents! 
Dealer's leader, as well as Joker have appeared at some of these areas. 
There could be some traces of Dealer at any of these incident sites. 
We're all counting on you! 
0Yes, sir! 
1Yes, sir! 
4...{16}{E1}Geo Stelar! 
<Geo-2> Y-Yes, sir!! 
4The Commandos... 
You will remain on reserve duty until Team leader Ace has recovered. 
<Geo-2> ...! 
Wait just a second, Chief! 
Please at least let me help with something! 
4G-Geo... 
<Geo-2> As Ace pointed out earlier... Dealer is still going ahead with their plans. 
We don't have a lot of time... 
Dealer is getting closer to their goal of taking over the world... 
Ace said we can't give them that chance! 
S-So... I can't just stand around... 
... 
<Dr.Goodall> Geo? 
Don't you know that reserve duty can be very important, as well? 
4! 
<Geo-2> Dr. Goodall... 
<Dr.Goodall> You've already done so much for us today. 
That's why you have to take it easy for the rest of the day. 
There will be a lot for you to do, tomorrow. 
<Geo-2> Tomorrow!?{15}{E1} So then I actually can help? 
<Dr.Goodall> Of course! 
There are a lot of things that no one else can handle but you! 
Right, Chief? 
4Y-Yes, of course... 
It's just as Dr. Goodall has said, Geo. 
Today you are to go home and get some rest. 
One rests when they can. It's the most vital of duties! 
<Geo> U-Understood! 
Well then, I'll be off for now! 
{A0}{E1}{04}{00}<(Queen)Tia> 
<Geo> Alright, time for some sleep!! 
4...Are we not able to protect the world without sending that young boy into danger? 
<Dr.Goodall> I see things differently. 
4{13}{EC}! 
<Dr.Goodall> Wanting to protect the world has nothing to do with being an adult or a child. 
In fact, children surely want to do so based on more 
pure and innocent beliefs and motives. 
That young boy is doing all he possibly can to protect the planet... 
But I bet he doesn't even realize how much he has already done for all of us. 
4When this is all over, we will have to make sure he does. 
4Now let us begin our part of the plan. 
There are many things that only adults can do, too... 
Isn't that right, Dr. Goodall? 
<Dr.Goodall> You said it. 
