<Game> *beep* 
<Geo> *snoring* 
{13}{EC}... 
*mumbling* 
There's just no way that I can eat all that... 
<Mega> Hey, kid!{15}{E1} Wake up!! 
<Geo-2> Wha!? 
<Geo-2> Wh-Wh-Wh-What is it!? 
Has there been another incident!? 
<Mega> You have a call! 
It's from Dr. Goodall! 
<Geo-2> Oh! OK. 
<Mega> For cryin' out loud... Do I look like an alarm clock Wizard or something? 
Sweet lordie! 
<Geo-2> Good morning, Dr. Goodall. 
<Dr.Goodall> Good morning, Geo. 
Hee hee.{15}{E1} You look like you got some good sleeping in! 
Oh, to be young again... 
I find that the older you get, the earlier you wake up. 
You just can't sleep as much as when you were young. 
You know! 
I used to sleep so much when I was a young girl! 
<Geo-2> Umm...{15}{E1} Umm...{15}{E1} Dr. Goodall... 
<Dr.Goodall> {15}{E1}...Oh, yes indeed. 
That's enough chit-chat, for the time being. 
I'm sorry I had to wake you up, but I have an assignment for you. 
<Geo-2> No problem! What's the assignment? 
<Dr.Goodall> I want you to investigate the following three areas. 
<Echo.Ridge> Elementary... 
<Spica.Mall>... 
and <Studi.WBG>... 
You should be able to find Noise Waves there. 
<Geo-2> Noise Waves!? 
<Dr.Goodall> Yes. 
It seems that Dealer uses Noise Waves to travel to and from different places. 
If you went and talked to the denizens of the Noise Waves... 
You might be able to track that child... 
Joker... 
Tracking him should lead you to Dealer's base. 
<Mega> So... You're telling us to go mine for data! 
<Dr.Goodall> That's right, Meggers! 
You are such a smart little guy, aren't you? 
<Mega> Bah! You'd have to be pretty dumb to not understand what you meant! 
<Geo> {13}{EC}(That reminds me. We {13}{EC} watched that wave crime {13}{EC} investigation show, recently.) 
{13}{EC}(I think it's called "WRI:  {13}{EC} Wave Road Investigation"...) 
{13}{EC}(Mega seemed to {13}{EC} be really into it.) 
<Dr.Goodall> Hee hee. Silly Meggers. 
Well now, let's go over what happened yesterday. 
<Dr.Goodall> The first incident was at Geo's school. 
<Geo-2> Wizards went out of control and terrorized the front entrance area. 
<Mega> That was really strange, wasn't it!? 
<Dr.Goodall> Following that, three out of control Wizards attacked <Spica.Mall>. 
The entrances to Noise Waves are in the Real World, 
so make sure to check out all suspicious places in the three areas for them. 
<Geo-2> The final area to have an incident was <Studi.WBG>. 
That's where Joker showed up! 
<Dr.Goodall> The Noise in that area is a little different, or should I say special... 
You should not go there until after you've checked 
out Echo Ridge Elementary and <Spica.Mall>. 
<Mega> OK, we got it! You can count on us to catch those bad guys! 
<Dr.Goodall> Hee hee! I'm counting on you, Meggers. 
Well then, Geo. 
Since Noise Waves are very dangerous areas, this is something only you can do... 
Do your best, and make sure to stay safe, OK? 
<Geo> Yes, ma'am! Over and out! 
<Geo> Alright, let's go investigate! 
<Mega> Data mining! It's called data mining! 
Hehehe. I'm going to be the best Wizard detective ever! 
You're going to let me help out at the scene, right? 
If you need any help, just talk to me! 
Got it, Detective Stelar!? 
<Geo> Detective Stelar? 
Hmm, that doesn't sound half bad... 
<Mega> It's time, Detective Stelar! The scene of the crime is calling us!! 
