<Geo-2> We finally got to the entrance! 
<Mega> Hehe, I'm itchin' for a fight! 
Let's bust in there, and go buck wild on those jerks!! 
<Ace> Didn't I tell you not to act up like that? 
<Geo-2> {13}{EC}!! 
<Geo-2> Ace!? 
<Mega> Acid's here... Super... 
<Ace> Well done on finding Dealer's base for us, Geo. 
I knew you could do it! 
Well actually... 
It was Dr. Goodall and the Chief that said you could. 
<Geo-2> Ace, are you feeling up to this? 
<Ace> 100%! 
There's no need to worry. I even have Dr. Goodall's approval. 
<Acid> Omega-Xis... 
The fate of the planet will be decided by this mission. 
Absolutely zero non-team approved actions will be tolerated. 
<Mega> Oh, give me a break! Just keep your mouth shut! 
I don't need a lecture from some reject Wizard who can't even stop yapping! 
<Acid> ... 
I'm not trying to lecture you.{15}{E1} But... you can be impulsive. 
<Mega> I'll show you impulsive! 
<Sonia> Geeeo!! 
<Geo-2> Who... 
<Sonia> I'm here to help, too... 
Teehee! 
<Geo-2> Sonia! 
<Ace> Harp Note is equally as important of an ally as Mega Man is. 
She too is vital to this mission. 
<Sonia> Yep! 
We can do this, Geo! 
<Lyra> Let's do our best to work together, as well. 
{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1}Meggers. *giggles* 
<Mega> Grr! Why you...! 
J-Just don't slow me down! 
<Ace> So, let's go over everything... 
<Ace> Everyone here is a member of the Team, "Satella Police Commandos"... 
And all of us have gathered here to end Dealer's plan for world domination. 
We are the most skilled and strongest of all the Satella Police officers. 
So if we fail, Earth may not have another chance to escape the wrath of Dealer. 
But from here on out, we will not even acknowledge that possibility. 
Because our new Purpose is to... 
Crush Dealer! 
0Yes, sir! 
1Yes, sir! 
<Game> Geo's Purpose has changed! 
<Ace> Geo... 
Are you ready to get to work, right away? 
<Geo-2> Of course! 
<Ace> That horrid looking door behind us is locked tight. 
It's next to impossible to unlock it from the Real World. 
So... 
<Geo-2> That means it's time for Mega Man! 
<Ace> Precisely. 
Would you please find the control panel located in 
the Cyber Core, and then unlock the door? 
<Acid> And please do so as quickly as you can. 
We don't want to be loitering around here for very long. 
<Mega> Who do you think you are!? You think you can just boss him around like that!? 
<Geo-2> U{15}{E1}-Understood, Acid! 
We'll be back ASAP! 
