<Geo-2> What's that...!? 
<Ace> That's a pretty impressive piece of equipment, eh? 
Let's check it out. 
But be careful, it doesn't have a good vibe to it. 
<Ace> A "Crimson machine"? 
<Acid> It takes the huge amount of Noise that is released from 
Crimson, then condenses it and stores it in a tank. 
<Ace> So all of those tanks... They are all full of Noise? 
<Acid> That's what the data says. 
<Ace> What could they possibly be used for? 
Ah, well I guess that's a silly question. 
Clearly, they're being used to take control of Meteor G. 
I didn't want to do anything out of the ordinary before King detected us, but... 
Let's destroy them.{15}{E1} It's too dangerous to leave them here. 
<Acid> That is a fine decision, Ace. 
The power core of the machine is up above. 
The machine will stop functioning if the power core is destroyed. 
Please attack that area. 
<Ace> OK! 
<Ace> You all heard Acid! 
We're destroying this Crimson machine! 
Everyone, to your positions! 
0Yes, sir! 
1Yes, sir! 
<Ace> Fire! 
0Yes, sir! 
1Yes, sir! 
0...Huh!? 
0No way! It has a defense system!? 
1Oh no! 
1{13}{EC}!! 
{A0}{E1}{04}{00}<(Queen)Tia> 
0Watch out!! 
<Ace> {13}{EC}!! 
<Geo-2> Ugh{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
Wh-What was that? 
<Geo-2> G-Guys!? 
<Sonia> They...{15}{E1} They saved us!! 
<Ace> Geo, Sonia! 
We've got to move them to a safer place! 
<Geo-2> Right! 
<Geo-2> Wake up! 
0The most important thing... Is that you are safe... 
<Geo-2> Thanks to you guys, we are. 
You saved us all! 
Me, Sonia, and Ace! 
0Thank goodness... 
You all possess a power that we never could... 
You three are our last hope... 
We're... counting... on... you... 
{13}{EC}... 
<Geo-2> {13}{EC}(He lost consciousness.) 
<Geo-2> Ace! 
<Ace> Yeah? 
<Geo-2> I'll destroy the Crimson machine! 
Mega Man should have no trouble getting to the top 
and destroying the power core! 
<Ace> ...I see. 
OK, but be careful. 
We'll take the others outside of the base. 
<Ace> Can you help me out, Sonia? 
<Sonia> Yeah, of course. 
<Ace> Then let's get these people to safety. 
<Mega> It's going to be pretty complicated, but... 
We can take the Wave Road to the power core! 
<Geo-2> Let's pulse in and find that power core! 
