<Megaman> {13}{EC}!! 
<Acid.Ace> {14}{E1}.{14}{E1}.{14}{E1}.{14}{E1}Ungh... 
<Megaman> A-Acid Ace!! 
<Acid.Ace> Haha... I'm not looking so great, am I? 
I thought I'd be able to take him out, even in this state... 
But apparently Joker has quite a grip on Acid and I... 
<Megaman> Ace... 
<Joker> Stand up, Acid Ace. 
Give in to your urge to wreak havoc, once again! 
You can hear me, can you not, Acid? 
Do as I say! 
<Megaman> Just shut up already! 
<Joker> {14}{E1}.{14}{E1}.{14}{E1}.{14}{E1}And just what do you plan on doing to stop me? 
<Megaman> Joker!! 
Do you think you can handle me!? 
<Joker> Hah. 
You've got a lot of nerve. 
However, it is not your time to fight. 
Be gone. 
<Megaman> Ace, Acid... 
And even Prez! 
You keep hurting the people who are special to me!! 
You will pay for that!! 
<Joker> You good-for-nothing... 
I was actually expecting a great deal from you... 
But you're just the same as this fool, who acts on the 
whim of his emotions and is willing to sacrifice himself. 
And you will die just like him. 
<Mr.King-2> Ho ho ho! 
It looks like you are having fun, Joker! 
<Joker> Mr. King... 
<Mr.King-2> Why don't you play a little bit longer... 
And you might as well be as wild as you possibly can! 
Joker! 
Show him your true form! 
<Joker> Yes, sir. 
<Mr.King-2> Ho ho ho... This should be a blast! 
Don't you think, Heartless? 
<Heartless> Yes, Mr. King. 
<Mr.King-2> Would you like to place a bet on who will win the battle? 
Ho ho ho ho ho! 
<Joker> By the orders of Mr. King, I must show you my true form. 
<Megaman> Your true form? 
<Joker> ...Hah! 
Hah hah hah!! 
Only a few have seen the power of the red shooting star... 
Using its power is my Purpose! 
It's my reason for existing!! 
<Megaman> What the...!? I can feel his power!! 
<Joker> Wraaaaaar!! 
Finalize!!{16}{E1} Dread Joker!! 
<Dread.Joker> Hah... Hah hah hah...! 
<Megaman> H-He changed!? 
<Mega> That's no EM Wave Change!! 
I...{16}{E1} I don't think that he's a human being! 
<Dread.Joker> Hah hah hah... That is correct... 
The truth is that... 
I am the most powerful Battle Wizard ever created... 
<Megaman> W-Wizard!? 
You're a Wizard...!? 
<Dread.Joker> And this form is the manifestation of the power of the red shooting star... 
Only he who accesses the "Meteor Server" can acquire this ultimate form of power!! 
Are you watching, Acid? Can you hear me, Brother!? 
This is also your true form!! 
<Megaman> What are you saying!? 
Joker... How are you and Acid connected? 
<Dread.Joker> We were both born from the same program. 
The program was designed to create Wizards that can adapt to any level of Noise! 
<Megaman> Adapt to Noise...? 
<Mega> Are you talking about Noise Changing then!? 
<Dread.Joker> Hah hah hah... 
I suppose you could call it that! You have also acquired the same ability! 
However!! 
You are but a low-grade imitation... 
You are only able to draw on but a scarce amount of the Meteor Server's power! 
Pathetic!! Truly pathetic! 
Leave it to a human to be scared of the infinite power that Noise can bring them! 
Mega Man... 
That program that you use is actually something that was stolen from us. 
But it's really just a tiny fragment of its true power! 
<Megaman> I have no clue what... 
<Dread.Joker> While it was you humans who gave us our power... 
Our reason for living... 
You also felt that we were too powerful, and mercilessly stole our power from us! 
<Megaman> !! 
<Dread.Joker> Can you possibly understand!? 
How do you think it feels to have your reason for living taken away from you!? 
But then, Mr. King gave me a new reason to live! 
As Mr. King's Wizard, I have been able to return myself to my original and true form! 
<Mega> Bah!! A reason to live!? 
Even a windbag like you could find that all by yourself! 
<Dread.Joker> What does that mean!? 
<Mega> I'm saying I don't understand all this "given" and "stolen" stuff you keep talking about!! 
Real Wizards don't whine on and on about stuff like that! 
Do you want to be a human or something!? 
<Dread.Joker> ...!! 
Me{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} Become a human{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1}? 
... 
...Heh... 
...Ha... 
Hahaha! 
That's funny{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} Really... That's really funny{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
Me become a human... 
Hah hah hah!! 
{A0}{E1}{04}{00}<(Queen)Tia> 
<Dread.Joker> Hah hah hah hah hah hah!! 
<Mega> What's with this guy? Is he broken? 
{12}{E2}<Solo> {00}{00} 
<Dread.Joker> You think you're funny, don't you!? Hah hah hah!! 
Well then, why don't you use your great power to show me what I truly am!? 
Wizard, human, or something else completely!? 
<Mega> My pleasure! That's a favor I can do. 
As long as you're asking for a can of butt whoopin'! 
<Megaman> Joker!! 
I think you have bigger things to worry about, other than what you are! 
Because what you're doing is ruining billions of lives! 
Including all of the people that are special to me! 
You must be stopped! 
So I'm{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} I'm bringing you down!! 
Wave Battle!{16}{E1} Ride{15}{E1} On!! 
