<Dread.Joker> Hah... 
Hah... Ahhhhhh!! 
<Joker> Argh... Ugh... 
{13}{EC}... 
<Mega> We did it, kid!! 
We brought that jerk down!! 
<Megaman> *huff, huff* 
Y-Yeah...!! 
<Acid.Ace> Ha... Haha! 
<Acid.Ace> You... Defeated Joker...! 
You really are the world's greatest hero! 
<HarpNote> Mega Maaan! 
<HarpNote> Phew! I finally caught up to you! 
<Megaman> Harp Note... 
Acid Ace! 
<HarpNote> The only thing left to do is to stop King! 
<Acid.Ace> It's time for the final push, Mega Man. 
<Megaman> ...Yeah!! 
<Megaman> King! 
<Mr.King-2> Hmph... 
I should have placed my bet on you, after all. 
But who would have thought you would defeat Joker... 
Ho ho ho! 
<Acid.Ace> You haven't changed a bit, King. 
Too bad you won't have the chance to reform! 
Dealer and all its evil doings will end today!! 
<Mr.King-2> Ho ho{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
Ho ho ho ho ho!! 
You are hilarious, Ace! What a superb joke!! 
<Acid.Ace> Give me a...! 
<Mr.King-2> Heartless! 
<Heartless> Yes, sir. 
<Megaman> {13}{EC}!? 
<Mr.King-2> This should be fine here. 
You look like the despicable and worthless little ants that you truly are! 
Ho ho ho ho ho!! 
<Acid.Ace> Why you...!! 
<Megaman> Err... 
<Mega> Hey!! We're not letting him get away, kid! 
<Megaman> I'm with you on that! 
<Game> Wait. 
<Megaman> !? 
<Megaman> J-Jack!? 
<Acid.Ace> Tia...!? 
<Mr.King-2> Oh, how pleasant! 
My children have come home to me! 
<(Queen)Tia> {13}{EC}... 
<Mr.King-2> Would you do your father a favor, and take out these pieces of garbage for me? 
Ho ho ho! Such good children! 
<(Queen)Tia> {13}{EC}... 
<Jack> {13}{EC}... 
...King. 
<Mr.King-2> !? 
<Jack> Why don't you give us all of the Crimson that you've collected? 
It's not like you need it anymore. 
<Mr.King-2> {13}{EC}... 
What are you trying to say, my dear boy? 
<(Queen)Tia> First, you lost Acid. Now Joker has been defeated... 
Dealer is done for... 
We'll take care of everything from here. Just the two of us. 
Does everything make sense, now? 
<Mr.King-2> {14}{E1}.{14}{E1}.{14}{E1}.{14}{E1}You would dare turn your back on the man who raised you? 
<(Queen)Tia> Raised us!? How dare you presume to be our father!! 
<Jack> I'll only say this once... 
We never have, and never will think of you as our father! 
<Mr.King-2> {13}{EC}... 
<Mr.King-2> Ho...! 
Ho ho ho! 
<Mr.King-2> Hoooooo! Ho ho ho ho ho!! 
<(Queen)Tia> {13}{EC}...! 
<Jack> What do you think is so funny!? Jerk... 
<Mr.King-2> You truly are foolish little children! 
You came back here nonchalantly, with your noses pointed high... 
And now, you actually believe that they have me defeated!? 
<Jack> Enough jabber! Spit it out! 
<Mr.King-2> Joker! 
<Joker> {13}{EC}... 
<Megaman> J-Joker...!? 
What are you going to do? 
<Acid.Ace> No way... 
I think he's going to self-destruct!! 
<Megaman> Self-destruct...!? 
<HarpNote> No way!! 
<Mr.King-2> Ho ho ho!! 
That is correct, Ace! 
Joker will soon self-destruct... 
I always have a trump card up my sleeve! 
At least you'll be in the company of friends when you go down!! 
Ho ho ho ho ho!! 
<Joker> Hah! 
What are you going to do, Acid Ace? 
Are you going to let everyone here be deleted? 
<Acid.Ace> {13}{EC}... 
<Megaman> Acid... 
Ace!! 
<(Queen)Tia> Ace...! 
<Acid.Ace> Geo... 
I'm sorry, but there isn't enough time to explain. 
<Megaman> A-Ace...!? 
<Joker> Hah! 
Hah hah hah!! 
That's it, Ace! 
Absorb all of the explosive energy that I am releasing! 
We will be deleted... 
But the lives of your friends may be saved! 
{AD}{00}I can't think of a better way to go! 
<Joker> Hah...! 
That is truly{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} despicable. 
I am impressed by your determination, nonetheless. 
Goodbye, Acid Ace! 
Aaaaaargh...! Raaaaaarrr!! 
{AD}{00}Whoaaaaaagh! 
{AD}{00}Queen... Tia!! 
<(Queen)Tia> {13}{EC}...!? 
<(Queen)Tia> A{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} Ace...!! 
<Ace> Tia... 
The reason I left Dealer and acquired all this power... 
Was so that I could make my wish come true... 
My wish was that one day I could see you smile again. 
That you could be happy again. 
<(Queen)Tia> You... You always were so selfish! 
I never asked that of you... 
All I wanted was for my own wish to come true! 
If you really wanted me to be happy, then you should 
have stayed in Dealer and worked together with us. 
I always believed that you would come back... 
I never stopped believing... 
<Ace> ...I see. 
That might not have been so bad. 
Haha.{16}{E1} If I would have done that, we could have been together! 
<(Queen)Tia> ... 
<Ace> But, we can't change the past now, can we? 
Hah. Regret doesn't make any difference at all! 
<(Queen)Tia> Ace... 
<Ace> Goodbye, Tia. 
{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1}Don't forget to smile and eat lots of chocolate. 
<(Queen)Tia> W-Wait... 
<Ace> ...I... lov... y... 
Tia... ... 
<(Queen)Tia> {13}{EC}!! 
Ace!! 
<Megaman> A{15}{E1}-Aaaaaace!! 
<Mega> Ace{16}{E1}... Aciiid!! 
<Megaman> Ac... 
...!! 
...! 
<Game> ... 
... 
... 
<Mr.King-2> Ho ho ho... 
<Mr.King-2> Very good, Joker! 
And you too, Ace!! 
You've granted me with more Crimson than I know what to do with!! 
You were always such an overly serious and foolish lad! 
How dare you leave my organization and then stand in opposition against me! 
Is that how you repay your father? 
I suppose your deletion is compensation enough for me... 
Ho... Ho ho ho ho ho!! 
<Heartless> {13}{EC}... 
