<Mega> Alright, let's go over how to Wave Battle! We'll start with the bottom screen. 
<Mega> This is the Custom Screen. 
Six cards are randomly selected from the 30 cards 
that are in your Folder, and then displayed here. 
Then you select cards to use from those six. 
Using a card won't make it disappear forever, so don't be scared to use them! 
However, you can't just use all of the cards on the Custom Screen. 
There are rules that decide which cards you can use in combination. 
Rule #1! Cards in the same column can be selected together. 
<Mega> It doesn't matter if they're not lined up exactly straight, 
as long as they're in the same column. 
Rule #2! Three cards in the same row can be picked together. 
<Mega> It doesn't matter if they're not lined up exactly 
straight, as long as they're in the same row. 
Rule #3! Cards that have the same 
name can be picked together, regardless of their position. 
<Mega> Can you see the card on the screen that is white? 
<Mega> White cards are very useful. They can be paired with any card on the screen. 
None of the previous three rules apply to them. 
<Megaman> Got it! But what if I don't know what a card does? 
There's a description, right? How do I access it? 
<Mega> You can use the R Button or Y Button to see card descriptions. 
OK! I think that about sums up the Custom Screen. 
Try to select more than two cards, OK!? 
You can select them by touching them, as well. 
<Mega> Hey, you can still pick more. 
<Mega> You still need to pick a card that you can attack with. 
<Mega> Pick that card after you select an attack card. 
<Mega> I'll teach you about that one later, so don't use it now. 
<Mega> Let's go, kid. You haven't picked anything yet! 
<Mega> There's no need to run away, kid! 
<Mega> Press the OK Button now. 
<Mega> Finally, it's battling time! Wipe out those bad guys! Oh, but before that... 
In the bottom left are the cards you selected in the 
Custom Screen in the order that you selected them. 
<Mega> And to the right is the name and attack power of the card you can currently use. 
<Mega> You can use Battle Cards by pressing the A Button. 
Holding down the B Button will fire the Mega Buster constantly without delay! 
<Megaman> The A Button for Battle Cards, and the B Button for the Mega Buster... Got it! 
And that's my HP up in the top left, right? 
<Mega> Correctomundo. And it's game over for us if it drops to 0! 
The gauge in the top right is called the Custom Gauge. 
<Mega> The Custom Gauge fills up as time passes. 
Once the Custom Gauge is full, you can return to the Custom Screen by pressing 
the L Button or the R Button. 
<Megaman> So even if I've used all six of my cards, I can get more from the Custom Screen... 
<Mega> Exactly! So are you all set, kid? It's time to practice! 
<Megaman> Yeah, I'm ready! 
