<Mega> Up next, I'll explain about Countering and Bonus Cards. 
If you land a card attack on an enemy just as they're 
about to attack, that's a Counter. 
That'll catch them off-guard, paralyzing them for a time. 
You'll also receive a Bonus Card for doing so. 
Usually, you can only use cards you select on the Custom Screen. But if you 
land a Counter, then you'll be rewarded a Bonus Card. 
Bonus Cards are chosen from your Card Folder at random. 
Even so, they're great because you don't have to wait for the Custom Gauge 
to fill up before going buck wild on the enemy! 
But, you can't get another Bonus Card if you pull off a Counter with a Bonus Card. 
Countering is pretty hard to pull off, so you should work on your timing for a bit. 
Try to use a Bonus Card to delete all the enemies in one turn! 
<Megaman> I want to say "understood", but it's been a while since I last battled... 
It might take a little bit for it all to come back to me. 
<Mega> Why does it feel like I've heard that before...? 
Oh well! Just this once I'll help you with the timing, but just this once, you hear!? 
I can't focus on the battle if I'm trying to tell you what to do all the time! 
<Megaman> Thanks, Mega! 
<Mega> Yeah, yeah, yeah. So, this is how I'll help you with the Counter timing... 
I'll stick an arrow on top of the head of enemies that can be Countered. 
You'll achieve a Counter if you hit the enemy while the arrow is still over its head. 
There are Battle Cards that hit the enemy right away... 
But there are also ones that take more time to hit enemies. 
So, do your best to make Battle Cards hit the enemy 
while the arrow is still over its head. 
<Megaman> Got it! I'm ready to try it out now! 
<Mega> You haven't picked any Battle Cards yet! 
<Mega> There's no need to run, kid! 
