<Ace> OK, let's begin the tutorial program on the "Multi-Noise Form". 
Multi-Noise Form is when you fuse the power of two Noise types into one form. 
The act of fusing two types of Noise together is called "Multi-Noising". 
It's really easy to do, so take a look at the bottom screen, eh? 
<Ace> First, you must equip the ability, "<AcePrgm>". Don't forget to do that. 
Then, you select either a Brother Card or an 
Opponent Noise from the Custom Screen. 
So you know, you have to pick a Brother Card or 
Opponent Noise that is a different type of Noise than you are. 
<Ace> That's Multi-Noise Form for you. Simple, eh? But, oh yeah... 
When you select a Brother Card or Opponent Noise, you will be asked to either 
choose to perform a Multi-Noise or roulette. Understanding them is key. 
Roulette is when one of the four White Cards the Brother or Opponent has 
set is randomly selected and given to you. 
But, roulette will occur automatically if you are the 
same Noise type as the Brother or Opponent. 
Upon Muti-Noising, you will gain access to the power of both Noise types. 
If you take a hit by an elemental attack, you will revert back to Noise Form. 
Your elemental weakness will be the weakness of the 
Noise type you used to Multi-Noise. 
The same goes for your charged shot. 
That's it for the tutorial. Hurry up and try Multi-Noising! 
<Ace> Wait a second... Shouldn't you be Multi-Noising? 
You can't do it without selecting a Brother Card or an Opponent Noise. 
<Ace> ...Why would you run now? 
<Ace> Shouldn't you be Multi-Noising? So select "Multi-Noise" already! 
<Ace> Nice job! You seem like you're used to Multi-Noise Forms now. 
Multi-Noise Forms can be really powerful, depending on the Noise combination. 
Combine the types that work well with your battling style! 
