<Game> A Few Days Later... 
<Bud> I still can't believe it... 
Ace is... He's really dead isn't he? 
<Zack> It's a terrible shame, but... 
No one has been able to pick up his or Acid's signal. 
<Geo-2> {13}{EC}.{13}{E1}.{13}{E1}.{13}{E1} 
<Sonia> {13}{EC}.{13}{E1}.{13}{E1}.{13}{E1} 
<Prez> This is the first time that I've ever known someone that has died... 
Of course... I'm really sad, but... 
More than that... 
It almost feels like I have a hole in my heart... 
<Sonia> I can almost see him pop up out of nowhere... 
And give us that smile of his. Then say, "I'm counting 
on you!", while munching his snacks... 
*sniffle*{15}{E1}.{15}{E1}.{15}{E1}.{15}{E1} *breath*{15}{E1}.{15}{E1}.{15}{E1}.{15}{E1} 
*sob*{15}{E1}.{15}{E1}.{15}{E1}.{15}{E1} 
<Geo-2> Uh{15}{E1}.{15}{E1}.{15}{E1}.{15}{E1} Uh{15}{E1}.{15}{E1}.{15}{E1}.{15}{E1} 
*cry*{15}{E1}.{15}{E1}.{15}{E1}.{15}{E1} 
<Ace> But Geo, I know you can handle it. 
You're the world's greatest hero, after all! 
<Geo-2> Ace{15}{E1}.{15}{E1}.{15}{E1}.{15}{E1} 
Ace{15}{E1}.{15}{E1}.{15}{E1}.{15}{E1} 
Waaa!! 
<Mega> There's no time for crying, kid... 
It's just a waste of time. 
<Geo-2> .{15}{E1}.{15}{E1}.{15}{E1}Cut it out, Mega! 
<Geo-2> Ace died! 
Are you saying there's no time to mourn a friend!? 
Why!? 
And how... How can you act like nothing happened!? 
<Mega> I'm not. 
<Geo-2> {13}{EC}!! 
<Mega> It was just as horrible for me to see him go like that... I'm really hurting, too... 
But sobbing like a little baby isn't going to bring him back... 
I understand that, and I'm trying my best to deal with it like a man. 
<Prez> Will you two shut it already!? 
<Prez> This is no time for you two to be fighting. 
And it's the last thing that I want to put up with, considering the circumstances. 
<Sonia> Luna is right. 
We understand that Geo is sad, and we also understand what you are saying, Mega... 
And you're probably both right, in your own way... 
<Geo-2> {13}{EC}... 
<Bud> Geo... After that, what happened to Jack and Ms. Tia? 
<Geo-2> They... 
<Geo-2> Where do you plan on going...? 
<(Queen)Tia> We've had a certain "wish" for a long time now... 
And it hasn't come true, yet. 
<Geo-2> Ace... He died for you, Ms. Tia!! 
<(Queen)Tia> {13}{EC}.{14}{E1}.{14}{E1}.{14}{E1} 
We can't change anything that's happened... 
<Jack> {13}{EC}.{14}{E1}.{14}{E1}.{14}{E1} 
<Geo-2> I wonder what their "wish" is? 
And I have no idea where they went... 
<Mega> King was also gone after the explosion. 
<Zack> All the Crimson was taken away too. 
I'm certain he will make his next move very soon. 
<Mega> Hey, kid... 
Have you realized why Ace sacrificed his life and fought the way he did? 
<Geo-2> To protect what was precious to him... 
<Mega> Exactly. 
It wasn't just for Queen Tia. 
He fought and died for his fellow Satella Police officers, and also for you guys. 
If we don't take up his cause and fight for the reasons that he did... 
<Geo-2> Mega... 
{13}{E2}{03}{00} 
<Mega> There's no time to stand around idle. 
We have to fight in place of Ace. 
There isn't a lot that we can do at the moment. 
But we won't gain a single thing by being sad and crying. 
<Geo-2> Fight in place of Ace... 
Yeah, you're right. 
I'm sorry, Mega... 
I've been making Ace's death meaningless. 
Let's do what we can. 
After all, we are members of Ace's Commandos! 
<Sonia> I'm with you! 
<Bud> Hey, don't forget about me! 
<Prez> I'm with you too, Geo. 
I can't fight by your side, but there's still a lot that I can help with. 
<Zack> Same here! Pedia and I are always down with helping our friends!! 
<Geo> You guys are the best! 
<Mega> Kid... Let's go home and have a meeting to decide on our next move!! 
We've got to fight to keep our loved ones safe! 
