<Geo-2> W-WAZA was...! 
<Mr.King-2> Ho ho ho ho ho!! 
You have no way out, you worthless human scum!! 
Leaders of the world! I will be waiting for your letters of submission!! 
If you don't submit, your country will drown in Meteor G's Jamming! 
<Mega> That jerk!! You're threatening them!? 
Why don't you try me on for size instead!? 
<Mr.King-2> You have three days! 
After that, the countries who do not submit will cease to exist! 
Ho ho ho!! 
<Sonia> G-Geo!! What about the people that were in WAZA!? 
<Prez> Yeah! Do you think Dr. Goodall and Mr. Boreal are OK!? 
<Geo-2> Darn it{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} I can't get a hold of them. 
<Bud> That can't be good{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} I can't believe WAZA could be taken out so easily{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
<Zack> Pedia!! What's the status of WAZA!? 
<Pedia> It has become completely surrounded by Noise. 
The Noise appears to be strong enough to block all communications. 
<Zack> Inconceivable... 
So that's what he meant by "Jamming"... 
<Geo-2> What should we do{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} If Dr. Goodall and everyone... 
<Sonia> I won't believe that{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} It was already hard enough with Ace gone... 
They all can't be gone too... 
<Prez> We can't lose heart people! 
Once we do that, we've already lost!! 
<Geo-2> You're right!! 
We haven't lost yet! We can still do something!! 
<Bud> Geo... 
<Geo-2> We've fought our way through so much lately! 
Just because King has Meteor G doesn't mean he's won already!! 
Ace would... Ace would never give up at a time like this!! 
Let's all calm down and think! 
We'll definitely think of something with all of us working together!! 
<Sonia> No doubt! 
It's just like Geo and Luna said guys!! 
<Bud> Yeah!! I'm not giving up yet! 
<Zack> I'll work with Pedia to try and analyze the Jamming more thoroughly!! 
