<Mega> Geo!! There's a call from Boreal!! 
<Geo-2> From Mr. Boreal!? 
<Mr.Boreal> Geo, can you hear me? 
<Geo-2> Mr. Boreal! Mr. Boreal!! 
Are you OK!? 
<Mr.Boreal> Somehow, yes. 
<Sonia> Thank goodness! 
<Prez> How is everyone else? 
{13}{E2}{00}{00} 
<Mr.Boreal> {13}{EC}.{14}{E1}.{14}{E1}.{14}{E1} 
<Geo-2> Mr. Boreal...? 
<Mr.Boreal> .{15}{E1}.{15}{E1}.{15}{E1}I don't know how to say this... But... 
Dr. Goodall was swallowed up by the Jamming... 
<Geo-2> Dr. Goodall!? 
<Mr.Boreal> We got away unhurt only because we followed her orders to leave. 
But she told us that she had something that she must do. So she stayed... 
And that's when{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
I just hope... 
<Prez> ... 
<Geo-2> I'm coming to WAZA to help!! 
<Mr.Boreal> I would appreciate that. We're still in the middle of evacuating, so I could use 
a Commando like you to help search over here. 
<Bud> If you need Commandos, then I'm your man! 
<Sonia> Me too! 
<Mr.Boreal> Actually, could I have you two stay back? 
We don't know where Dealer will attack next, so I'd like to have people everywhere. 
<Bud> Ah... I understand. 
<Sonia> Good point... 
<Mr.Boreal> Well, that's that then. 
Geo, it's going to be sticky, but I'm counting on you to help the search over here! 
I've prepared a special Wave Liner that goes straight to WAZA. 
Please move out ASAP!! 
<Geo-2> Understood! 
I'll find Dr. Goodall! I promise! 
<Mega> Sweet!! I'm all fired up again!! 
<Prez> Hmm, why doesn't everyone else come over to my house for now? 
We'll do what we can from there!! 
<Sonia> Sounds good!! 
