<Geo> Mr. Boreal! Chief! I'm so glad to see that you two are safe! 
<Mr.Boreal> It's all thanks to Dr. Goodall. 
Geo, she's OK, right? 
<Geo> Yeah. 
.{14}{E1}.{14}{E1}.{14}{E1}Wait. She's not here yet? 
<Mr.Boreal> I heard that she is having an examination at the local hospital. 
After all, she did spend a long time in the Noise Wave. 
4But, why did she have us take shelter here? 
<Dr.Goodall> Yes, yes. 
I was just going to explain that to you. 
<Mr.Boreal> Dr, Goodall! How is your health!? 
<Dr.Goodall> There's nothing to worry about, thank you. 
.{14}{E1}.{14}{E1}.{14}{E1}That being said... About why I had you all evacuate to here{14}{E1}.{14}{E1}.{14}{E1}.{15}{E1} 
We predicted that Dealer's first target using Meteor G would be WAZA... 
And that after the other WAZA locations were destroyed, that the main 
computer would be our last hope... 
Dealer would never let that remain in our possession. 
4So... 
So then you stayed behind in order to complete certain counter-measures, correct? 
<Mr.Boreal> But, what counter-measures were they? 
<Dr.Goodall> I was completing the transfer of the main computer's functions. 
They are now in the environmental system that is here in <Castello.Alohaha>. 
4Brilliant! 
The environmental system certainly has the specs to 
perform the functions of the main computer properly. 
1Chief! 
1The analysis of Meteor G has been completed! 
It is currently resting in orbit above Earth!! 
<Geo-2> It's just as King said... 
<Mega> He's actually able to control its movement... Not to mention its other functions. 
4He truly is in complete control of it... 
<Dr.Goodall> If Meteor G were to strike the planet, every piece of 
technology would be wiped out. 
However, instead of hitting Earth with it, he will most 
likely use it as a tool of fear to control the world. 
<Geo-2> I won't let that happen! 
<Mr.Boreal> Well, we have no idea where he is now, plus we still have 
to come up with a plan to stop Meteor G. 
<Dr.Goodall> Hmm... 
Let's think about it in the opposite way. If we stop 
Meteor G, then we also ruin King's plans. 
We still have a chance... This battle is not over, yet. 
4Very well! 
From here on out, I am designating <Castello.Alohaha> 
as WAZA's new anti-Meteor G headquarters!! 
Let's hammer out the plans people!! This is our planet!! 
<Game> Yes, sir!! 
<Dr.Goodall> So, Geo... 
<Geo> Yes? 
<Dr.Goodall> The WAZA staff members are only doing what they are expected to do. 
Don't try to do too much on your own, Geo. Just do what you are capable of doing. 
<Geo> What I'm capable of doing? 
<Dr.Goodall> Right now, there is really nothing that can be done about Meteor G. 
<Mega> What are you talking about!? "Nothing to be done"!? 
We can take out some viruses or something!! Just let us go buck wild!! 
<Dr.Goodall> Hee hee hee... Oh, Meggers... 
Would you please save up all that energy for just a bit longer? 
We'll have you do your part once we have a plan. 
For now, I want you two to go back to <Echo.Ridge>. 
<Geo> Back to <Echo.Ridge>...? 
<Dr.Goodall> Yes, your mother must be worried sick about you. 
Go home and put a smile on her face. 
<Mega> She's got a point... You've been so busy that you haven't seen her lately. 
<Geo> OK, Dr. Goodall. I'll go home for a little while. 
But if anything happens, please let me know! 
<Dr.Goodall> I promise I will. 
<Mega> Alrighty then. Let's go see your mom!! 
