<Geo-2> Just what can I really do? 
I said I would fight on behalf of Ace as well, but... 
King has control of Meteor G, and we don't know where Jack and Ms. Tia are... 
Is there really anything that I can do? 
<Dread.Joker> You are so pathetic{15}{E1}.{15}{E1}.{15}{E1}.{15}{E1} 
<Geo-2> {13}{EC}!! 
<Dread.Joker> Weak creatures, such as yourself, have no reason to exist... 
And those who don't acknowledge their weakness are worthless themselves. 
The first step to gaining true power is to accept your weaknesses. 
In doing so{13}{E1}.{13}{E1}.{13}{E1}.{15}{E1} 
You will finally be able to join the battle as a fierce and proud warrior. 
<Geo-2> What do you know? 
What could you possibly know about a person's worth!? 
<Acid.Ace> Everyone is weak in the beginning. 
You know that, right, Geo? 
<Acid.Ace> To fight is to live. 
To fight with courage and not succumb to difficulties and hardships... 
When in the midst of battle, a powerless human will come to know both weakness and 
strength, bestowing them with true power. 
Geo{13}{E1}.{13}{E1}.{13}{E1}.{13}{E1} You have been through so much... 
You are no where near powerless... 
In fact, your ability to fight and persevere cannot be rivaled. 
{15}{00}No matter how difficult, never giving in, never being afraid, continuing the fight... 
That is strength... 
<Geo-2> Dad! 
{15}{00}You are a young man who has fought through many hardships in your short life. 
And that has enabled you to understand others' pain as if it was your own. 
"Righteousness"... 
Is when you believe from the bottom of your heart that you must help people. 
"Strength" and "Righteousness"{13}{E1}.{13}{E1}.{13}{E1}.{13}{E1} 
There is no stronger combination of attributes for a warrior... For a hero. 
Geo... You are already a true hero. 
You are a strong, righteous young man. You make me so proud!! 
<Geo-2> Was that{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} a dream{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1}? 
<Geo-2> Ah, a message. 
<Mega> It's from Boreal!! 
<Geo-2> TV...? I wonder what's up? 
