<Geo-2> It looks just like WAZA did... 
<Mega> Sadly there's no one around to update us on what's going on in there, this time. 
I wonder how many people are in there? 
<Geo> Ah, a call from Mr. Boreal! 
<Mr.Boreal> Wow... Are you already at <Studi.WBG>? 
You're pretty quick on your feet, Geo. 
<Geo> Mr. Boreal, there's no one here to give us any insight on the situation. 
<Mr.Boreal> Hmm, OK. 
I will tell you everything we have found out about <Studi.WBG>. 
<Mega> What took you so long!? 
<Mr.Boreal> Almost everyone was able to escape from <Studi.WBG>. 
However{15}{E1}.{15}{E1}.{15}{E1}.{15}{E1} 
<Geo-2> However? 
<Mr.Boreal> In the panic to escape, the celebrity, Belle appears to have been left behind. 
<Geo-2> Belle!? 
<Mr.Boreal> And then a staff member, Lee Stern, was swallowed 
in the Jamming while trying to rescue her. 
<Geo-2> Lee and Belle... 
<Mr.Boreal> So you know them? 
<Geo-2> Are they the only two who didn't get out? 
<Mr.Boreal> That's correct. 
Geo, would you mind going in to try to rescue them? 
<Geo-2> Of course! You can count on me! 
<Mr.Boreal> Great to hear. 
I will also send some Satella Police officers out to support you! 
<Geo-2> Understood! 
<Mega> Geo! We'll do this the same way that we did at WAZA! 
I'll smash down the brittle areas, so that we can get into a Noise Wave! 
Then we'll look for them inside there! 
<Geo-2> Sounds like a plan! Show that wall who's boss!! 
<Geo-2> Wizard On!! 
<Mega> Grrrrrr!! 
Time to tear this wall up!! 
<Mega> Grr! Roooaaar!! 
<Mega> OK! A couple of Noise Wave entrances, ready to go!! 
<Geo-2> Thanks, Mega!! 
We're coming guys! Just hold on!! 
