<Heartless> New information has come in, Mr. King. 
Leaders from all over the world are debating over 
whether they should or should not submit to Dealer. 
<Mr.King-2> They truly are idiots... 
They still can't understand the fact that there is no 
one who can defeat me, as long as I control Meteor G. 
Let them debate. 
They will never find a means to prevail over me. 
And when the time comes when they realize that, they 
will fall to their knees and beg for forgiveness! 
<Heartless> It shall be as you say, Mr. King. 
<Mr.King-2> By the way... 
Have you learned anything about whoever is causing 
problems with my control over Meteor G? 
<Heartless> Unfortunately... There has been no break in information, yet... 
<Mr.King-2> How dare you be so slow! 
When I say do something, then you complete the task immediately! 
You have until tomorrow! Otherwise, you will pay!! 
<Heartless> Please forgive me, sir... 
<Game> It looks like the demands of controlling Meteor G have made you a little irritable... 
Mr. King... 
<Mr.King-2> {13}{EC}! 
Who is that{15}{E1}.{15}{E1}.{15}{E1}.{15}{E1}? 
<Mr.King-2> Queen Tia! Jack! 
<Heartless> How did you get in here? 
<Queen.Virgo> You'd be better off if you didn't take us so lightly... 
Anyone with half a brain could escape from the 
Satella Police and break into this place. 
<Mr.King-2> So then it is you two who have been interfering with my control of Meteor G! 
<Queen.Virgo> {13}{EC}.{13}{E1}.{13}{E1}.{13}{E1}? 
I have no idea what you are talking about. 
<Jack.Corvus> Sis and I have been waiting a very long time for this exact moment... 
The moment when Joker is out of the picture, and you are in control of Meteor G! 
<Queen.Virgo> We can finally make our "wish" come true... 
King!! 
We're taking over both Dealer and Meteor G! 
<Mr.King-2> Ho ho... 
So you are telling me that you are taking everything I have from me? 
<Jack.Corvus> You got it, you jerk!! 
<Heartless> You must be insane, child... 
<Mr.King-2> Who was the person that raised you after you lost your parents and home? 
Was it not me? 
I cannot believe that my own children would stab me in the back like this. 
<Queen.Virgo> Oh spare us the benevolent father figure routine! 
Yes, you established the "King Foundation", in which you took orphans in from 
around the world and had them cared for... 
But the foundation was just a cover for your real work. 
<Jack.Corvus> You had a completely different reason for gathering all those children. 
<Mr.King-2> {13}{EC}... 
<Jack.Corvus> You choose the children with the most promise, and made them your subordinates. 
Then you had them commit all of your crimes for you. 
Sis and I were just two of those children. 
{13}{E2}{01}{00} 
<Queen.Virgo> However... Over time, those children were sent into extremely 
dangerous situations by your command. 
And none of them, except us, ever came back!! 
<Heartless> {13}{EC}... 
<Queen.Virgo> They never even considered that they were only being used by you!! 
<Mr.King-2> It was because of me that they even lived long enough to serve me. 
They should have been thanking me for that! 
<Queen.Virgo> Shut your mouth!! 
<Jack.Corvus> Right here, right now... 
You will pay for what you did to us and all of the other children!! 
King!! 
<Queen.Virgo> You're going down!! 
<Mr.King-2> Fools... 
<(Queen)Tia> Our EM Wave Change! 
<Jack> W-What's going on!? 
<Wolf.Woods> It's some kind of special Noise!! It's cancelling out EM Wave Changing!! 
<Virgo> Argh! This isn't right!! 
<Mr.King-2> This whole facility is under my direct control. 
In other words, everything here becomes as I desire. 
Now it is time... 
For you two naughty children to be punished. 
<(Queen)Tia> Ungh{15}{E1}.{15}{E1}.{15}{E1}.{15}{E1}!! 
<Jack> Argh! 
<Mr.King-2> Ho ho ho ho ho!! 
This is what happens when children play with things that they shouldn't!! 
<(Queen)Tia> Not{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} now{14}{E1}.{14}{E1}.{14}{E1}.!! 
<Jack> S{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1}is{14}{E1}.{14}{E1}.{14}{E1}.!! 
<Mr.King-2> Foolish children, that is all you ever were! Ho ho ho ho!! 
<Jack> Nooo{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1}!! 
<Mr.King-2> {13}{EC}!? 
<Jack> W-What...? 
<(Queen)Tia> .{14}{E1}.{14}{E1}.{14}{E1}It{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} wore off... 
<Mr.King-2> What is this!? 
Heartless, explain! 
Heartless!! 
<Heartless> It was I that stopped the attack on them. 
<Mr.King-2> Why would you do that!? 
Who gave you that order!? 
<Heartless> {13}{EC}... 
<Mr.King-2> Heartless!! 
<Heartless> {13}{EC}... 
.{16}{E1}.{16}{E1}.{16}{E1}Hmph. 
<Mr.King-2> {13}{EC}...!! 
H-Heartless{15}{E1}.{15}{E1}.{15}{E1}.{15}{E1} 
Y{15}{E1}-Y{15}{E1}-Y{15}{E1}.{15}{E1}.{15}{E1}.{15}{E1} 
Yooou!! 
It was you!? 
<Heartless> Muwahaha... 
I was the only one that you thought would never turn on you, wasn't I? 
Mr. King... 
<(Queen)Tia> {13}{EC}!! 
<Jack> W-What the...!? 
{12}{E2}{07}{00}{00}{00} 
<Heartless> Joker was the last of your loyal subordinates. 
Actually, he was only your Wizard so that he could fulfill his own Purpose... 
You have been surrounded by traitors from the very beginning. 
There was Jack, Queen Tia, and of course, myself... 
<Heartless> I wasn't expecting you two to show up here now, but... 
<(Queen)Tia> {13}{EC}... 
<Mr.King-2> Your insolence disgusts me!! 
All of you will...!! 
<Heartless> Don't bother. 
<Mr.King-2> What!? 
H-How did you...!? 
<Heartless> Goodbye, Mr. King... 
You will pay for your sins in the bowels of your own Noise. 
<Mr.King-2> N-Noooooo!! 
<Mr.King-2> Noooooo!! 
<Heartless> {13}{EC}... 
<Jack> So what game are you playing here, lady? 
<Heartless> I've been waiting for the opportunity to take King out. 
When the moment came I had to take my shot. 
That is all. 
But I actually expected Mega Man to show up. 
I never even considered that you two would get here before him. 
<(Queen)Tia> We appreciate you helping us out... 
But we don't know what your aim is, and we don't really care. 
We are here to make our wish come true. 
<Heartless> Why don't you tell me what your wish is in exchange for saving your lives? 
{13}{E2}{00}{00} 
<(Queen)Tia> To send Meteor G... 
...right into the planet. 
<Heartless> {13}{EC}... 
Are you crazy? 
You must know what would happen if Meteor G were to crash into the Earth. 
<Jack> Of course we know. 
We are now going to the main Cyber Core of this 
facility to overwrite the programming. 
Then we will delete King's control access, and reset its original course for Earth. 
<(Queen)Tia> Using Meteor G, we will be able to destroy every piece of technology in the world... 
That is our "wish". 
<Heartless> You don't seem like you are willing to change your mind. 
<Jack> It looks like you understand us completely. Now get out of our way, Heartless! 
<Queen.Virgo> You'll be sorry if you try to interfere. 
<Heartless> You sure aren't innocent little children, now are you? 
I don't want to make you cry, so I won't get in your way. 
But I won't forget this. I miscalculated that Mega Man would get here before you. 
But once he does show up, I will continue with my plans. 
<Queen.Virgo> {13}{EC}... 
We're leaving, Jack... 
<Jack.Corvus> Good!! 
<Heartless> {13}{EC}.{13}{E1}.{13}{E1}.{13}{E1}.{13}{E1}.{15}{E1} 
Mega Man{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
