<Heartless> Welcome to the orbital base... 
Thank you for coming, Mega Man. 
Or should I say... Geo Stelar. 
<Megaman> {13}{EC}... 
<Geo-2> Are you the one that sent me that pop-up? 
<Heartless> Yes. 
<Mega> Isn't she King's right hand woman? 
<Heartless> Call me Heartless. 
And just so you know... King is no more. 
<Geo-2> No more...? 
<Heartless> There was a minor setback in my plans, so I... 
Actually, there isn't much time, so I will be brief... 
<Geo-2> Jack and Ms. Tia took over Dealer? 
<Mega> And they're trying to crash Meteor G into the planet? 
<Heartless> That's basically it... 
<Heartless> The two of them are now in the {17}{E5}, which you can trans into ahead. 
I need you to stop them as quickly as you can. 
If they overwrite the main program, then Meteor G will hit Earth... 
<Heartless> And it won't only be EM technology that is lost when it hits. 
An astoundingly powerful shock wave will wipe out 80% of all human life. 
<Geo-2> That's horrible!! 
<Mega> Holy monkey!! 
<Heartless> But those two don't realize the grave consequences... 
Even if they did understand, one look into their eyes will tell you they won't stop. 
<Geo-2> Got it. 
Heartless... 
I'll stop them before they can complete the overwrite! 
<Heartless> The world is counting on you. 
<Mega> Wait just a second now. 
<Heartless> What is it, Omega-Xis? 
<Mega> Who are you, really? 
And what are you trying to achieve here? 
<Heartless> {13}{EC}... 
As I said before, there isn't any time right now. 
Please stop Jack and Tia. 
I will explain everything after the world is safe. 
<Geo-2> Come on, Mega!! If we don't stop those two, then the... 
<Mega> I guess I have no choice... You're gonna tell us everything later, lady! 
<Heartless> I promise... 
