<Megaman> Jack!! Ms. Tia!! 
{12}{E2}<Hope(Mom)> {01}{00} 
<Jack.Corvus> So you came, Mega Man. 
<Queen.Virgo> You're too late though... 
<Queen.Virgo> The overwriting of the program just completed. 
<Megaman> {13}{EC}!! 
<Jack.Corvus> Meteor G is now free from King's control. 
And its course for Earth has been set. 
It can't be stopped now. 
<Megaman> N-No!! 
<Mega> Are you guys crazy!? You have to stop that thing! 
<Megaman> 80% of humanity will perish if Meteor G hits the planet!! 
<Jack.Corvus> We know that. 
<Queen.Virgo> Our resolve will not be shaken, no matter the cost. 
<Jack.Corvus> This is necessary for our "wish" to come true... 
And there is nothing that can change our minds. 
<Megaman> Is that really true, Jack? 
<Jack.Corvus> Of course. 
We put up with being treated like slaves by King, for so long, for this very moment! 
<Megaman> What is this "wish" of yours? 
Why does it require Meteor G to crash into Earth? 
{13}{E2}{00}{00} 
<Queen.Virgo> To remake the world{15}{E1}.{15}{E1}.{15}{E1}.{15}{E1} 
<Megaman> Remake? 
<Queen.Virgo> To start completely anew... 
The world has grown foul and corrupted by technology. 
Technology stole everything from us. So we will wipe it out completely. 
Thus allowing the world to be reborn, pure and good. 
<Mega> I see you two feel strongly about this. 
What actually happened to you? 
<Jack.Corvus> .{14}{E1}.{14}{E1}.{14}{E1}If you really want to know, then shut up and listen. 
<Jack.Corvus> ...Fast-paced advancements in EM technology drastically improved people's way of life. 
The world itself also began to change as more and more 
EM technology was included into everyday life. 
<Queen.Virgo> Jack and I... 
Were born in a small country that was prospering thanks to its own EM technologies. 
Our father was the king of that country. 
<Jack.Corvus> Eventually, the countries that surrounded ours grew 
more and more interested in the EM technologies that our country was developing. 
Then before long{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
<Jack.Corvus> They invaded. 
Even though we were developing EM technologies, we were still a small country. 
We couldn't hold them off. And all the secrets to our EM technologies were taken. 
Our country was left in shambles. No technology, no infrastructure, no hope. 
<Queen.Virgo> We lost our parents during the struggle, leaving us to 
wander aimlessly as small and defenseless children... 
Every day was a nightmare... 
<Jack.Corvus> And then, we met King... 
You know the rest. 
He was attempting to gain control of Meteor G, which 
has the ability to corrupt EM technology. 
So we faked our loyalty, and waited earnestly for the chance to steal Meteor G. 
<Jack.Corvus> And finally our chance has come... 
Our wish is finally coming true!! 
<Queen.Virgo> Technology, in general, has made human beings suffer more than it ever helped{13}{E1}.{13}{E1}.{13}{E1}.{13}{E1} 
It has caused and sustained so many wars{13}{E1}.{13}{E1}.{13}{E1}.{13}{E1} 
That's why we will give this world a new beginning... 
<Jack.Corvus> We are leaving to join Meteor G for its descent. 
We will be its heralds as it brings judgment down upon the world. 
<Megaman> I can't let you do that! 
You two and Meteor G must be stopped!! 
<Jack.Corvus> You can't stop us. 
<Megaman> Spade Magnes!? 
<Mega> That's not the real one!! They've just made that from a bunch of data!! 
Let's take him out, kid!! 
<Jack.Corvus> Farewell{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
<Megaman> Jack!! Ms. Tia!! 
{10}{E2}{5E}{04} 
<Spade-Magnes> Raaaaaarrr!! 
<Megaman> Crud!! 
