<Heartless> Mega Man... I mean Geo... 
Where are Jack and Tia? 
<Geo-2> I couldn't stop them in time. 
They just wouldn't listen to anything I said. 
<Heartless> I see... 
So Meteor G is now 100% under their control. 
This is not the situation that I was hoping for. 
<Mega> Hey!! Something isn't right here!! 
You totally know more about what's going on than we do! 
So start talking!! 
Who are you!? 
And what are you up to!? 
<Geo-2> Please tell us, Heartless. 
<Heartless> .{14}{E1}.{14}{E1}.{14}{E1}Working for King was only a means to achieve my goal. 
<Geo-2> Your goal? 
<Heartless> There was someone that I urgently had to contact. 
You actually know him quite well, Geo. 
<Mega> .{15}{E1}.{15}{E1}.{15}{E1}Who could it be? 
<Geo-2> No clue... 
<Heartless> Kelvin Stelar{16}{E1}.{16}{E1}.{16}{E1}.{16}{E1} 
Your father. 
<Geo-2> D-Dad!? 
<Mega> What the heck!? 
How do you know Kelvin!? 
<Heartless> I used to work for a space research organization. 
My organization worked with Kelvin and his team on his mission into space. 
<Heartless> I talked to Kelvin quite a bit during that time. 
He was always talking about forming bonds with other 
worlds, and exchanging our cultures and ideas. 
I completely agreed with his views and ideas. 
He is truly a vital part of this planet's future on a galactic scale. 
<Geo-2> So you tried to contact him in order to rescue him from space, right? 
<Heartless> Yes. 
And that is when I bumped into King. 
<Mega> How did you "bump" into King while looking for Kelvin? 
What the heck could they have in common? 
<Heartless> {13}{EC}... 
<Geo-2> Heartless...? 
<Heartless> I discovered King while trying to contact Kelvin because... 
Because Kelvin is inside of{16}{E1}.{16}{E1}.{16}{E1}.{16}{E1} 
Meteor G. 
<Geo-2> .{14}{E1}.{14}{E1}.{14}{E1}D{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1}Dad{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} Is inside of Meteor G...? 
<Heartless> {13}{EC}... 
<Mega> Are you sure? 
<Heartless> Yes. 
Kelvin was in an accident in space, where he became an EM being, right? 
<Mega> Yeah, that's right... I turned him into an EM being so that he could 
achieve his dream of returning to this family. 
{12}{E2}<Heartless> {01}{00} 
<Heartless> And since then he has been wandering through space as an EM being. 
He discovered Meteor G on his way back. 
<Heartless> He realized that if he let it go, then Meteor G would strike the planet. 
So he transed into the core of Meteor G, and began to battle with it. 
<Geo-2> Dad is fighting it{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
<Heartless> Kelvin has continued to fight Meteor G by himself this whole time. 
<Geo-2> I finally know what happened to him... 
You tried to make contact with Dad while King was first 
gaining control of Meteor G, right? 
<Heartless> Exactly. 
My plan was to steal control of Meteor G away from King, 
call Mega Man there, and finally have him bring Kelvin back. 
After that, I would change Meteor G's flight path, thus saving Kelvin and the world. 
My plan was perfect... 
<Geo-2> But then Jack and Tia got in the way. 
<Heartless> Yes... My only miscalculation. 
Because of them, Meteor G is headed for Earth again. 
By now, there's nothing that we can do. 
<Geo-2> That can't be... We can't give up! We're so close!! 
There has to be a way to stop them!! 
As long as you don't give up there is always hope!! 
<Heartless> Geo... 
<Geo-2> There's a call from someone... 
<Mega> It's Boreal. 
<Mr.Boreal> Can you hear me, Geo? 
It looks like you are just about at the distance limit for voice communications... 
<Geo-2> Mr. Boreal, I'm so sorry... 
Jack and Ms. Tia took over control of Meteor G. 
<Mr.Boreal> Don't worry, I've heard everything through your <Hunter>. 
Geo, Heartless, please come back to WAZA. We've come up with a plan. 
<Geo-2> Go back to WAZA? 
Isn't the area completely covered by Jamming? 
<Mr.Boreal> When King lost control of Meteor G, the Jamming 
covering both WAZA and <Studi.WBG> dissipated. 
Please get here quickly. We don't have much time. 
<Geo-2> Understood!! 
<Geo-2> Heartless!! 
<Heartless> Yes... 
Before we leave I want to give you this, Geo. 
{A1}{E1} 
<Game> Geo got: "{F2}{E5}"! 
<Geo-2> What is this folder? 
<Heartless> I found this while searching for Kelvin. 
It was his folder. So I'm giving it to you, his son. 
<Geo-2> Dad's... folder... 
<Heartless> I will join you when I have finished my preparations. 
Please go on ahead. 
<Geo-2> OK. See you at WAZA!! 
<Mega> We've gotta move, kid!! 
