<Mr.Boreal> Geo, I'm so glad to see that you are OK. 
<Geo-2> But, Mr. Boreal... If we can't stop Meteor G... 
<Mr.Boreal> I know, I know... 
We have absolutely no intentions of giving up. 
As long as we don't give up there is always hope. 
Isn't that right, Geo? 
<Geo> Yeah! 
<Dr.Goodall> That's why we have decided to form a new Team. 
The Team's Purpose is to "Stop Meteor G". 
And we've decided to name the Team after the great power given to you by the 
Satellite Admins the first time you protected Earth. 
That great power was called... 
"Star Force". 
<Geo> Star Force... 
4We would like you to take the leader position of the Team. 
We believe it is in your power to stop Meteor G. 
<Geo> But, I don't have any clue how to do that. 
<Mr.Boreal> Oh, I almost forgot. 
The explanation will go much smoother if I introduce the other members first. 
<Mega> Other members? 
<Mr.Boreal> Would you two please come forward? 
<Geo> Woody!? And Lee too!? 
<Lee.Stern> To be honest, we both aren't really sure why we were selected for this. 
<Woody> But just being able to check out WAZA's facilities and 
meet the esteemed Dr. Goodall has been moving! 
.{14}{E1}.{14}{E1}.{14}{E1}Actually, why is it that you were called here, Geo? 
<Mr.Boreal> Well, now that all of the Team members have been 
assembled, we can discuss our mission plans. 
I will also explain why you all have been selected. 
<Mr.Boreal> But before that, a quick briefing on the current situation is in order. 
Meteor G has been freed of King's control, and is again headed straight for Earth. 
<Lee.Stern> Really!? 
<Woody> Magnes sent me a report on this not too long ago. 
If it isn't stopped, Meteor G will smash into the planet, 
destroying all EM technology in the world. 
And worst of all, most of humanity will be wiped out. 
<Lee.Stern> Really!? 
<Mr.Boreal> It's exactly as he said. 
Star Force must stop Meteor G at any cost! 
So let's move on to how we plan on doing that. 
<Mr.Boreal> We are going to use WAZA's massive Wave Station, known as "Dynamic Station"... 
To send Mega Man into space. 
<Woody> Mega Man!? 
You mean the same Mega Man that saved us before!? 
<Geo> {13}{EC}... 
<Mr.Boreal> We will use Dynamic Station to trans Mega Man into 
Woody's rocket, which is currently in orbit around the planet. 
<Woody> I'm with you so far, but why my rocket? 
<Mr.Boreal> Well... 
Thanks to Magnes going out of control for a short time, 
your rocket acquired a high degree of Noise resistance. 
Its resistance is high enough that the Noise being emitted 
from Meteor G will have little to no effect on it. 
<Dr.Goodall> Do you understand? 
<Geo-2> Mega Man will trans into the rocket, then it will get as close to Meteor G as it can. 
<Woody> Then Mega Man will trans into Meteor G from the rocket. 
Is that correct? 
<Dr.Goodall> Yes it is. 
You two are both very clever. 
<Woody> Thank you very much for the compliment, Dr. Goodall!! 
<Mr.Boreal> Finally, Mega Man will destroy Meteor G's central core. 
It will be very dangerous for Mega Man, but we have no other choice... 
<Geo-2> {13}{EC}... 
<Lee.Stern> Umm, I understand what you have said so far... 
But why have I been called here? 
<Mr.Boreal> Actually, you have a very important role to perform. 
Which is of course why we called you here today. 
<Lee.Stern> A very important role? 
<Mr.Boreal> Using Dynamic Station to send Mega Man to Woody's rocket... 
This involves him being sent out of Earth's atmosphere by dynabit transmission. 
The force of this style of transmission will incur quite the shock on Mega Man. 
That is why we would like you to design and build a 
Real Wave protective barrier that will allow Mega Man to get to the rocket safely. 
It will have to be an extraordinarily tough barrier, to say the least. 
<Lee.Stern> I see... 
<Mr.Boreal> We heard that the Real Wave event stage that you built was able to hold up, 
even when it was overrun with out of control Wizards. 
<Lee.Stern> Well, it did freeze up. 
What I did was... When the Cyber Core was taken over, I quickly 
rewrote the programming, creating a firewall. 
Very simply, I reinforced the event stage's strength. 
<Mr.Boreal> There is no one else in all of Electopia that is able to 
do such a thing in the short timeframe that you had. 
We really need your help with this. 
<Lee.Stern> I'll do anything I can to help protect the planet! 
<Dr.Goodall> We have 12 hours until Meteor G hits Earth... 
There is no time for any dilly-dallying. 
<Woody> 12 hours{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} That's going to be tight. 
<Lee.Stern> It's not enough time... 
<Game> No, there's actually more time than you think. 
<Geo> Heartless! 
<Woody> Who? 
<Lee.Stern> Wow, she's beautiful! 
<Heartless> According to my calculations, there are still 48 hours until Meteor G strikes. 
We have 2 days left. 
<Mr.Boreal> 2 days... How is that possible? 
<Heartless> Kelvin still hasn't given up{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
He has continued to battle with Meteor G, hindering its advance. 
<Geo-2> Dad{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
<Dr.Goodall> He really is an amazing man, isn't he? 
Just amazing... 
<Lee.Stern> If we have a whole 2 days, then we can definitely figure something out! 
<Woody> Configuring the rocket in time will be no problem then! 
<Mr.Boreal> Great! Then let's get to work, Star Force!! 
<Game> Geo's Team and Purpose have changed! 
<Woody> .{15}{E1}.{15}{E1}.{15}{E1}So, umm... Where is our great leader, Mega Man? 
<Geo> {13}{EC}! 
<Game> Ho ho ho... What a happy lot you all are. 
<Geo-2> K{13}{E1}.{13}{E1}.{13}{E1}.{13}{E1}King!! 
<Heartless> That can't be! 
<Mr.King-2> Did you really think dropping me in a little Noise Wave would finish me? 
Heartless, you've hurt my feelings. 
<Heartless> A human being can't possibly exist in a Noise Wave for any period of time and... 
{13}{EC}...!! 
W-Wait!! 
<Mr.King-2> Finally catching on, eh? Think everything through. 
The fact is that I am not human anymore. 
I used Joker's power to make myself an EM being. 
And now, Heartless!! You traitor!! You will die!! 
<Heartless> {13}{EC}!! 
<Geo-2> Watch out!! 
<Megaman> That was a close one... 
<Heartless> Mega Man! 
<Woody> No way! Geo is Mega Man!? 
<Lee.Stern> I knew it! 
<Mr.King-2> Hmph, it makes no difference. 
My plan is not yet complete, but soon enough... 
I will be the ruler of the world!! 
I hope you are looking forward to it as much as I! 
Ho ho ho ho ho!! 
<Geo-2> King{15}{E1}.{15}{E1}.{15}{E1}.{15}{E1} What could he be planning? 
{11}{E2}{02}{00} 
<Mr.Boreal> I have no idea. All we can do is make sure that our plan goes smoothly. 
Let's get back to work. 
<Geo> You're right! 
<Mega> You got a message, kid! 
<Geo> It looks like everyone wants to see me. 
<Dr.Goodall> Go see your friends, Geo. 
And have some fun. 
We should be able to send you to Meteor G tomorrow. 
<Geo> Understood! 
I really want to talk to everyone before tomorrow. 
I'll be back! 
