<Bud> Mr. Boreal called us while you were on your way here. 
<Zack> He told us everything that happened, as well as what the plan is. 
<Geo> Oh, OK{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
It's just like he told you. 
Tomorrow, I'm going into space to stop Meteor G. 
This will be our last chance to stop it. 
<Sonia> .{14}{E1}.{14}{E1}.{14}{E1}You'll be OK, right? 
There's nothing that could go wrong, right? 
Am I worrying too much? 
If you were to... Like Ace... 
<Geo> I'll be fine. 
I made a promise to Ace. 
I said that I would never stop protecting those who are close to me. 
<Prez> I just wish we could all be together during a terrible time like this... 
If any of you were to never come back... I can't even think about it. 
You have to promise me this, Geo. 
Promise that you will come back to us{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
<Geo> That's a promise I can keep. I'll be back. 
<Bud> You just promised us, right!? 
If you lie to us, then I'll make you eat lima beans! 
You better... You better come back safe!! 
<Zack> You have to be there for Prez's election celebration party! 
And also for Sonia's next concert! 
There's too much for you to skip out on!! 
<Geo> Yeah... I can't wait to do all that! 
<Zack> Me too! 
It'll be so much fun! 
Everyone will be there! 
Everyone{15}{E1}.{15}{E1}.{15}{E1}.{15}{E1} 
All of us{15}{E1}.{15}{E1}.{15}{E1}.{15}{E1} 
*sniffle*{15}{E1}.{15}{E1}.{15}{E1}.{15}{E1} *sniffle*{15}{E1}.{15}{E1}.{15}{E1}.{15}{E1} 
<Prez> Don't cry, Zack!! 
<Zack> Yes, Prez!! 
.{14}{E1}.{14}{E1}.{14}{E1}Waaa! 
<Geo> Mom... 
<Hope(Mom)> I'm sorry to interrupt your time with your friends. 
But there was something that I had to talk to you about. 
<Prez> We are the ones that should apologize for taking away precious time with your son. 
Please, take your time. 
<Hope(Mom)> An old friend was just over at our house. 
She is a former co-worker of your father's, as well as a dear friend of mine. 
<Geo> .{14}{E1}.{14}{E1}.{14}{E1}Heartless? 
<Hope(Mom)> That's one name she uses... 
<Geo> She told you everything, didn't she? 
<Hope(Mom)> Yes... 
About you being Mega Man, and about your father being inside of that shooting star{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
<Geo> .{14}{E1}.{14}{E1}.{14}{E1}I'm really sorry that I didn't tell you, Mom. 
I didn't want to worry you. 
<Hope(Mom)> You've been fighting this whole time, haven't you? 
I thought you would always be my little boy... 
But you've grown up into a strong, brave man, just like your father. 
It makes me a little sad, but it also makes me so proud of you. 
<Geo> Mom... 
<Hope(Mom)> I won't stop you. 
You are your father's son. 
I believe that you will come home... 
I believe that you will come home even more of a man than you are now{15}{E1}.{15}{E1}.{15}{E1}.{15}{E1} 
<Hope(Mom)> Take this with you. 
It's data that your father left with me when he went to space. 
<Geo> Dad's data... 
<Hope(Mom)> This data was your father's treasure. 
It is full of memories of our family together. 
I'm sure that it will bind you and your father together inside of that shooting star. 
<Geo> Thanks, Mom. 
I'll return it when I get back. 
{02}{E2}{0C}{00}{A1}{E1} 
<Game> Geo got: "Kelvin Key"! 
{01}{E2}{0C}{00}
<Game> Tomorrow{15}{E1}.{15}{E1}.{15}{E1}.{15}{E1} 
Is the last day before Meteor G strikes. 
<Mr.Boreal> Geo... .{15}{E1}.{15}{E1}.{15}{E1}Preparations are complete. 
Would you please come to WAZA? 
