<Mr.Boreal> Thanks for coming, Geo. Everything is ready to go. 
<Dr.Goodall> Behind me is the Dynamic Station{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
From here you can trans into Woody's rocket. 
4How is the rocket doing, Woody? 
<Woody> Everything is A-OK! 
It is very close to Meteor G at the moment, but I am reading all systems nominal. 
<Mr.Boreal> Wonderful. Just as expected. 
4How is the Real Wave, Lee? 
<Lee.Stern> Excellent. 
I've set it to automatically protect Mega Man as he is 
transing in from Dynamic Station to the rocket. 
<Heartless> Meteor G is steadily gaining speed as we speak. 
Kelvin might be{13}{E1}.{13}{E1}.{13}{E1}.{13}{E1} Reaching his limit... 
<Hope(Mom)> {13}{EC}... 
<Mr.Boreal> Geo... 
<Geo-2> Yes? 
<Mr.Boreal> The fate of the world is in your hands. 
We are all counting on you. 
<Geo-2> Don't worry{13}{E1}.{13}{E1}.{13}{E1}.{13}{E1} Meteor G doesn't have a chance against me and Mega! 
<Hope(Mom)> After you stop it{13}{E1}.{13}{E1}.{13}{E1}.{13}{E1} I want you home, right away. Got it, Geo? 
<Geo> Got it, Mom... 
And I'll bring Dad back with me. 
<Sonia> This stinks... 
Even though we fought this far as the Commandos, now 
Geo has to take the burden of completing the mission all by himself. 
I wish that I could have the power to resist Noise like he does... 
<Bud> Me too... 
I've worked so hard to learn to fight. And now I have to sit out in the final round,  
knowing that I can't help Geo... 
I'm sorry, Geo... 
<Geo> Don't be sorry, guys... 
I'm so proud to have had the two of you by my side this whole time. 
<Zack> You took on the FM-ians... And Lady Vega... 
You've used the power of bonds to create miracles, 
turning hopeless days into times of celebration... 
So I'm not worried at all! 
I know you will save the day and make it back safe! 
<Prez> Geo... We are your Brothers{13}{E1}{13}{E1}.{13}{E1}.{13}{E1}. We're always by your side. 
It doesn't matter whether you're in space or in Meteor G, wherever... 
No matter what happens{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
No matter how far away{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
We will all be right by your side. 
Don't ever forget that! 
<Geo> Thanks, guys... 
I know I can do this. 
With all of you guys... And Ace too... 
I have so many great friends supporting me. 
No matter what happens,  all your strength will see me through it. 
<Mr.Boreal> When you are ready, Geo... 
Trans into Dynamic Station over here. 
And Geo{13}{E1}.{13}{E1}.{13}{E1}.{13}{E1} Earth{13}{E1}.{13}{E1}.{13}{E1}.{13}{E1} and Kelvin{13}{E1}.{13}{E1}.{13}{E1}.{13}{E1} Are counting on you! 
