<Queen.Virgo> .{15}{E1}.{15}{E1}.{15}{E1}He's on his way... To stop our red shooting star{15}{E1}.{15}{E1}.{15}{E1}.{15}{E1} 
He's so close{15}{E1}.{15}{E1}.{15}{E1}.{15}{E1} That blue shooting star...{15}{E1} Mega Man. 
<Jack.Corvus> He doesn't have a chance... 
Bring it on, Mega Man! 
<Megaman> We made it to the rocket's Cyber Core{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
<Mega> We're in one piece too. 
<Megaman> W-What's going on!? 
<Mega> The Noise here is extremely strong!! It's because we're so close to Meteor G!! 
<Megaman> Will we be OK!? 
What if the rocket were to collapse before we accessed Meteor G? 
<Game> There's no need to worry!! 
<Megaman> Magnes!! 
<Magnes> Yup!! Good to see you, Mega Man!! 
There's no time to talk now, though. I need to boost the 
Noise resistance and suppress these vibrations!! 
Y{13}{E1}u{13}{E1}u{13}{E1}u{13}{E1}u{13}{E1}p!! 
<Magnes> When I launched the rocket, I never would have believed 
that it would be used to help save the world! 
And on top of that, the reason it can help is that I once went out of control, 
which gave it the resistance to Noise that is necessary! 
How crazy is that!? 
<Megaman> Magnes... How close is the rocket to Meteor G at the moment? 
<Mega> In other words... Are we going to make it there!? 
<Magnes> Even though the rocket is highly resistant to Noise{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
<Magnes> .{14}{E1}.{14}{E1}.{14}{E1}It's almost reached its limit. 
I'm going to take this thing as close to Meteor G as I possibly can, but... 
It looks like you will have to go through the Noise Wave to access Meteor G... 
<Mega> So now we have to go via a Noise Wave to get there? 
<Megaman> That'll be good enough! Thanks, Magnes! 
<Megaman> Viruses! 
<Magnes> They must have got in with all the Noise!! 
<Megaman> Leave it to me! 
Come on, Mega!! 
<Mega> It's butt whoopin' time!! 
