<Queen.Virgo> Umph{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1}!! 
<(Queen)Tia> I-I never imagined... 
<Megaman> Ms. Tia... 
<(Queen)Tia> It's not... over yet! 
I'm not giving up after all we've been through! 
We dulled our emotions and did countless terrible things... 
We even ignored all the times that Ace risked his life to save us from Dealer!! 
<Megaman> {13}{EC}...!! 
<(Queen)Tia> I can't quit now!! I refuse to lose! 
There is nothing left for us{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
Except to make our wish come true!! 
<Megaman> That's not true... 
<(Queen)Tia> {13}{EC}!? 
<Megaman> It's just not true, Ms. Tia... 
Yes, you did lose so much that was special in your life through technology... 
But{15}{E1}.{15}{E1}.{15}{E1}.{15}{E1} You still have Jack. That bond hasn't been broken... 
And all Ace could think about was saving you... 
This whole time you have had wonderful people in your life, right next to you... 
<(Queen)Tia> {13}{EC}... 
<Megaman> If you really let Meteor G crash into the planet... 
All the pain and suffering that Jack and you went 
through would be transferred to countless children throughout the world. 
How is that any different than what those other countries did to your own!? 
<(Queen)Tia> Be quiet! 
Don't you dare talk to me like you understand our pain!! 
<(Queen)Tia> I'm not giving up... Not ever!! 
<Megaman> Ms. Tia... 
<Jack> Sis... 
I think we should stop... 
<(Queen)Tia> {13}{EC}!! 
<(Queen)Tia> Jack... 
<Jack> I think Geo is right... 
We've been wrong all along... 
What we've been planning will not remake the world... 
Our plan would just make a whole lot of children like us. 
That's "destruction", not "construction". 
<(Queen)Tia> {13}{EC}... 
<Jack> The suffering caused by the development of technology should end with us. 
We were caught in the middle of other people's hate, and lost so much for it... 
Ace and Geo have risked their lives over and over to get us to understand... 
<(Queen)Tia> Ace{14}{E1}.{14}{E1}.{14}{E1}.{15}{E1} 
<Wolf.Woods> Hey, hey, hey! 
What the heck are you talking about, Jack!? 
<Jack> Just listen to me... I've been thinking about this for a while now. 
<Virgo> Hold up!! That's crazy talk! 
<Virgo> What's with the grim face, Tia!? 
Don't tell me you're second guessing yourself, or some ridiculous garbage like that!? 
<(Queen)Tia> {13}{EC}... 
<Wolf.Woods> You two are going to remake the world, and then become its rulers... 
I only decided to help you guys out because that sounded like a lot of fun! 
<(Queen)Tia> .{16}{E1}.{16}{E1}.{16}{E1}I'm not fighting anymore... 
<Virgo> You can't mean that!! 
Do you think that I'll let you get away with that? 
<Wolf.Woods> If you do this, then we'll destroy you and take Meteor G all for ourselves!! 
<Virgo> You're finished, Tia!! 
<(Queen)Tia> {13}{EC}!! 
<Jack> !! 
<Megaman> Jack! Ms. Tia! 
<Wolf.Woods> Aaarrrgh!! 
<Virgo> Aaahhh!! 
<Rogue> .{14}{E1}.{14}{E1}.{14}{E1}Pathetic. 
<Megaman> Rogue! 
<Mega> How did you get here!? 
<Rogue> Don't be silly. 
Breaking into a place like this is nothing to me. 
<Megaman> Well{13}{E1}.{13}{E1}.{13}{E1}.{13}{E1} Thanks for saving them... 
<Rogue> Save them? Give me a break. 
I told you this before. All members and supporters of Dealer will be dealt with. 
<Jack> ... 
<Rogue> ...So I guess there's nothing else for me to do here. 
<Megaman> Rogue... 
<Rogue> Do whatever you want once I'm out of here. 
<Megaman> Umm... 
Would you please take Jack and Ms. Tia back to Earth with you? 
<Rogue> They can follow me... 
But if they slow me down at all, they're on their own. 
<Megaman> .{13}{E1}.{13}{E1}.{13}{E1}Thanks. 
<(Queen)Tia> You just might be able to make a miracle happen... 
You might be able to fix the problems we created... 
We can probably never make up for what we've done, but we will do everything we can. 
<Jack> The future... Is in your hands. 
Once I've made up for all the things that I've done... 
Let's go out and play again... 
That is... if it's OK with you of course. I'd understand if you didn't want to... 
<Megaman> That sounds great! Wait for me on Earth!! 
<Mega> It's time, kid. 
<Megaman> Let's go see Dad and stop Meteor G! 
Come on, Mega!! 
