<Megaman> .{16}{E1}.{16}{E1}.{16}{E1}Dad. 
{15}{00}...Hey, kiddo. 
{15}{00}.{15}{E1}.{15}{E1}.{15}{E1}You've grown. 
<Megaman> Dad...!! 
{15}{00}Thanks for taking care of him, Mega... 
<Mega> No sweat. 
{15}{00}There's so much I want to talk to you about. But it'll have to wait for now. 
{15}{00}Meteor G is still growing stronger and stronger... 
I can't hold it back anymore. 
<Megaman> Let me help, Dad!! 
You'll be deleted if you push yourself any harder!! 
Leave it to me! 
{15}{00}You've really grown into an upstanding young man... 
I guess it's time to pass the baton... 
Mega Man is capable of anything, right? 
<Game> Ho ho ho... 
I'm not so sure about that. 
<Megaman> King!! 
<Mr.King-2> If I cannot have the planet for my own... 
Then I will just have to destroy it. 
I will become one with this shooting star, and rain 
punishment down on all of you pathetic humans. 
Farewell, Earth!{15}{E1} Farewell, humanity!{15}{E1} 
Your time is up!! 
<Mr.King-2> Meteor G!! Return to me!! 
{15}{00}...!! This isn't good!! 
<Megaman> Please stop, King!! 
<Mega> It's too late! 
<Mr.King-2> Watch in awe as Meteor G and I become one!! 
Ho ho ho ho ho! 
<Game> Mu{13}{E1}wa{13}{E1}ha{13}{E1}ha{13}{E1}ha{13}{E1}ha{13}{E1}ha{13}{E1}ha{13}{E1}ha!! 
Well... What do you think!? 
I will lead Earth to its destruction... I am Crimson Dragon!! 
{15}{00}What the...!? 
<Game> Kelvin Stelar!! 
You have been a thorn in my paw for far too long... 
It is a shame that such great power must go to waste!! 
Which is why I will have your power added to mine!! 
{15}{00}Ungh!! A{13}{E1}a{13}{E1}a{13}{E1}a{13}{E1}a{13}{E1}a{13}{E1}a{13}{E1}a{13}{E1}a{13}{E1}h{13}{E1}h{13}{E1}h! 
<Megaman> Dad!! 
<Mega> Kelvin!! 
{15}{00}Geo!! Don't worry about me!! 
You've got to stop King and destroy Meteor G!! 
<Megaman> But... I can't... 
I've missed you so much... And now I finally found you... 
I won't let you go!! 
{15}{00}What did you come all the way here for!? 
To protect those you love... Right!? 
There are many people on Earth who you share deep bonds with... 
And Hope... Your mother is there too!! 
You can't let all of them down!! They believe in you!! 
{15}{00}You must fight, Mega Man!! 
<Megaman> Dad{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
<Mega> Darn it!! Kelvin!! 
<Game> Ho ho ho ho ho! The power is overwhelming!! 
So, Mega Man! What will you do!? 
Are you still going to challenge me, even after I have acquired such power!? 
<Megaman> {13}{EC}.{13}{E1}.{13}{E1}.{13}{E1} 
<Game> Kelvin Stelar is now a part of me!! 
Would a nice boy like you harm his own father!? 
<Mega> K-Kid...! 
<Megaman> Dad told me to fight{13}{E1}.{13}{E1}.{13}{E1}.{13}{E1} 
If I don't stop you now, then all the sacrifices that 
everyone has made until now will have been in vain!! 
<Megaman> Crimson Dragon!! 
For the people that I love... 
I will defeat you! You won't see the light of tomorrow! 
<Game> You are pitiable, indeed! 
Come then!! 
Have a look at the true power of Meteor G!! 
<Mega> Let's rock, kid!! 
<Megaman> Last Battle!! 
<Megaman> Ride On!!{30}{EC}
