<Mr.Boreal> Geo!! Geo, please respond!! 
...Darn it!! It's not getting through!! 
<Heartless> Even though Meteor G is gone... 
<Hope(Mom)> Geo...!! 
<Prez> Come on, Geo... 
You promised me that you would come back... 
<Sonia> Isn't there something that we can do, Mr. Boreal!? 
<Mr.Boreal> ...!! 
<Zack> Mr. Boreal!! 
<Bud> For cryin' out loud!! 
Isn't there someone that can help him!? 
I'll do anything if someone rescues him!! 
I'll stop eating, I'll study, whatever it takes... 
So please... 
Somebody please help him!! 
<Game> *static* 
<Mr.Boreal> {13}{EC}.{15}{E1}.{15}{E1}.{15}{E1}? 
What's that noise? 
<Sonia> It's from my <Hunter>. 
<Zack> Actually, everyone's <Hunter> has received a message. 
<Pedia> It's not just us. 
Every person in the whole world has received a direct transmission to their <Hunter>. 
<Prez> What's going on? 
<Game> *static*{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
.{14}{E1}.{14}{E1}.{14}{E1}People of Earth{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
.{14}{E1}.{14}{E1}.{14}{E1}Can you read me{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1}? 
<Mr.Boreal> T-That voice... Could it be{13}{E1}.{13}{E1}.{13}{E1}.{13}{E1}? 
<Hope(Mom)> Kelvin!! 
{15}{00}Meteor G was destroyed... 
By a young boy... 
Who wanted to protect the people that he loved... 
He always believed in us, and he never gave up... He... saved us all... 
However... Right now, that young boy is alone and lost in space... 
That boy is{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
My son, and he means more to me than anything... I want to{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
Bring him back to all of his friends{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
Back to his mother... Geo{15}{E1}.{15}{E1}.{15}{E1}.{15}{E1} 
<Hope(Mom)> Kelvin!! 
I-I can't believe it!! 
<Heartless> Hope... 
{15}{00}Geo fought all by himself, risking his life in order to 
give us a chance to live our own lives to the fullest. 
I need{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} you all{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
To pray, wish, or picture in your minds that Geo will make it home. 
As a fellow human being... 
As a father... 
I'm begging you all{15}{E1}.{15}{E1}.{15}{E1}.{16}{E1} 
Please{15}{E1}.{15}{E1}.{15}{E1}.{16}{E1} 
{16}{EC}{10}{E2}{79}{04} 
<Game> *static* 
<Zack> The transmission was cut{15}{E1}.{15}{E1}.{15}{E1}.{15}{E1} 
<Mr.Boreal> .{15}{E1}.{15}{E1}.{15}{E1}Kelvin is right. We can't give up on Geo! 
<Dr.Goodall> You heard the man, people! 
We're going to do everything that we can to bring Geo back to Earth!! 
4All WAZA staff and Satella Police officers!! 
You are to do everything in your power to rescue Geo Stelar from space!! 
I want ideas and strategies! Immediately!! 
There is only one condition to my orders!! 
Never give up!! 
Now get to work!! 
