<Game> A memory belonging to Kelvin has surfaced{16}{E1}.{16}{E1}.{16}{E1}. 
{15}{00}OK... It's time for me to leave. 
<Hope(Mom)> {13}{EC}... 
AHave a safe trip, Dad! 
{15}{00}Hope... I wish you would send me 
off with a smile, like Geo. 
<Hope(Mom)> You're right. I'm sorry. 
I know going to space has always been your dream. 
I'm so happy for you. 
{15}{00}Thank you, honey. 
ADad! 
Will you tell me all about space once you get back!? 
{15}{00}Of course! But only if you're a good boy while I'm gone! 
<Hope(Mom)> Kelvin... 
Please... Please be careful out there. 
{15}{00}I will, I promise. 
I would never leave my family all alone. 
Geo... Take care of your mother for me while I'm away, OK!? 
AOK! Leave it to me! 
I'll protect her with my life! 
<Hope(Mom)> Geo... 
{15}{00}You're a good boy, Geo. You make me so proud. 
And don't worry about me. I'll be just fine up there. 
<Hope(Mom)> Kelvin... Be careful... 
{15}{00}I will... I love you both. 
{15}{00}{13}{EC}(No matter what happens  to me, Geo will be there...) 
{13}{EC}(He'll protect her.) 
{13}{EC}(I can trust him to continue  my dream of spreading  the importance of bonds.) 
{13}{EC}... 
{13}{EC}(.{14}{E1}.{14}{E1}.{14}{E1}Wow, it's not like  me to talk like that...) 
{13}{EC}(I'll make it home...) 
{13}{EC}(And I'll hold my family  in my arms, like always.) 
{13}{EC}(Then I'll have Hope's special  meatloaf and green beans.) 
{13}{EC}(While I tell Geo all  about my time in space.) 
{13}{EC}(Dang, I'm the luckiest  man in the world!) 
