<Mega> Hey, are you done yet!? We should get to the Roof ASAP! 
<Mega> That Prez girl's calling for us. We better hustle to the first floor snack shop. 
<Mega> Wave change with the R Button and pulse in via the Wave Station! 
<Mega> Viruses! It's been way too long since our last battle... It's time to go buck wild! 
<Mega> I wonder if that Woody, or whoever, guy is OK? 
<Mega> Use the R Button to cancel your Wave Change and pulse out at the same time! 
<Mega> Head for the Sprinkler CC! There are some viruses that need deleting! 
<Mega> Use the R Button to trans out! 
<Mega> Prez is waiting for us at the first floor snack shop. 
<Mega> Aren't you going to form a Brother Band with both Bud and Zack? 
<Mega> Shouldn't you be searching for people in school who look like they need help? 
<Mega> You're supposed to find the teacher who is in charge of the Real Wave tree. 
<Mega> We need to fix the moth display in the Science Club Room. Let's get in the CC! 
<Mega> The display is back to normal now, huh? Let's go tell that scary teacher! 
<Mega> We have to get the things the scary teacher needs in his HELP pop-up. 
<Mega> Alright! It's time to get to the Real Wave tree on the Roof! 
<Mega> This Wizard is the reason the moth display is wacky! Let's take him out! 
<Mega> It looks like there's someone that needs help at the first floor snack shop. 
<Mega> You have to help them make up. The other friend is in the park in <Echo.Ridge>. 
<Mega> The source of the problem may be on the Wave Road. Let's check it out. 
<Mega> The message should have gotten through. Let's report in at the snack shop. 
<Mega> The science club seems to be in a bind. You should go to the Science Club Room. 
<Mega> I wonder who it is that's waiting for you in the school entrance? 
<Mega> You should get some rest so you're fresh for tomorrow. 
<Mega> We're supposed to meet by the train wicket, right? 
<Mega> The tournament is taking place in the {BD}{E4}. 
<Mega> Hey! So now it's cool if you don't go to <Spica.Mall>? 
<Mega> The security system has activated, even though 
there's been no emergency! We should check things out! 
<Mega> Don't you think we should go report in to Prez? She scares me when she's mad! 
<Mega> If someone is asking for a fight, then I'm accepting! 
EM Wave Change and head to the Event Stage! 
<Mega> Now we can get to the {BD}{E4}. 
<Mega> We've got to stop the out of control Wizards! 
<Mega> We should see that Prez girl now that we have the card. She's in the {BD}{E4}. 
<Mega> Let's get the card to that Woody guy. He said he'd be in the Science Club Room. 
<Mega> Tomorrow's launch day, huh? It's probably best that you get a good night's rest. 
<Mega> It's finally launch day!! They're launching from the roof, so let's go! 
<Mega> Magnes must be stopped! Trans in to the Rocket's Cyber Core! 
<Mega> That out of control Magnes is going down!! Come on, kid! 
<Mega> That out of control Magnes is going down!! Come on, kid! 
