<Mega> Aren't you going to school? 
<Mega> We need to go to the apartment building and enter the number Prez gave us. 
<Mega> We should be able to open the school gate's Real Wave now. 
<Mega> You gotta get to class! 
<Mega> The classroom is really bustling today. I wonder what's going on? 
<Mega> You're going to look for that Jack kid, right? 
<Mega> The Roof should be a safe place to go! Come on! 
<Mega> We should be safe for now. Let's just waste some time for a bit. 
<Mega> You should go get some sleep so you're 100% for tomorrow. 
<Mega> We're meeting at the train wicket, aren't we? You better move your butt! 
<Mega> I've never been to a TV studio before! Let's go see what it's like in there! 
<Mega> Aren't we supposed to use the Wave Road to find Sonia inside the studio? 
<Mega> Now that you have the pass you can enter the studio all dignified like. 
<Mega> Let's take a look around the studio! 
<Mega> Don't you need to get to the street lined with trees for the filming? 
<Mega> You need to talk to the make-up Wizard. 
<Mega> It seems that the missing Wizard is in the Regulator Cyber Core. 
<Mega> Problem solved, huh? Go check on Prez and the others. 
<Mega> It's filming time! Get over to the street lined with trees! 
<Mega> Taurus Fire is going down! 
<Mega> You should really get over to the Event Stage. 
<Mega> Patrol the studio! We won't let anything bad happen while we're here! 
<Mega> There's something going on in the equipment area. 
<Mega> I wonder if the Wizard is OK or not? Trans in to the {10}{E5}! 
<Mega> Let's keep on patrolling the studio. 
<Mega> Lee looks troubled. We better go talk to him. 
<Mega> It's our duty to patrol the studio and make sure nothing else bad happens. 
<Mega> It's bomb searching time! First we should talk to the security Wizard. 
<Mega> Hey, kid! Trans in to the stunt car! 
<Mega> A Wizard that's helping look for the bomb is in here! Let's go help him out! 
<Mega> The problems just keep popping up... All we can do is to keep on patrolling! 
<Mega> Argh! It looks like there's another disturbance! 
<Mega> It's just about time for Sonia's concert to start. The stage awaits! 
<Mega> We have to find that Wizard, kid. He should be in this Cyber Core. 
<Mega> What a spectacular stage... The special seats are right over there! 
<Mega> Hey, what are you doing? Hurry up and get to the Event Stage to see Sonia! 
<Mega> Trans in to the <Stage.Evento> CC! Move, move, move! 
<Mega> Get your butt transed in to the <Stage.Evento> CC! This is no time for goofing off, kid! 
<Mega> That out of control Ice must be up ahead. Stay frosty, kid... No pun intended. 
<Mega> Let's get to the stage, kid! It's almost time for Sonia's last song already! 
