<Mega> We're headed for the "Astro Wave"! You can 
get there from the highest point in <Echo.Ridge>. 
<Mega> The distance to <Alohaha> is shortened greatly by using the Astro Wave! 
<Mega> We've finally made it to <Alohaha>! You can get down using the Wave Station. 
<Mega> What are we doing here? Prez is going to get angry if we don't stop dilly-dallying. 
<Mega> We should go see, "Strong", the Wizard that's in <Castello.Alohaha>. 
<Mega> I guess Strong isn't around... Do you think we should head back to where Prez is? 
<Mega> Let's explore the Cyber Core of the stand. 
<Mega> Looks like everything is settled now. We should go let Bud know. 
<Mega> It looks like we can go to the beach now. We shouldn't waste such an opportunity! 
<Mega> You should get closer to the water and put on your bathing suit! 
<Mega> Who cares about the Wave Road? The ocean is calling! 
<Mega> Either way, I wonder who it was that rented out the beach? 
<Mega> Let's take a look inside the Real Wave of the stone wall. Trans in to the Cyber Core! 
<Mega> Hey, it looks like something is going on up ahead. 
<Mega> Don't waste a great chance to enjoy the ocean water! 
<Mega> Let's go ask Strong if he knows anything about the thief. 
<Mega> It seems that the thieves are somewhere on the Wave Road. We have to find them! 
<Mega> You need to find the stolen stuff! It should be on the Wave Road somewhere! 
<Mega> Let's go return what we got back. 
<Mega> I thought you wanted to go learn about <Castello.Alohaha>'s environmental system? 
<Mega> The environmental system is in the back. Let's go see what it's like. 
<Mega> We gotta trans in to the environmental system's CC! Come on, come on! 
<Mega> The out of control Strong is in back. Don't let your guard down for a second! 
<Mega> You fell in... You better get out of there! 
<Mega> The Crimson was being pulled away toward the beach. We better head that way... 
<Mega> Could they be up ahead...? 
