<Mega> You're looking for Boreal... Maybe your mom knows where he is? 
<Mega> She said Boreal is in Alohaha! Get there on the double! 
<Mega> She said Boreal is in Alohaha! Get there on the double! 
<Mega> Boreal should be on the island somewhere. Let's find him! 
<Mega> Get off the Wave Road and look for Boreal! 
<Mega> You're supposed to enter a passcode into the security gate, right? 
<Mega> A fingerprint? Will mine work? Are claws OK? 
<Mega> We finally got in! What's with all the pomp and circumstance anyway? 
<Mega> It looks like this is going to take a while. Why don't 
you go ask around about Kelvin for a bit? 
<Mega> There's probably someone here who knew Kelvin! 
Let's ask around the Command Center! 
<Mega> Hmph... Ace, or whatever he calls himself, called for us! Go to the Satella Police HQ! 
<Mega> Is this the viruses' doing? Kid... We should check out the Info Board CC! 
<Mega> Dr. Goodall called for you! Maybe she figured something out? 
<Mega> The viruses causing the problem should be close by! 
<Mega> Scattered pieces of Luna's data? Bah! Ask that jerk, Acid! 
<Mega> We have to keep finding these until that loser Acid tells us there's no more! 
<Mega> They said you can get to WAZA via the Astro Wave! 
<Mega> That's some strong Noise! Be careful, kid! 
<Mega> We'll worry about Dark Phantom later, kid. We need to hurry to WAZA! 
<Mega> The place is swarming with those copy freaks! We're wiping them out! 
<Mega> That Dark Phantom dolt! We've got no choice. Let's go to the main computer room! 
<Mega> He ran away into the Main Computer CC! Let's catch him, kid! 
<Mega> Ace and Queen Tia... I want to see that! Let's go outside! 
<Mega> Dr. Goodall... Please take care of Prez. 
<Mega> This time we're taking that Shakespeare loser down! 
<Mega> Now we just have to worry about Prez... Dr. Goodall is in the main computer room. 
