<Mega> Let's talk to the teachers around school and help Luna out! 
<Mega> You're going to talk to the gardener on the roof that has a problem, right? 
<Mega> That's some powerful Noise! That won't work with all of it in there! 
<Mega> Get your butt to the Cyber Core of the Sprinkler! 
<Mega> That was easy as pie, kid! Now let's go tell Damian and Wolf! 
<Mega> You've already went around to enough people, right? So go tell Prez you're done! 
<Mega> You've got a message from Ace! Hurry up and read it! 
<Mega> The Main Computer CC... That's where you fought Dark Phantom! 
<Mega> There's something going on in <Echo.Ridge>! Move, move, move! 
<Mega> It looks like the only way to <Echo.Ridge> is via the Astro Wave! 
<Mega> Where's the fire!? Keep an eye out, kid! 
<Mega> Use the Astro Wave to get to <Alohaha>! Then go to <Studi.WBG> from there! 
<Mega> OK, let's go find Prez and the gang! 
<Mega> Shouldn't we be getting back to <Echo.Ridge>? 
<Mega> That's some fierce Noise! 
<Mega> Don't be afraid, kid! Man up and get in that Noise Wave! 
<Mega> There's usually a Noise Wave wherever viruses are around! Keep your eyes peeled, kid! 
<Mega> Did you really read the message from Harp Note? 
<Mega> That's one thing taken care of for now. Let's get back to Satella Police HQ! 
<Mega> There has to be some place where the viruses are coming from! 
<Mega> Alright, it's time to get out of this Noise Wave! 
<Mega> There has to be some place where the viruses are coming from! 
<Mega> Well then, I think it's time to go home! 
<Mega> Don't you think it's time to go get some rest? You had quite the busy day. 
<Mega> Prez and the rest already went to school ahead of you! You better get there quick! 
<Mega> Hey, kid! I think you better talk to Prez before anything else! 
<Mega> She said Bud and them are in the classroom! 
<Mega> You've got to follow that Solo jerk! Get to the first floor Wave Road! 
<Mega> Who would have thought!? We're actually going to fight alongside of Rogue! 
<Mega> All that's left is for us to go to the Roof and whoop Jack and Corvus's butts! 
