<Mega> You ought to at least say hello to your mom! Manners, kid! Manners! 
<Mega> The Wizards are going out of control in the entrance! Go, go, go! 
<Mega> It sounds like there are Wizards going out of control in <Spica.Mall>! 
<Mega> Find any Wizards that are going out of control and stop them in their tracks! 
<Mega> Let's get to school on the double! 
<Mega> Prez and the gang are outside waiting for you. 
<Mega> You better get to class! 
<Mega> Since there's time, why don't you talk to everyone for a bit? 
<Mega> The Satella Police want to see you! 
<Mega> Now what's going on? I guess we better go talk to Ace! 
<Mega> Wizards are out of control at the <Stage.Evento> of WBG Studios! We better hurry! 
<Mega> Today was a pretty rough one, huh!? You should go home and take it easy! 
<Mega> Hey, kid. Your mom doesn't look so happy... 
<Mega> Let's go get some rest! 
<Mega> I think it's time you got some sleep, kid. You are only human after all! 
<Mega> Detective Stelar! First, you need to do some 
investigative research at school and at <Spica.Mall>! 
<Mega> The Wizards went out of control here, huh? Let's look for a Noise Wave entrance. 
<Mega> There's something here! My detective's sixth sense is never wrong! 
<Mega> Three separate incidents took place in the building. Let's search all of <Spica.Mall>! 
<Mega> There's something here! My detective's sixth sense is never wrong! 
<Mega> They said an out of control Wizard was in a Cyber Core in this area. 
<Mega> There's something here! My detective's sixth sense is never wrong! 
<Mega> They said an out of control Wizard was in a Cyber Core in this area. 
<Mega> There's something here! My detective's sixth sense is never wrong! 
<Mega> Let's go look up ahead! 
<Mega> Trans in to the Cyber Core of that door, kid! 
<Mega> The door should be open now! Let's go check! 
<Mega> Take the Wave Road all the way to the power core! 
<Mega> If we break the defense system, the Wave Road should reconnect again. 
<Mega> We're almost to the power core! Stay frosty, kid! 
<Mega> We can move forward now that that's taken care of! We're so close! 
<Mega> Ace didn't seem right... Stay on his heels, kid! 
<START-DIALOG>
<Mega> Ace took off ahead all by himself... 
<START-DIALOG>
<Mega> There should be a way to unlock the lock in this Cyber Core! 
<Mega> A defense system, huh? Destroying the control unit ought to do the trick. 
<Mega> Find the control unit and destroy it! 
<Mega> There should be a control unit here too! Tear it up! 
<Mega> Hey, aren't you going to meet with Ace!? 
<Mega> Hey, kid... Do you think that maybe Ace... Never mind, forget it. 
<Mega> Hey! What the heck are you doing? We've got to search the Dealer Base! 
<Mega> We found a decent clue, huh!? But we need to find more! 
<Mega> See! There was a good clue here after all! My sixth sense is never wrong! 
<Mega> We'll come back here later... Impatience is a felony, detective! 
<Mega> We got a Noise Code! The only place left to search is <Studi.WBG>! 
<Mega> There's no doubt about it, detective! It ran away into the Noise Wave! 
<Mega> We opened the Noise Wave with the Noise Codes. We're so close to the Dealer Base! 
<Mega> The entrance to the Dealer Base should be around here somewhere! 
