<Mega> Let's go back to your house and work out a strategy! 
<Mega> Why don't you talk to everyone for a bit? 
<Mega> We're going to WAZA! We have to save Dr. Goodall! 
<Mega> Hey! Hurry up and get to WAZA! Don't you want to save the old lady!? 
<Mega> We can enter the Noise Wave through the holes I knocked in the wall! 
<Mega> Is Dr. Goodall here!? Find her, kid! 
<Mega> It looks like the old lady has a plan. Go talk to her. 
<Mega> Come on, kid! Pulse out and go talk to Dr. Goodall! 
<Mega> She said something was in <Castello.Alohaha>, right? Let's check it out. 
<Mega> You ought to go see your mom! 
<Mega> You should get some rest. 
<Mega> He said to check out the TV. I wonder if something is up? 
<Mega> King attacked <Studi.WBG>! We have to go help!! 
<Mega> Let's go rescue Lee and Belle! Get a move on to <Studi.WBG>! 
<Mega> We can enter the Noise Wave through the holes I knocked in the wall! 
<Mega> Lee and Belle should be here somewhere! Find them! 
<Mega> We still have to find Belle! Hurry! 
<Mega> We still have to find Lee! Hurry! 
<Mega> You can get to King via the Astro Wave with that pop-up. 
<Mega> I've got a bad feeling about this... But we're not giving up! Let's keep going! 
<Mega> That jerk, King, is definitely around here. 
<Mega> We have to hurry to the {17}{E5}! Those two must be stopped! 
<Mega> Jack and Queen Tia are in here... We have to act quickly and stop those two! 
<Mega> Let's return to the Orbital Base and talk to that one lady... Heartless, or whatever. 
<Mega> Let's go talk to that lady, Heartless, or whatever. 
<Mega> Boreal is waiting at WAZA. 
<Mega> Boreal is in the Command Center. Go talk to him. 
<Mega> Get off of the Wave Road and go see Boreal in the Command Center. 
<Mega> Isn't everyone waiting in <Echo.Ridge>? 
<Mega> Finally... Let's head to WAZA, kid. 
<Mega> Welcome to WAZA... Everyone is assembled. 
<Mega> The plan is for us to trans into the rocket from WAZA! Meteor G, here we come! 
<Mega> Trans in to the rocket from that huge Wave Station! Watch out, Meteor G! 
<Mega> It's finally time!! We're going to Meteor G!! 
<Mega> Meteor G is right out there! Get fired up kid! It's time to go buck wild on the bad guys! 
<Mega> It's finally time!! We're going to Meteor G!! 
<Mega> We're stopping that stupid red shooting star no matter what it takes!! Onward, kid! 
<Mega> Hey, kid... Are you ready for this? 
