<Game> It's a shelf for shoes. 
Kelvin bought it because he likes the chic design. 
<Game> It's a plant that Hope named Barnaby. 
<Game> It's a TV. 
<Game> The flower bed is visible. 
It's really relaxing just looking at it. 
<Game> It's a refrigerator. 
The inside is sparkling clean just like always! 
<Game> The kitchen. 
It's cleaner than clean! 
<Game> Utensils. 
They're sparkling! 
<Game> It's the control panel for the living room. 
The air conditioning and lighting can be fine tuned with it. 
Kelvin special ordered it! 
{0C}{E1}{01}{00}{B1}{13}{0F}{00}
<Game> It's the dining room table. 
<Game> It's the living room table. 
<Game> The <Hunter>-VG is reacting! 
NOISE WAVE DETECTED. {15}{E1}.{15}{E1}.{15}{E1}.{15}{E1}ACCESSED! 
{0A}{E1}{8B}{13}
<Game> The kitchen. 
Dinner today is chicken and mashed potatoes. 
The mashed potatoes are handmade! 
<Game> The kitchen. 
Dinner today is macaroni and cheese. 
Hope's favorite... 
<Game> The kitchen. 
Dinner today is liver... 
<Geo> Whoa...! 
T-Today... I'm just not feeling hungry at all... 
I'm fine until breakfast tomorrow. 
<Game> The kitchen. 
Today's dinner is... Breakfast. 
Geo's favorite day is "Breakfast for dinner day". 
<Mega> Hope has never made my favorite meal before... 
{13}{EC}(Who do they think I  am! The family dog!?) 
<Game> The kitchen. 
Today's dinner is pasta carbonara! 
They don't even make it this good in Italy! 
<Game> The kitchen. 
Today's dinner is steak and green beans. 
The price of beef went up this week. In other words, the steaks are too high... 
Haha... 
