<Geo> It's still too early to go to sleep. 
<Game> It's a TV. 
There's an older video game console connected to it. 
<Geo> Maybe I'll get a new system for my birthday? 
<Game> It's a control panel. 
<Game> It's a desk. 
Doing homework on this desk will help the student finish three times quicker... 
Psyche! 
<Game> It's a bookshelf. 
It's full of video games and comic books. 
<Game> It's a baseball glove and ball. 
<Geo> {13}{EC}(Dad gave these to me...) 
{13}{EC}(I'll always keep them safe.) 
<Game> It's a poster of a space shuttle. 
<Game> It's a poster of the Pleiades star cluster. 
It's also known as the "Seven Sisters". 
<Game> It's a globe. 
<Mega> Muwahaha... One day this planet will be mine! 
<Geo> A-Are you being serious...!? 
<Game> It's a telescope. 
It's a pretty popular model among space lovers. 
<Game> The weather is nice today. 
<Game> It's a meteorite. 
<Geo> Isn't this awesome!? It's the real thing, too! 
<Mega> {13}{EC}(Are you really going to  brag about something  like that to an AM-ian?) 
<Game> It's a garbage can. It's easy to throw garbage in it since it's in the corner. 
<Game> It's a poster of the famous baseball player, Ando Ryuu. 
<Game> It's a dresser. Is there anything hidden behind the drawer? 
Nope. 
<Game> There's a big closet inside. It's full of a bunch of useless stuff. 
<Game> A book that's been scribbled all over has fallen down. 
Title: "Baseball and Space". 
<Mega> What kind of book is this? 
<Mega> Call it quits for the day? {05}{EC}{00}{00}{02}{00}    {06}{EC}Sleep    {07}{EC}Don't sleep 
{11}{EC}{00}{00}{12}{00}
