<Game> A communication area. 
It's a place where people can trade Battle Cards and form Brother Bands. 
If one looks very closely there is a price tag on it! 
"Friends...{16}{E1}     {15}{E1}.{15}{E1}.{15}{E1}.{15}{E1}Priceless." 
<Game> It's a display case with rare cards specially arranged. 
<Game> It's a register. 
<Geo> Come to think of it... I don't think I've ever seen Mr. Suther use it. 
<Game> Normal cards are lined up pretty normally. 
<Game> The palm tree looks real... 
#It IS real! 
Those trees grow crazy fast if you plant one of the seeds! 
<Game> It's a life-sized cut-out of Mr. Suther. What a smile... 
<Game> It's a hand-made speaker. 
The dried wood of a certain southern tree makes for a fantastic sound. 
<Game> It's a life-sized carving of a sea turtle. It's too big to move. 
There is a majestic feeling about him. 
<Game> Expensive looking items are eloquently displayed. 
#Welcome! We have lots of awesome stuff for sale! 
{0C}{E1}{01}{00}{B9}{00}{12}{00}{06}{E1}{13}{00}
#Welcome! We just got a ton of really sweet new stuff in stock! 
{0B}{E1}{7A}{02}{0C}{E1}{01}{00}{B9}{00}{12}{00}{06}{E1}{13}{00}
#We can also order stuff from other stores if you want! 
But it costs an extra 20% for the delivery charges. 
Use the service? {05}{EC}{00}{00}{0D}{00}   {06}{EC}Shop here    {09}{EC}Use the service 
#I'm sorry, but that is still out of order. 
It should be ready to go in no time. Please wait patiently. 
<Geo> Whoa, it's "{94}{E5}"! 
Geez, that's expensive! It's 5000 Zennys! Should I buy it? 
<Game> Buy it? {05}{EC}{00}{00}{04}{00}  {06}{EC}Buy   {09}{EC}Don't buy 
{11}{EC}{00}{00};{11}{EC}{03}{00}=
<Geo> Doh... I don't haven enough Zennys. 
<Game> {35}{EC} got: "{94}{E5}"! 
{81}{E1}{78}{EC}
<Geo> Maybe I should hold back from spending my money. 
<Game> I can't buy stuff looking like this! 
<Game> The palm tree looks real. 
