<Game> It's the Science Club's Rocket! 
<Game> It's some serious-looking equipment. 
<Game> It's the Science Club's mascot, "Hugh Maan". 
*gasp* 
<Mega> H-Hey, kid! D-Did his eyes just move!? 
<Geo> It's one of the seven wonders of Echo Ridge Elementary! 
<Game> It's some serious-looking equipment. 
<Geo> The Science Club Room is kind of a cool place... 
<Game> It's a bulletin board with experiments scheduled on it. 
<Game> "Warning: Flammable!" "Warning: Do Not Mix!" "Warning: Do Not Shake!" 
<Game> "Experiment in Process!" "Do Not Touch!" 
<Mega> {13}{EC}... 
{13}{EC}Oh man, soooo tempting... 
<Game> It's a case filled with strange looking things. 
Moth specimens are being displayed on the monitor. 
<Game> It's a blackboard. 
A blue print for the rocket is on it. 
<Game> It's a teacher's desk. 
<Game> Cables and other electronic equipment have been carelessly thrown in the box. 
<Mega> Hey! Look what's in there! 
{85}{E1}{00}{00}{01}{00}{A1}{E1} 
<Game> {35}{EC} got Power Up Ability: "{E0}{E5}"! 
HP capacity has been increased! 
{0A}{E1}{E4}{00}
<Game> It's a bunch of pretty technical-looking parts. 
<Game> The rocket's blueprint is spread out on the floor. 
Propulsion. Payload weight. Burn time. 
<Game> The rocket's blueprint is spread out on the floor. 
<Game> The rocket is gone... Was it stolen!? 
<Geo> It looks like it was already taken to the roof! 
{09}{E1}{00}{00}{CF}{06}{DB}{06}{11}{00} 
<Mega> Let's get there ASAP, kid! It's going to be so cool to watch! 
<Game> It's a case filled with strange looking things. 
Moth specimens are being displayed on the monitor. 
{00}{E2}<Solo> {00}{00}{04}{00} 
<Geo> Is this the moth specimen that that teacher mentioned? 
<Mega> That kind of stuff creeps me out! 
<Game> Cables and other electronic equipment have been carelessly thrown in the box. 
