<Game> The glory of the school's past is on display. 
"Nation-Wide Elementary School Egg Cracking Competition Champions!" 
"We did our best to make our principal proud!" 
Legend has it that once night falls, the number of trophies increases by one. 
<Geo-2> It's one of the seven wonders of Echo Ridge Elementary! 
<Game> The cafeteria area is one the most relaxing areas... 
...Until lunch time hits, then all heck breaks loose! 
<Game> It's full of ice-cold milk. 
There's chocolate milk, too! 
<Game> "Study hard,  eat right,  sleep tight." 
<Game> It's a statue of the first principal of Echo Ridge Elementary. 
It looks like the beard is growing... slightly. 
<Geo-2> It's one of the seven wonders of Echo Ridge Elementary! 
{0C}{E1}{01}{00}{B1}{13}<Geo>
<Game> It's the faculty room. 
It's too scary to even think about going in there. 
<Game> It's the control panel for the bulletin board. 
<Geo> I'll get yelled at by the teachers if I mess with it. 
<Game> It's a bulletin board. 
<Game> The elevator goes to the second floor and the roof. 
<Game> The weather is really nice. 
<Game> A map of the school is displayed. 
The red spot marks where you currently are. 
<Game> The elevator goes to the second floor and the roof. 
<Game> A row of potted plants that have beautifully bloomed. 
The students take turns watering it. 
<Game> It's the school store. 
"The popular Mega Snacks are now 10 Zennys each!" 
,Hello there... I'm sorry but we're all sold out! 
A man in white with long hair bought them all! 
<Game> It's the entrance to the school store. 
No one has ever seen the store lady use it. 
<Geo-2> It's one of the seven wonders of Echo Ridge Elementary! 
<Game> It's the school store. 
"The popular Mega Snacks are now 10 Zennys each!" 
,Hello there... We've got Mega Snacks! 
<Game> It's the school store. 
"The popular Mega Snacks are now 10 Zennys each!" 
,Hello there... We've got Mega Snacks! 
That handsome man in white hasn't come around lately. 
He really brightens my day... 
<Game> The <Hunter>-VG is reacting! 
NOISE WAVE DETECTED. {15}{E1}.{15}{E1}.{15}{E1}.{15}{E1}ACCESSED! 
{0A}{E1}{82}{13}{0A}{E1}p
<Game> The milk isn't ice-cold! 
<Geo> Maybe Noise had a bad effect on it... 
,This thing isn't working so well all of a sudden. 
Hmm... It's really noisy, too. 
I wonder if something happened to it? 
<Game> The elevator isn't working! 
<Geo> It looks like it broke down from the effects of Noise! 
,Lunches? OK, three, right? 
{A1}{E1} 
<Game> {35}{EC} got: "Lunches"! 
<Geo> Nice. Now I just have to get these to the staff. 
,What a good kid you are for helping them out. 
<Game> It's the school store. 
"The popular Mega Snacks are now 10 Zennys each!" 
<Game> The milk isn't ice-cold! 
<Megaman> Maybe Noise had a bad effect on it... 
<Geo> Solo... I can't believe he would just blow a hole through the wall like that. 
<Mega> You know... Maybe you could learn a thing or two from him. 
