<Game> Cockle-doodle-doo!! 
<Game> It's the roof garden. 
Radishes and strawberries are being grown in it now. 
<Game> It's a basketball hoop. 
The ball mysteriously returns by itself, even if it falls off the building. 
<Geo-2> It's one of the seven wonders of Echo Ridge Elementary! 
{0C}{E1}{01}{00}{B1}{13}{0F}{00}
<Game> It's a projector that projects Real Waves, creating the nearby tree. 
<Game> It's a Real Wave tree. 
<Game> It's a real evergreen tree. 
<Game> The Sprinker is attacking Woody with crazy force! 
<Game> *crackle, crackle* 
<Woody> Argh! *cough, gasp* 
<Game> Some gourds... 
Who knows how big they will get!? 
<Game> It's a paper airplane that landed here. 
It looks like it would fly very far if someone were to throw it into the wind. 
<Game> The <Hunter>-VG is reacting! 
NOISE WAVE DETECTED. {15}{E1}.{15}{E1}.{15}{E1}.{15}{E1}ACCESSED! 
{0A}{E1}{8E}{13}
<Game> It's a basketball hoop. 
The ball mysteriously returns by itself, even if it falls off the building. 
<Geo-2> It's one of the seven wonders of Echo Ridge Elementary! 
<Mega> {13}{EC}(For a second there {13}{EC} I felt a really strong {13}{EC} Noise presence...) 
Hmm, it must have just been my imagination... 
<Game> It looks like a tree... But something about it feels strange. 
<Game> The sprinkler is going out of control! 
<Mega> It must be a virus's doing! Let's check out the sprinkler's Cyber Core! 
<Game> The sprinkler isn't working at all. 
<Geo> There's definitely something wrong with it. We better check out its Cyber Core. 
<Game> The wall has writing on it. "The school is done! Yahoo!" 
<Geo> Ah, I found the graffiti! I better remove it. 
<Game> *scrub, scrub* 
<Geo> It's nice and clean now. 
