<Game> It's a route map for the Wave Liner. 
<Mega> Sweet! We found something good! 
{84}{E1}{02}{00}{01}{00}{A1}{E1} 
<Game> {35}{EC} got Sub-Card: "{D2}{E5}"! 
{0A}{E1}{F6}{00}
<Game> It's the <Spica.Mall> mascot, "Spimo the Cat". He almost looks like he wants to say 
something... Like, "What up!? This is the famed <Spica.Mall>! Check it out!" 
<Game> It's an advertisement for "<Hunter>-VGs". 
{0C}{E1}{01}{00}{B1}{13}<Geo>
<Game> It's a dentist office... 
<Geo> ... 
{13}{EC}(My molar is definitely {13}{EC} not hurting at all.) 
{13}{EC}(Definitely not at all!!) 
<Game> "We're always closed!    This restaurant is       Good for nothing!" 
<Geo> Nice slogan they got there. 
<Game> It's a poster of <Spica.Mall>'s mascot, Spimo the Cat. 
If it could talk, it would probably say... 
"What up!? It's shopping everyday for everybody here at Spica Mall!" 
<Mega> Nice! Look what I found! 
{85}{E1}{00}{00}{01}{00}{A1}{E1} 
<Game> {35}{EC} got Power Up Item: "{E0}{E5}"! 
HP capacity has been increased! 
{0A}{E1}{EE}{00}
<Game> It's the men's bathroom. 
{0C}{E1}{01}{00}{B1}{13}{0F}{00}
<Game> It's a control panel for the security system. 
<Geo-2> It's no good! It won't budge! 
Let's have a look in the Cyber Core of the security system! 
<Game> It's a projector. 
<Game> <Hunter>-VGs are lined up in front of the store. 
Nowadays, it is almost impossible to live without having one of your own. 
It has truly become an EM wave society. 
<Game> The <Hunter>-VG is reacting! 
NOISE WAVE DETECTED. {15}{E1}.{15}{E1}.{15}{E1}.{15}{E1}ACCESSED! 
{0A}{E1}{8F}{13}
<Game> It's the women's bathroom. 
<Game> The <Hunter>-VG is reacting! 
NOISE WAVE DETECTED. {15}{E1}.{15}{E1}.{15}{E1}.{15}{E1}ACCESSED! 
{0A}{E1}{83}{13}{0A}{E1}q
<Geo> Ah, it's "{93}{E5}"! 
5000 Zennys!? That's crazy expensive! Should I buy it? 
<Game> Buy it? {05}{EC}{00}{00}{04}{00}  {06}{EC}Buy it   {09}{EC}Don't buy it 
{11}{EC}{00}{00}<Heartless> {11}{EC}{03}{00}"
<Geo> *sigh* I don't have enough Zennys. 
<Game> {35}{EC} got: "{93}{E5}"! 
{81}{E1}{78}{EC}
<Geo> I really don't need to right now. 
<Game> The wall has writing on it. "The mall is done! Yahoo!" 
<Geo> Ah, I found the graffiti! I better remove it. 
<Game> *scrub, scrub* 
<Geo> It's nice and clean now. 
<Geo> *heart pounding* If I just knock three times and chant the spell... 
<Game> *knock* {15}{E1}*knock* {15}{E1}*knock* 
<Geo> That should do it. 
... 
... 
Nothing's happening. 
<Mega> Shhh... I can hear something, kid. 
<Geo> ...? 
... 
... 
<Game> Play {16}{E1}with {16}{E1}me... 
<Geo> Aaahhh! 
<Mega> They're here! 
<Geo> Nothing's happening. The spell must be wrong. 
<Game> It's a poster of Spica Mall's mascot, Spimo the Cat. 
If it could talk, it would probably say... 
"What up!? It's shopping everyday for everybody here at Spica Mall!" 
<Game> It's a route map for the Wave Liner. 
