<Geo> Hmm, is this a shopping basket? 
<Game> There are various candies on display... 
<Mega> Oh, that's... 
<Geo> Mega Snacks. Ace loves them! 
This candy shop is great! They have every flavor! 
<Mega> Which would you recommend? 
<Geo> I like them all, but... Pepperoni pizza is the best. 
<Mega> Taco cheese sounds really good to me! 
<Game> It's a game where you can win gifts. 
The poster of Sonia isn't related at all. 
{0C}{E1}{01}{00}{B1}{13}
<Game> There are various candies on display... 
<Mega> Jalapeno chocolate... California roll... Steak sandwich... 
There are so many different flavors to choose from! 
<Geo> Candy shops are the best place to find a wide variety of different flavors! 
<Game> "Bubble Gum Lottery   Red... Fail   Blue... Too Bad 
  Yellow... Sorry!" 
<Mega> Come on, gimme a break! 
<Game> It's a strange, yet relaxing sight. 
<Game> It's a register that's been used to death. 
There's an abacus by it. 
<Game> The cooler is jam-packed with ice cream. 
They'll be staying nice and cold even if the cooler stops working! 
<Game> The <Hunter>-VG is reacting! 
NOISE WAVE DETECTED. {15}{E1}.{15}{E1}.{15}{E1}.{15}{E1}ACCESSED! 
{0A}{E1}{85}{13}{0A}{E1}s
<Game> The entrance to the Noise Wave is open. 
<Game> It's a bubble gum machine. 
<Mega> It's not working right! We better check out its Cyber Core! 
<Geo> There're a ton of different flavors of ice cream, huh? This one looks pretty good. 
<Game> Buy ice cream? (50 Zennys) {05}{EC}{00}{00}{04}{00}  {06}{EC}Buy   {09}{EC}Don't buy 
{11}{EC}{00}{00}{12}{00}{11}{EC}{03}{00}<Geo>
<Geo> *sigh* I don't have enough Zennys. 
<Game> {35}{EC} got: "Ice Cream"! 
<Geo> I have to get the ice cream to her before it melts! 
<Game> Time limit: 3 minutes. 
<Geo> Maybe I should hold back from spending my money. 
