<Game> It's a plant. It's hard to tell what species it is. 
*Welcome to <Studi.WBG>! 
This is where TV shows for lucky channel 77 are filmed. 
<Game> It's a sculpture based on the logo of <Studi.WBG>. 
{0C}{E1}{01}{00}{B1}{13}<Geo>
<Game> "Saturday at 9pm! Sonia Strumm stars in Song of Dreams!" 
<Geo> Wow, an ad for Sonia's new TV show. Amazing, Sonia... 
<Game> It's a machine used for editing recorded video. 
<Game> It's a big mirror. Don't forget to do a quick check... 
<Game> A bunch of metal chairs are lined up. They look like they've been used a lot. 
<Game> Several of Sonia's outfits. They're all so cute. 
<Mega> Hey, kid. Want to try one of them on for fun? 
<Geo> ...I'll pass, thanks. 
<Game> Bouquets of flowers. Sonia has received quite a few from her fans. 
<Game> Make-up equipment is nicely arranged. How much of this stuff is necessary? 
<Geo> Ah! This is...! 
{80}{E1}{81}{00}{01}{00}{A1}{E1} 
<Game> {35}{EC} got Battle Card "{C1}{E7}"! 
{0A}{E1}{F1}{00}
<Game> It's a cabinet with various props stored in it. It's locked tight. 
<Game> It's a really gaudy arch. It's used as a set piece in different talk shows. 
<Game> It's a large lighting rig. It must drain a ton of electricity. 
<Game> "Editing Room" 
<Game> "Event Stage Ahead" 
<Game> "Waiting Room" 
<Game> "Set Piece Warehouse" 
<Game> The door is frozen shut! 
<Game> The <Hunter>-VG is reacting! 
NOISE WAVE DETECTED. {15}{E1}.{15}{E1}.{15}{E1}.{15}{E1}ACCESSED! 
{0A}{E1}{90}{13}
<Game> It's a cabinet with various props stored in it. 
There are spiders, snakes, and other creepy crawlies... 
<Geo> Wow... They sure have a bunch of random props... 
<Game> It's a cabinet with various props stored in it. 
{00}{E2}<Solo> {00}{00}{04}{00} 
<Game> It appears that the electronic locking mechanism is malfunctioning. 
<Geo> It's not working right... I should go check out the Cyber Core! 
<Game> Make-up equipment is nicely arranged. How much of this stuff is necessary? 
<Game> It's the reception desk for <Studi.WBG>. 
