<Game> It's a stand that sells an Alohahaian pork delicacy. A pig head is sitting there... 
<Geo> Wh-Whoa! Craaazy! 
<Game> It's a stand that sells bitter melon burgers. Many people love the unique flavor. 
<Geo> Huh? What's with the menu? 
<Game>   "Delta86531" 
<Mega> That doesn't sound like food... 
<Game> It's a stand that sells ice cream made from a rare fruit native to Alohaha. 
<Game> It's a stand that sells special Alohahaian doughnuts. They're awesome! 
<Game> It's said that when this boat departs for sea, the island's Real Wave dissappears. 
{0C}{E1}{01}{00}{B1}{13}<Geo>
<Game> The <Hunter>-VG is reacting! 
NOISE WAVE DETECTED. {15}{E1}.{15}{E1}.{15}{E1}.{15}{E1}ACCESSED! 
{0A}{E1}{9B}{13}
<Acid> Luna Frag discovered. Recovering now. 
{0A}{E1}*{82}{E1}{02}{00}{01}{00}{02}{E2}L{A1}{E1} 
<Game> {35}{EC} got: "{72}{E5}"! 
{01}{E2}L 
<Geo> Nice! 
<Game> The <Hunter>-VG is reacting! 
NOISE WAVE DETECTED. {15}{E1}.{15}{E1}.{15}{E1}.{15}{E1}ACCESSED! 
{0A}{E1}{91}{13}
<Game> It's 100% mango juice. It's filled with healthy vitamins. 
+I'm not sure why, but it's out of order right now. 
Sorry. 
<Game> It's 100% mango juice. It's filled with healthy vitamins. 
<Game> It's a palm tree that's the result of selective breeding. 
<Mega> It sure looks sturdy! 
<Game> Fully bloomed hibiscus. These flowers represent the spirit of the tropics. 
<Geo> A {95}{E5} is on the ground. Let's take one. 
{0A}{E1}{5E}{16}{82}{E1}%{01}{00}{A1}{E1} 
<Game> {35}{EC} got: "{95}{E5}"! 
<Mega> Hey, isn't that a "{96}{E5}" plant? Let's take a flower! 
<Geo> I don't want to hurt the plant, Mega. I'll just take a flower that has fallen off. 
{0A}{E1}{5F}{16}{82}{E1}&{01}{00}{A1}{E1} 
<Game> {35}{EC} got: "{96}{E5}"! 
+Oh, are you looking for a health drink? 
Unfortunately, I can't make one unless you bring me all of the ingredients necessary. 
<Geo> OK, then I'll go find them! 
+In that case you'll need the following... 
A {95}{E5}, a {96}{E5} flower, and some {97}{E5}. 
<Geo> OK! I'll be back ASAP! 
+Bring back a {95}{E5}, a {96}{E5} flower, and some {97}{E5}. 
<Geo> I brought the ingredients. 
+Nice. Give me a few minutes to make it for you. 
First I do this, then mix, then wring it out... 
{A0}{E1}{03}{00}x 
+The last step is to shake it vigorously, but no stirring! 
{A0}{E1}{01}{00}{00}{00} 
+Ta-da! All done! 
{0A}{E1}{61}{16}{82}{E1}({01}{00}{A1}{E1} 
<Game> {35}{EC} got: "{98}{E5}"! 
<Geo> Thank you very much! 
Time to take this to Woody. 
+Don't drink too much. 
<Game> There's something written on the wall... 
"Repairs complete! Yahoo!" 
<Geo> Ah, I found the graffiti! I better remove it. 
<Game> *scrub, scrub* 
<Geo> It's nice and clean now. That should have been the last of it. I'll go tell him now. 
