<Megaman> Whoa... Where are we? 
There're stars everywhere... I've never seen a place like this before. 
<Mega> I'm sensing that we've left the solar system, and 
are actually in the center of our galaxy. 
Your scientists would call it "deep space". 
Strangely enough, something here seems familiar to me. 
...Huh? 
<Mega> I remember now! 
This is where Kelvin and his team built the communications Wave Road to <Pianeta.FM-color>! 
This EM wave tower has seen better days, but there is no doubt about it. 
This Wave Road leads to Planet FM! 
<Megaman> ...Mega! That's terrible! 
<Mega> Huh? What is? 
<Megaman> Think about it. 
We got here by following the path the "R" guys traveled... 
That means that the planet that they and their leader are invading is Planet FM... 
<Game> So you've finally made it this far... 
<Megaman> !! 
<Mega> Whoever is speaking has a very strong presence, kid! 
It could be an "R" guy... 
Or maybe their leader! 
<Megaman> ... 
<Mega> You guys!? 
<Megaman> You're the <3.Saggi.di.AM-color>! 
{81}{00}Omega-Xis... We don't appreciate you treating us like enemies. 
<Mega> I can't help it when you look like you guys do! 
{82}{00}Moving on... Geo Stelar... Mega Man... 
<Megaman> Yes? 
{83}{00}It's just as you guessed. 
Planet FM is currently on the brink of destruction. 
{81}{00}Your Brother, <Cepheus-color> the FM King, is fighting for 
his life along with the other FM-ians. 
Things are not looking good. 
<Megaman> Cepheus... 
So that means that the Astro Hertz who came to Earth was sent to find us... 
<Mega> And you guys must be on your way to help, right? 
{82}{00}If we could help, we would of course do so... 
However, the enemy has placed an EM barrier around the whole planet. 
We can't get through to join the battle. 
<Megaman> I can't believe that there's a barrier that the 3 Sages of <Pianeta.AM-color> can't get past. 
Do you know who the leader of those "R" guys is? 
Please tell us if you do! 
{83}{00}His name is "Sirius". 
<Megaman> "Sirius"... 
{83}{00}The data on him is very scarce. 
<Mega> We heard something about him wanting to destroy everything... 
{81}{00}Yes... 
Sirius has the ability to control black holes. 
<Megaman> Black holes!? 
{82}{00}Any planet that is targeted by Sirius will be swallowed up 
by a black hole, completely disappearing from existence. 
<Mega> A black hole isn't something that is normally controllable, is it? 
{83}{00}No, however, Sirius is capable of doing so. We have no idea how he does it though. 
<Megaman> What can we do to stop a black hole? 
{83}{00}Unfortunately... We have no idea. 
<Megaman> I see... 
{81}{00}Yet, there is one thing that we can tell you. 
A very powerful EM being that is not of the title "R" was spotted near Planet FM. 
Currently, its whereabouts are unknown. 
{82}{00}It may have been carried away by a Noise stream... 
That being was more powerful than anything you have fought in the past. 
{83}{00}Be careful to not be taken by surprise while focusing on Sirius and the "R"s. 
<Megaman> Thank you! I'll be careful! 
{81}{00}The FM King... Cepheus is fighting, expecting you to come to his aid. 
<Megaman> I understand. I'll do whatever it takes to help a Brother! 
{82}{00}Omega-Xis... Geo Stelar is in your hands... 
<Mega> I already know that! 
And I'm going to go extra buck wild to make up for you guys not coming! 
{83}{00}Good... We are counting on you, Mega Man... 
<Mega> So this guy can control black holes, huh? 
We can't let a guy like that get away! 
Come on, kid! 
<Megaman> OK! We'll rescue you Cepheus... And Planet FM! 
