<Apollo.Flame> H-How could I lose twice? 
Is the universe saying that it would rather have Sirius rule instead of me? 
...It can't be...{14}{E1} But it is...! 
Muwahahaha!! 
...If that's the case! Then I'll... let you through! 
Siri...{14}{E1}us will have... {14}{E1}an audience... with you... in 
the... inescapable depths of his... {14}{E1}black hole! 
<Game> Aaaaaarrrgh!! 
<Megaman> We... won. 
<Mega> That was a close one. 
<Megaman> I don't want to compliment him, but he sure was strong. 
<Mega> Yeah, I don't think that there is anyone stronger than that guy was. 
<Game> That may be true... 
But it was his pride that made him such a difficult pawn for me to control. 
<Mega> Who is that!? 
<Megaman> ...Sirius!? 
<Game> Gahaha... 
<Megaman> Show yourself! 
<Game> Gahaha... 
Before that... I'd like to congratulate you, Mega Man. 
I was very interested in your profile data when I found it in Meteor G. 
Its analysis of your abilities was right on the mark. 
However... The trials ahead will push you to your limits. 
If you were to make it all the way to me... 
I would be most impressed. 
And I would be thrilled to add you to my collection. 
...But for now, adieu. 
<Megaman> Wait! I said show yourself! 
<Mega> .{14}{E1}.{14}{E1}.{14}{E1} 
Don't bother, kid. He's already gone. 
<Megaman> I bet that was Sirius... 
<Mega> Possibly. 
The way he talked made it seem like he looks down on everyone... 
That really ticks me off! 
<Megaman> I wonder what someone who talks about Apollo Flame like that is like? 
