<Megaman> So... Are we finally there? 
<Mega> Yeah. Over there is Planet FM. 
And Sirius's Black Hole Server... 
<Megaman> It's right on top of it! 
<Megaman> We have to get there ASAP! 
<Mega> Definitely. This Wave Road should lead to the server's entrance. 
<Game> Geo, my Brother. You really came... 
<Megaman> That voice...!{15}{E1} Is that you, Cepheus!? 
<Megaman> Cepheus! Are you OK!? 
<Mega> Good to see you, FM King! 
<Cepheus> Thank you very much for coming all this way. 
<Megaman> It's not a problem. 
Brothers do whatever it takes to help out when their Brothers are in trouble. 
<Cepheus> Geo... You're always teaching me more and more about life. 
<Mega> ...Heh, it looks like you've softened up a bit. 
But anyway, what's the situation looking like? 
Is there some way to stop the black hole? 
<Cepheus> We've tried everything within our arsenal. 
Nothing has had an effect on the black hole. 
<Mega> What about that super powerful weapon that the government was working on? 
<Cepheus> You mean the Ultimate Wave Force Missile. It had little to no effect. 
<Mega> Geez! 
Well, did you sortie the defense troops for an attack on the core? 
<Cepheus> Yes. They were completely wiped out... 
<Mega> What!? That's...! 
<Cepheus> There is nothing we can do. 
According to our analysis... We have exactly one day 
before Planet FM is swallowed by the black hole. 
I have just ordered every citizen of Planet FM to 
board our resonance rockets for evacuation. 
Geo...{15}{E1} Thank you for coming, but... Please return to Earth. 
<Megaman> !! 
<Mega> FM King! 
<Cepheus> Sirius and his black hole are just too much. 
Losing one's home is a tragic event. 
Yet, as king, my first duty is to keep my people safe. 
I share the same duty to you, as your Brother. 
<Megaman> ... 
.{14}{E1}.{14}{E1}.{14}{E1}One day, right? 
<Cepheus> Geo? 
<Megaman> What if we could stop Sirius and his black hole within one day? 
<Cepheus> Don't even think about it! My decision has been made, and that's final! 
<Megaman> I understand. ...But I can't accept what Sirius is doing! 
He has no right to do this to you and your people! 
<Mega> I'm with the kid on this one! 
There's no way I can just sit around and watch my home planet be destroyed! 
<Cepheus> Geo... Omega-Xis... 
<Megaman> Mega and I are going into the black hole. 
And we'll defeat Sirius! 
...But I can't promise that Planet FM will be saved from being swallowed up. 
So please continue with your evacuation plans, Cepheus. 
<Cepheus> Geo...{15}{E1} I don't know what to say... 
<Megaman> ... 
Just tell me that you believe in me. A Brother's trust is invaluable. 
Cepheus, please head back! We'll take care of this. 
<Cepheus> ... 
I believe in you, Mega Man. 
As a Brother... And as a representative of Planet FM. 
<Megaman> Mega... 
Do you know how I feel right now? 
<Mega> Of course... You seem unusually angry and ready for a fight. 
<Megaman> I guess you know me well. 
So why don't you get fired up with me!? 
Let's rock, Mega! 
<Mega> Yeah! But how about a little blues every once in a while!? 
