<Megaman> Mega! 
<Mega> Nice! We found it! 
<Megaman> Yeah! That should be the entrance to the Black Hole Server! 
<Mega> Sirius is most likely inside... 
<Megaman> We have him now! 
Here we go! 
<Rogue> ... 
<Megaman> Rogue! Why are you here!? 
<Rogue> ...I'm here for Sirius. 
{B1}{00}Gzzzt... 
<Megaman> I have no idea how you even know about him, but let's team up to get him! 
<Rogue> No... 
You are going to fight me... 
<Megaman> What? Why?{16}{E1} But I'm trying to stop Sirius too. 
If we were to combine our powers... 
<Rogue> Hmph... Not that talk about bonds, again... 
Maybe you'll understand once you hear this. 
I'm waiting to stop Sirius... {16}{E1}Two days from now. 
{13}{E2}{03}{00} 
<Megaman> Huh? 
<Mega> That's too late, kid! Planet FM will be destroyed before then! 
<Megaman> What are you up to, Rogue? 
<Rogue> I'm going to take back the Mu Metal that Sirius stole. 
<Mega> Why do you have to wait two days to do that? 
<Rogue> Because the Mu Metal has been absorbed into Sirius. 
And it rises out of his body in the shape of a crest, on a cyclical basis. 
The current cycle will end in two days... 
I'm going to defeat him, and take back the Mu Metal. 
<Mega> What happens if you delete him before then? 
<Rogue> Then the Mu Metal will be lost forever along with him. 
<Megaman> That Mu Metal is very important to you, isn't it? 
<Rogue> Yes. It's something that I must get back for myself... 
For my people... 
<Rogue> If the Mu Metal were fused with the edge of the Laplace Blade.{15}{E1}.{15}{E1}.{15}{E1} 
<Mega> ...? What would happen? 
{B1}{00}Brzzzt... 
<Rogue> Good point, Laplace. 
It's not necessary for you to know. 
<Megaman> .{15}{E1}.{15}{E1}.{15}{E1} 
<Rogue> Anyway... As long as you try to keep moving ahead... 
I will have to stop you. 
So, what do you think? 
Do you think you can beat me to get to Sirius? 
<Megaman> .{15}{E1}.{15}{E1}.{15}{E1} 
<Rogue> Planet FM or Mu... Which one can be saved? 
{B1}{00}Rzzzt... 
<Mega> ... 
<Megaman> .{15}{E1}.{15}{E1}.{15}{E1}Rogue... 
I'm going to defeat you...{14}{E1} And honor my...{16}{E1} Promise to Cepheus. 
<Rogue> Hmph... 
It looks like you've learned to make decisions like a man. 
<Megaman> Words and feelings aren't always enough to ensure peace and safety. 
Sometimes you have to risk your life to get them... 
I learned that from Dad, Ace, and Mega... 
And even from you, Rogue. 
<Rogue> Even from me...? 
<Megaman> You don't recognize or try to form bonds with the people of today. 
But you hold your bond to Mu very dearly in your heart. 
It doesn't matter what's in your way, you will risk your life to protect that bond. 
<Rogue> .{15}{E1}.{15}{E1}.{15}{E1} 
<Megaman> Of course, people nowadays don't understand about Mu, 
so you've been driven to protect your bond by some not so nice means... 
<Rogue> Don't you dare act like you understand me. 
I'm going to delete you because it will be fun. 
{B1}{00}Dzzzt... 
<Rogue> Shut up, Laplace. 
<Megaman> .{15}{E1}.{15}{E1}.{15}{E1}Rogue{15}{E1}... I see. 
There's no way that our feelings about bonds will ever coincide. 
But if we are both people who truly respect our bonds with others... 
Then we will both be willing to fight to protect them. 
<Rogue> Exactly... 
It would be ideal to protect your own bonds without harming anyone else's. 
But life is not that simple and easy. 
<Megaman> That's why I must protect my bond with Cepheus! 
I understand your situation, Rogue. But Cepheus 
entrusted me with the fate of his people! 
<Rogue> Then let it begin...{15}{E1} Mega Man. 
This is...{15}{E1} A fight for honor... 
<Megaman> I'm going to win, Rogue! 
Wave Battle! Ride On!! 
