<Sirius> Gahaha... 
Welcome, Mega Man. 
<Megaman> So you're Sirius!{15}{E1} How dare you... 
<Sirius> It has been a long time since I last had a guest. 
Oh, about... 100 years or so.{15}{E1} Yes, that sounds right. 
<Mega> Hey! Stop talking to yourself and pay attention for once!! 
<Sirius> ... 
I don't need that rude EM being for my collection. 
Mega Man will look much better on my shelf. 
So, Mega Man... Stand still, please. It's time to remove your will. 
Then we'll get you started battling with all sorts of fun EM beings...{16}{E1} 
Your battles are always so enjoyable to watch! 
<Mega> He wants to make us his toys... 
This guy... {15}{E1}is insane. 
<Megaman> I'm not letting you get anywhere near me! 
I'll make you pay for what you have done, Sirius! 
<Sirius> Oh! {14}{E1}Fantastic!{15}{E1} I just thought of something! 
Let's set Planet FM as your first battle stage! 
Do me a favor and go as "buck wild" as you like. 
I was hoping to enjoy watching everyone on the planet panic for a bit... 
But I suppose destroying it outright would be fun too. 
There are so many planets for me to play with. 
<Megaman> Peoples lives... Planets... They aren't toys for you to play with. 
Have you even considered the pain you are putting all 
those people down there through? 
<Sirius> Everything here will cease to exist. 
A black hole has no need for such things as emotions. 
You should... be happy. 
You will live forever within the darkness. 
You will be mine. 
<Megaman> I wouldn't call that living! 
I'd rather not exist! 
<Sirius> .{15}{E1}.{15}{E1}.{15}{E1}I see. Do you think that you might change your mind? 
Stopping you without causing you any injury would be a bit of a nuisance for me. 
It will be hard for us to play together with you injured. 
<Mega> Do you ever shut up!? You don't stand a chance against us! 
<Sirius> I have full control over all aspects of this server. 
You do realize that, right? 
That gives you absolutely no chance of stopping me. 
.{15}{E1}.{15}{E1}.{15}{E1}But I suppose some children need to be punished in order to learn their lesson. 
<Mega> Here he comes, kid! 
<Megaman> I'm ready! This fight...{16}{E1} Is ours!! 
Last Battle!{14}{E1} Ride On!! 
