<Sirius> I... I...{15}{E1} Like this... 
...There are... ways... To go... 
...However, Mega Man... 
You are still but an inch away from deletion. 
<Megaman> !? 
<Sirius> All of my EM powers are being transmitted... 
To another server. 
To that...{15}{E1} server! 
<Mega> For cryin' out loud! Just give it up, already! 
<Sirius> When the five stars shine together...{15}{E1} 
You two and Earth will see your final days! 
...And for extra fun...{16}{E1} 
Here's a gift from me. 
Enjoy fighting with that rival of yours for all of eternity! 
<Megaman> What are you talking about!? 
<Sirius> Gahaha...{16}{E1} Goodbye, Mega Man! 
<Game> Aaaaaahhhhhh!! 
<Mega> ... 
<Megaman> I just felt something...{15}{E1} Leave Sirius... and enter my body... 
<Mega> Yeah, I can feel it. 
It looks like we got ourselves into another mess! 
<Megaman> But what is... 
<Game> Interesting... I didn't expect things to work out like this. 
<Rogue> Mega Man... 
The Mu Metal was transferred from Sirius to you. 
<Mega> *sigh* 
Is this what he meant about battling a rival for eternity? 
<Megaman> Rogue... Are you going to try to delete me? 
<Rogue> I do have one more reason to do so, now. 
<Megaman> ... 
<Rogue> However...{15}{E1} I'm in no hurry. 
I can wait until the crest rises up from your body. 
Then I will finish you off. 
For now, you should celebrate your victory over Sirius. 
<Megaman> Rogue... 
<Rogue> We'll see each other again.{15}{E1} For now, I'm gone... 
<Megaman> Someday... Rogue and I... 
<Mega> Are going to have to fight... 
<Megaman> .{15}{E1}.{15}{E1}.{15}{E1} 
<Mega> Hey, hey! Don't get down, kid! 
Let's worry about it when the time comes! 
You... Just defeated Sirius, and saved Planet FM! 
<Game> Yes you did... 
Thank you... Geo. ...I mean, Mega Man! 
<Megaman> Cepheus! 
Is Planet FM OK? 
<Cepheus> Yes. The gravitational pull of the black hole has ceased. 
<Mega> Yeah! We're so...{14}{E1} wait for it... A{14}{E1}-W{14}{E1}-E{14}{E1}-S{14}{E1}-O{14}{E1}-M{14}{E1}-E!! 
<Cepheus> We owe you both a great debt of gratitude. 
Thank you so very much, Geo and Omega-Xis. 
<Megaman> You don't have to keep thanking us. 
If we were ever in trouble, you'd be right there to help. 
<Mega> That's right! So, don't sweat it. 
<Cepheus> You two are something else. 
Geo... It is time for us to part. 
I must return to my people. 
<Megaman> Everyone must be so happy that their king is safe. 
<Cepheus> Healing the people's hearts will prove a more arduous job than repairing the planet. 
<Mega> I know you can do it, FM King. 
<Megaman> There isn't anyone who they look up to more than you. Your bonds are unbreakable. 
<Cepheus> Hearing that from friends is inspiring. Thank you. 
I will do my best. 
And I would also like to strive to bring the relations 
between Earth and Planet FM to a whole new level! 
<Megaman> That's a great idea. I'm looking forward to the day that happens! 
<Mega> Yeah! I would love to be able to visit every once in a while! 
<Cepheus> Geo... Omega-Xis... Thank you, again... 
You've inspired me to be an even better king for my people. 
<Megaman> We'll try to be the best that we can be, too. 
<Mega> Darn straight. 
<Megaman> ... 
<Mega> What's wrong? 
<Megaman> Sirius... Was an EM being that could control black holes... 
He was so powerful. 
<Mega> Yeah... 
But space is pretty big, kid. I'm sure there's someone even stronger out there. 
<Megaman> Yeah, maybe. 
.{15}{E1}.{15}{E1}.{15}{E1}I'm counting on you, Mega. If we ever bump into someone like that... 
<Mega> You don't even have to say it! I'll be there for you! 
And I'm sure we can count on our friends, as well. 
Well, we should get back! 
I really want to figure out just what Sirius meant by... 
"When the five stars shine together..."{15}{E1} 
"You two and Earth will see your final days!" 
<Megaman> Yeah, me too! 
Alright, let's blues, Mega! 
<Mega> You don't miss a beat! 
<Game>   Bonus Chapter     {16}{E1}={16}{E1} E{16}{E1} N{16}{E1} D{16}{E1} ={16}{E1}   
