3I will now explain to you about the White Cards 
which you have downloaded. 
White Cards are the 4 card sets of 
Battle Cards available at every Wave Station. 
Of course, these white colored cards can be used in battle. 
Even the same Wave Station can have different sets of 
White Cards, and some sets are unique to 
Wave Stations in a particular region. 
So, if you see a Wave Station, be sure to download a set. 
If there is ever a White Card that you don't want to use in 
battle, you can go to the Folder Edit Screen, 
select it with the cursor and press the Y Button or the 
A Button to remove it from your folder. 
White Cards will have a "W" mark next to their names. 
This concludes the explanation about White Cards. 
<Mega> OK, before I forget, let me give you a 
quick review of Folders and how they work. 
Folders are containers where you put Battle Cards. 
At the start of a battle, cards picked at 
random are displayed on the bottom screen. 
So whether you're at an advantage or a disadvantage depends 
on what kind of cards you have put into your Folder. 
You can fill your Folder with cards that you find easy to use, 
or you can try to have a more balanced spread of cards. 
It really boils down to your own tastes. 
There's also something called a Card Box that 
is used when you get new Battle Cards. 
By moving cards back and forth between your Card Box and Folders, 
you can determine a Folder's contents. 
But there are rules for putting cards into Folders. 
The first is that a Folder always has to contain 30 cards. 
A Folder can't have more than 5 Standard Class cards of the same name. 
You can put a maximum of 5 rare Mega Class cards in a Folder. 
And for the very rare Giga Class cards, there's a limit of only one. 
Be aware that you can't have more than 1 Mega Class or Giga Class card of 
the same name in a folder. Also, Standard Class cards, 
Mega Class cards, and Giga Class cards aren't the only ones out there. 
There are many different types of cards. 
Man! All this talk about Battle Cards is getting me all fired up! 
Since all this Folder business is now taken care of, we can go have some fun! 
<Mega> Wizard Equip Data, otherwise known as W.E. Data, is data that 
Battle Wizards can equip which gives them things like more attack power, 
quicker Buster firepower, and faster charge times. 
You can equip W.E. Data on the Mega Screen, so give it a try! 
<Mega> Bud and Zack sent you some information about battling! 
I sent you a few rules and tips of my own, so be sure to have a look, kid! 
<Zack> The other day in class we learned about battling 
and what to do if we encounter a virus, right? 
Well Prez wanted me to write up a summary of the Custom Screen so that we 
can refer to it in an emergency, so I did. 
This is a copy for you, Geo. 
The first thing you'll see when you meet an enemy is the Custom Screen. 
Six cards are randomly selected from the 30 cards 
that are in your Folder, and then displayed there. 
That doesn't mean you can just choose any cards you want. 
There are rules for these kinds of things. 
Rule #1! Cards in the same column can be selected together. 
It doesn't matter if they're not lined up exactly straight, as long as 
they're in the same column. 
Rule #2! Three cards in the same row can be picked together. 
It doesn't matter if they're not lined up exactly 
straight, as long as they're in the same row. 
Rule #3! 
Cards that have the same name can be picked together, regardless of their position. 
The exception are White Cards, which can 
be paired with any card anywhere on the screen. Very useful, right? 
Finally, you can use the R Button or Y Button to see card descriptions. 
OK! I think that about sums up the Custom Screen. 
That took forever to explain! 
<Bud> Hey, Geo! This is a summary of how to battle! 
I thought you'd find it useful, so I'm sending it to you. 
You can move left and right using the +Control Pad, 
and you can use a card by pressing the A Button. 
Holding down the B Button will unleash 
a rapid-fire attack from the Mega Buster. 
Not pressing the B Button for a while 
will let the Mega Buster charge up. Once it does, 
fire with the B Button for a Charged Shot! 
Speaking of charging, once the Custom Gauge fills, 
press the L Button or R Button to see the Custom Screen. 
Well, I guess that about sums it up. 
<Zack> I thought I'd send you this explanation about using your shield. 
Press the Y Button to put up a shield. 
You can use the shield to block enemy attacks. 
You won't have to worry about this much with weaker enemies, 
but later, there will be some enemy attacks that 
you can't dodge by just moving left or right. 
That's when you'll need to use the shield to guard yourself. 
But you won't be able to block everything, 
you know. You can't block an enemy's rush attack, 
and some attacks will be able to break through your shield. 
So be very careful. 
<Mega> Nobody bothered to explain the Mega Attack!? 
That figures, since I'm the only expert on the subject. 
Anyway, here goes! 
The Mega Attack is very important. 
When you have cards that you can use, 
press down on the +Control Pad and I'll 
switch into lock-on mode. 
When I'm in that mode, a sight will be shown on any enemies 
directly or diagonally in front of us. If you use a card when a sight is on, 
we'll rush right up to the enemy and attack! 
But keep in mind that some non-attack type cards, 
such as recovery cards and cards that dim 
the screen cannot be used with lock-on mode. 
Oh, and if you don't like the camera changing on 
you when you do a Mega Attack, 
you can change the the camera settings 
by pressing START during a battle. 
Remember, kid. You don't have to use 
the Mega Attack in every fight you're in, but when you 
do, you'll be able to fight on a much higher level! 
<Bud> Here's the lowdown on Countering and Bonus Cards. 
If you land a card attack on an enemy 
just as they're about to attack, that's a Counter. 
That'll catch them off-guard, paralyzing them for a time. 
You'll also receive a Bonus Card for doing so. 
Usually, you can only use cards you select on the Custom Screen. But if you 
land a Counter, then you'll be rewarded a Bonus Card. 
Bonus Cards are chosen from your Card Folder at random. 
Even so, they're great because you don't have to wait for the Custom Gauge 
to fill up before going buck wild on the enemy! 
Counters can only be performed with attack cards that don't dim the screen. 
And you can't get another Bonus Card if you pull off a Counter with a Bonus Card. 
So don't think you can get an unlimited chain of cards. 
The timing of Counters is tough, but they're really cool when you can pull them off. 
You should practice a little until you get the hang of it! 
<Mr.Shepar> This is a message to all Echo Ridge Elementary students. 
Recently, viruses have been seen in the Real World, outside of Cyber Cores 
where they're known for causing damage. Anyone who sees a virus, 
especially students who are not used to battling, should keep a safe distance. 
<Bud> I found a kid at the school shop who needs your help! 
<Zack> Please come to the science club room. It looks like there's a situation. 
<Mr.Shepar> There's a guest waiting for you at the front entrance. 
{90}{00}Welcome to <Spica.Mall>! 
Don't miss the Wave Battle Tournament going on in the {BD}{E4}! 
{90}{00}The Candy Shop grand opening is fast approaching! 
{92}{00}How about having lunch in our food court? 
{95}{00}For safety reasons, the {BD}{E4} will be closed temporarily. 
<Magnes> Yup yup! How are you!? Thanks to your hard work, 
I'm having a great time out here in space! 
For all of your trouble, here's an Ability for you! 
Abilities expand the functionality of your Wizard! 
Of course, Abilities have to be equipped before they're effective. 
Well, I'm looking forward to the day when we meet again! Yup! 
#Whoo-hoo! {B6}{E4} is like totally re-opened, dude! 
We've even got a gnarly new Card Trader! 
So, come on over all you dudes and dudettes, and like check it out! 
<Bud> I was thinking of how I could help you out, 
you know, with the incident at the concert and all... 
And I thought, as your Brother, I can let you borrow my Wizard, Taurus! 
...So, here he is. I'm sending you a Wizard adapter! 
{92}{E1}(a 
<Game> You added the "Taurus adapter" to your <Hunter>-VG! 
{02}{E2}(
<Lee.Stern> Geo, we're having some trouble setting up our equipment. 
Could you go to the props room inside the studio? 
<Lee.Stern> Geo, there's something wrong with the stage projector. I'll tell you about 
it when you get here. Please come quickly! 
<Lee.Stern> Geo, we got a call saying that there's a bomb 
program somewhere on the premises. 
I've sent all the Wizards I can to investigate the situation. 
They're being instructed by the security Wizard from the front entrance. 
Would you go and talk to him and find out how they are coming along? 
<Lee.Stern> It's absolutely freezing in Sonia's dressing room! 
We're using a fire-breathing Wizard to try and do 
something about the situation. 
<Mr.Shepar> I have important information for any of you who happen to run into a virus and 
find yourselves in a situation where you can't run away... 
Have you ever heard of something called a hack panel? 
Hack panels are panels that emit a special kind of Noise that makes it 
impossible for anything but viruses to stand on them. 
That means that you have to delete viruses without standing on the 
hack panels. But there is an easy way to get rid of them. 
Just use a "{D0}{E7}", "{BA}{E7}", or similar card to convert the panels. 
And remember, don't panic. I'm sending all of you a "{BA}{E7}" card. 
{0C}{E1}{00}{00}{FD}{00}b
<Prez> I'll wait for you, so come immediately to <Alohaha>! 
{95}{00}The reserved session for this beach has ended. Everyone is free to enter! 
{95}{00}The Island Environmental System is out of control! Be on the look out for hazards! 
<Woody> Hey, Geo! 
I just had to pass this juicy tidbit of information on to you! 
You said you had a Battle Wizard, right? Apparently, 
they have this special thing called a "Support Card". 
What it does is convert a Battle Card into a different Battle Card. 
The type of card that a Battle Card is converted to varies from Battle Wizard to 
Battle Wizard. I'm sending you a tutorial program. 
Please check it out when you have some free time! 
<Ace> I'm all ready now. Please come to the Satella Police Department. 
<Ace> Dr. Goodall has something to tell you about Luna Platz. 
<HarpNote> It looks like Ace and Queen Virgo have an issue that they need help 
resolving. Ace may need your help! 
<Game> Geo got: "{BA}{E7}" on his Hunter-VG! 
