<Ace> It looks like it's up and running. 
The main feature of my <AcePrgm> is the Noise Change... When the 
<AcePrgm> encounters high concentrations of Noise, it installs itself and 
resonates with the Noise, summoning more of the same resonant Noise from 
a server in space. This way, Noise no longer 
harms Mega Man, it makes him stronger as he draws more of it into 
himself. This power doesn't come without risk, and for that I 
apologize. But it was my belief that you, Geo, 
would be able to keep the Noise under control. 
Now let me explain to you how the Noise change works. 
The system can't be fully effective unless your 
Noise level is greater than 50 percent. 
At less than 50 percent your color remains blue, 
and some of your Battle Card Attack Power Ups and abilities will be unusable. 
That is called your Noise Form. 
But, at greater than 50 percent, your combat effectiveness 
will increase markedly. You'll gain extra color and charged attacks, 
Counters, NFBs (Noise Force Big Bang), etc. will 
all be at your disposal. If you want to fight 
normally, all you need to do is unequip the <AcePrgm> from your Abilities. 
Was there anything else I needed to tell you 
about...? Oh, yes... While it is true that the 
higher your Noise Level, the better fighter you should be, if your Noise 
Level rises too high - say above 200 percent, 
it's uncertain what could happen... 
But I know that you'll be alright, Geo. 
You're every bit the hero I thought you were! Go get 'em! 
<Lee.Stern> Hey, Geo! I've got some good news! 
Do you know that some Battle Cards have 
inherent "Wind properties"? 
The WindyAtk, for example has a very interesting feature. 
It can strip away Barriers, Auras, etc. in one shot, regardless of damage. 
There are other cards out there with wind 
properties, so keep your eyes peeled for them! 
Well, talk to you later. 
.This is a message from <Spica.Mall>! The Candy Shop is now open! 
<Ace> There's something important I want to talk to you about. 
Come to the Main Computer Cyber Core. 
<HarpNote> The virus disturbance has died down, 
but now there's a very powerful Noise Wave at the Event Stage! 
Could you come? 
<Ace> Geo, I want to explain to you a little about your Multi Noise Form. 
I'm sending a tutorial program about it. Have a look when you get time. 
<Dr.Goodall> Hello, Geo. 
I hope you're doing well. 
There's something I learned about Noise Changing that I wanted to 
share with you. There's the possibility 
that you, having Noise Changed once already, 
could spontaneously Noise Change in the 
presence of very strong Noise. 
Also, Arthur may have told you this already, but 
fighting especially large viruses may also cause you to Noise Change, 
because of their ability to affect the area 
surrounding them by creating balls of Noise. 
There is still much we don't know about the Noise Change... 
So, please, Geo, be careful. 
<Zack> There's a strange EM body holding up traffic on the Natl Astro Wave2. 
It doesn't seem to be related to Dealer. 
But if you go there, please be careful. 
<Ace> If you're reading this pop-up, I'm probably 
already gone from this world. 
I set this pop-up to activate automatically in 
the event that anything should happen to me. 
I wonder how I went out? I can only imagine. 
I just hope that I can leave you with the will to 
keep on fighting till the end. 
I want to help my friends and colleagues in the 
Satella Police Force, and Queen Tia. 
I fought this long and hard because I want to protect all that is dear to me... 
You too, Geo, fight to protect the bonds that you've built-up until now, 
and the things you care about. 
Overcome the enemy, yourself, and anything that stands in your way. 
You are our final hope. I'm passing the torch onto you. 
And finally, I'm leaving the Satella Police's 
"Ultimate Weapon" in your care... 
I'm counting on you, Mega Man. 
<Game> King is now at the Orbital Base in space. This key will open the 
Astro Wave, which will take you there. Hurry, Mega Man! 
*Meteor G is once again on a collision course with our planet. 
Moreover, the leader of the organization known as 
Dealer is presumed deceased. 
<Mr.Boreal> Geo, turn on the TV! 
<Prez> Geo, would you mind coming to Echo Ridge if you have time? 
Everyone has something they want to talk with you about. 
Let's meet on the roof of the school. 
{98}{00}Presently, WAZA and the surrounding area is experiencing severe 
EM interference. Some kind of Noise is thought to be the cause. 
All members of the Satella Police Force able to respond are to 
proceed to the area around WAZA immediately. 
{98}{00}Notice to the Satella Police Department. 
Those who would like to request issue of a Wave Liner ID, which 
allow its holders to ride the WAZA-bound Wave Liner, should submit their 
application to the duty officer at WAZA Command. 
{98}{00}Information for Geo Stelar. 
Starting today, you can use any Wave Station to get Wave Road Maps. 
To use this service, select "Maps" from the Wave Station menu. 
<Zack> I almost forgot to mention something very important! 
If you come up against a virus you think you 
can't beat, you might want to try running away! 
All you have to do is press the L Button at the Custom Screen. 
But just know that there are some times you won't be able to run away. 
<Ace> So, how do you like that Astro Wave? 
By the way, did you ever use that <AcePrgm> I gave you in battle? 
When it's installed, you'll see a Noise Level 
gauge on the upper right of the screen. 
The gauge rises and falls depending on the battle situation. 
Until about 99 percent, you won't be affected 
much. But after 100%, be careful! 
All sorts of strange phenomena have been observed. For example, 
you may get hit with an attack even though you are flashing. 
Or you land an attack that is supposed to blow enemies back, 
but instead it draws them toward you. 
Also, this hasn't been confirmed, but Noise may 
cause your acquired data to be converted into data 
that is totally unrelated to the enemy you have deleted. 
These are just some of the reports that have come in. 
We're not quite sure what conditions govern the rise of Noise levels, 
but early reports suggest that when a non-dimming, 
non-elemental card is used to delete a virus, 
the difference of the card's attack power and 
the virus's HP correlates to the percentage of Noise elevation. 
I'd advise caution. But you, Mega Man, may be able to 
control it as Noise levels rise. 
I guess it all boils down to, don't overdo it. 
{98}{00}WAZA Top-secret program Purpose Card input has been confirmed. 
Only one of these Purpose Cards can be entered. 
Installing this data will Power Up your Finalization. 
And if you are on a Team, and that Team has your Real Brothers on it, 
you can share this data with them. 
So, the more Real Brothers you have on your Team, 
the more Power Ups you'll be able to share. 
In order to form a Team with your Real Brothers, 
you'll need to first clear the game, though. 
Power Ups can be turned ON and OFF on the Purpose Card Screen. 
This conclude the Purpose Card explanation. 
<Mr.King> Hahaha... 
I see that you have finally obtained the prized Noise Card... 
Allow me to explain to you how it's used. 
You can only enter up to 5 Noise Cards at a time. 
If you wish to enter a new Noise Card when you have already entered 5, 
you'll first need to select a Noise Card to delete from the list by touching it. 
Noise Cards come in four suits. Diamonds, Hearts, Clubs, and Spades. 
You should try to enter cards of the same suit as much as possible. 
If you enter cards from different suits, 
you may experience bugs that damage you... 
Oh, that reminds me... 
If you happen to get a card that bears the 
Star Force logo, consider yourself lucky! 
Because, those cards can be combined with cards from other suits. 
One last thing... I'll tell you one method to control Noise. 
You can make poker hands called Noise Hands. 
Depending on the kind of Noise Hand you make, 
not only will you control Noise, 
but the power that lies within the Noise will be bestowed upon you. 
Finally, the power of Noise Cards can be turned 
ON /OFF on the Mega Man Screen. 
Alas, will you be able to master the full potential of Noise Cards!? 
Mwu ha ha ha ha! 
<Mega> Kid, there's one thing I wanna tell you. 
While you're Wave Changed, Sub-Cards, 
Acquired Data, and HP Balls are the only means to restore your HP, 
but you can fully restore your HP by un-Wave Changing! Bear in mind 
though, that just pulsing out but staying in your Mega Man form won't do 
the trick! You have to completely un-Wave Change. 
<Prez> Helping people is the mission of Team Luna 4 Prez! 
That wonder work doesn't just stop here at school! 
It carries on across the whole nation... No! 
Team Luna 4 Prez will help people in need all around the world! 
As such if you ever talk to someone and you get a pop-up that says "HELP", 
it means that person is in need of assistance. 
You can touch the HELP pop-up to find out more about their situation! 
Once you've done that, it's a good idea to talk to them some more to get 
detailed information about what you can do for that person. 
At that point, that person can give you a formal "Mission Request". 
Take it and carry it out to its end, understood? 
Nobody should have a problem or request that 
you... oh I mean Mega Man can't handle in a flash! 
But, if for some reason, though no valid reasons come to mind at this time, 
you can't complete a mission that you've been given, you can go back 
to the person who gave you the mission request 
and formally cancel the mission. 
But don't worry, you can accept the mission as 
many times as it takes to resolve the issue! 
Oh, one more thing. 
Once you've taken a mission request from 
someone, until you either complete or cancel it, 
pop-ups from other people won't be displayed. 
That means you'll need to make a decision quickly, and not dilly-dally around. 
...OK, now do your best! Like the true leader that I am, I'll be watching over 
your progress, Ge... I mean Mega Man. 
{7B}{00} 
{7B}{00} 
{7B}{00} 
{7B}{00} 
{7B}{00} 
{7B}{00} 
{7B}{00} 
{7B}{00} 
{7B}{00} 
{7B}{00} 
<Ace> If you're reading this pop-up, I'm probably 
already gone from this world. 
I set this pop-up to activate automatically in 
the event that anything should happen to me. 
I wonder how I went out? I can only imagine. 
I just hope that I can leave you with the will to 
keep on fighting through till the end. 
I want to help my friends and colleagues in the Satella Police Force, 
and Queen Tia. 
I fought this long and hard because I want to protect all that is dear to me... 
You too, Geo, fight to protect the bonds that you've built-up until now, 
and the things you care about. 
Overcome the enemy, yourself, and anything that stands in your way. 
You are our final hope. I'm passing the torch onto you. 
And finally, I'm giving you the power that is 
the ace up the Satella Police's sleeve... 
I'm counting on you, Mega Man. 
