<Game> Libra Noise -Detailed Information- 
Body: Non-elemental Weakness: Break attacks 
Noise Form Capabilities: Fire and Aqua elemental card attacks +10 
Vibrant Noise Capabilities: Non-dimming, non-elemental cards restore HP 
Charged attack: "Side Spread" spreads damage left and right when it hits 
NFB: Non-elemental attack "Meteor Light Barrage" 
<Game> Corvus Noise -Detailed Information- 
Body: Fire elemental Weakness: Aqua elemental attacks 
Noise Form Capabilities: Non-dimming Fire elemental card attacks +30 
Vibrant Noise Capabilities: Nullifies Poison Panels, HP Bugs, and Black hole attacks 
Charged attack: "Shocking Flare", fires flames that stop enemies dead 
NFB: Fire elemental attack "Atomic Blazer" 
<Game> Cancer Noise -Detailed Information- 
Body: Aqua elemental Weakness: Elec elemental attacks 
Noise Form Capabilities: Non-dimming Aqua elemental card attacks +30 
Vibrant Noise Capabilities: Bubble enemies with non- dimming Aqua elemental cards 
Charged attack: "Bubble Shot", traps enemies in a bubble 
NFB: Aqua elemental attack "Dyna Wave" 
<Game> Gemini Noise -Detailed Information- 
Body: Elec elemental Weakness: Wood elemental attacks 
Noise Form Capabilities: Non-dimming Elec Elemental card attacks +30 
Tag Cards are cards you set on the Custom Screen to make them more likely 
to appear in battle. You can designate Tag Cards by 
pressing the Y Button on the Folder Edit Screen 
Vibrant Noise Capabilities: Adds paralyze effect to sword attacks 
Charged attack: "Rocket Knuckle", paralyzes enemies 
NFB: Elec elemental attack "Thunder Bolt Blade" 
<Game> Ophiuca Noise -Detailed Information- 
Body: Wood elemental Weakness: Fire elemental attacks 
Noise Form Capabilities: Wood elemental card attacks +20 
Vibrant Noise Capabilities: Land hit with non-dimming, non-elemental card to 
confuse enemies. You will not get blinded or confused 
Charged attack: "Wood Shot", turns adjacent panels to grass 
NFB: Wood elemental attack "Elemental Cyclone" 
<Game> Cygnus Noise -Detailed Information- 
Body: Non-elemental Weakness: Sword attacks 
Noise Form Capabilities: Equips AirShoes, FlotShoe 
Non-elemental card attacks +10 
Vibrant Noise Capabilities: Non-dimming wind attack card attacks +30 
Charged attack: "Feather Vulcan", ignites rear panels 
NFB: Non-elemental attack "Meteor Light Barrage" 
<Game> Taurus Noise -Detailed Information- 
Body: Fire elemental Weakness: Aqua elemental attacks 
Noise Form Capabilities: Equips SprArmr 
Vibrant Noise Capabilities: Non-dimming, Fire Elemental card attacks +50 
Charged attack: "Heat Cannon", ignites 3 back panels when it hits 
NFB: Fire elemental attack "Atomic Blazer" 
<Game> Virgo Noise -Detailed Information- 
Body: Aqua elemental Weakness: Elec elemental attacks 
Noise Form Capabilities: Non-dimming, Aqua elemental card attacks +30 
Vibrant Noise Capabilities: Nullifies effects of freezing or bubbling 
Charged attack: "Aqua Wave", washes 
over the entire row NFB: Aqua elemental attack "Dyna Wave" 
<Game> Crown Noise -Detailed Information- 
Body: Elec elemental Weakness: Wood elemental attacks 
Noise Form Capabilities: Increases probability of a Mega class card appearing 
first on Custom Screen, Elec elemental card attacks +20 
Vibrant Noise Capabilities: Land hit with non-dimming, 
non-elemental card to blind enemies 
Charged attack: "Plasma Shot", paralyzes enemies 
NFB: Elec elemental attack Thunder Bolt Blade 
<Game> Wolf Noise -Detailed Information- 
Body: Wood elemental Weakness: Fire elemental attacks 
Noise Form Capabilities: Equips Quick Gauge, 
Non-dimming sword attacks +30 
Vibrant Noise Capabilities: Wood elemental card attacks +10 and auto lock-on 
Charged attack: "Shock Claw", a 3 panel wide attack on the front 2 rows 
NFB: Wood elemental attack "Elemental Cyclone" 
<Game> Rogue Noise -Detailed Information- 
Body: Non-elemental Weakness: None 
Noise Form Capabilities: Non-dimming sword attacks +50 
Once per turn, can block attacks with "MuBarrier" 
Vibrant Noise Capabilities: Can destroy enemy's lock-on sight even if locked onto, 
adds paralyze effect to non-dimming, non-elemental cards 
Charged attack: Unchanged 
NFB: None This Noise breaks all of his bonds 
<Ace> Finalization explanation 
{7B}{00} 
{7B}{00} 
{7B}{00} 
{7B}{00} 
<Harry.Sasoon> I'm a big big big big fan of Sonia Strumm! 
Do you know about her trading cards? 
I've been collecting them since back when she debuted. 
But there's this one I just can't get my hands on no matter how hard I try. 
It's called the Sonia Little Devil card! 
I wonder if there's anyone out there who would want 
to trade me that one for a Sonia "Wink" card. 
<Jack.Flask> I got a bad grade on my test and I didn't want to show my mommy, 
so I made a paper airplane out of it and threw it from the roof. 
But my mommy found out about my test, and now she wants to see it. 
But I don't know where it went after I threw it. Can you help me find it? 
<Angel.Wise> Could you do me a favor!? 
Could you please get Belle's autograph for me? 
=I need to find a filming location for a new drama 
we're making, but it just takes so much time. 
I know it's kind of like cheating, but could you take a nice photo of a 
beautiful beach with some nice buildings and bring it back to me? 
)I'm looking for these two games called "{93}{E5}"  and "{94}{E5}", 
but they're so popular that they've sold out everywhere. 
The more I can't have them the more I want them. 
<Angel.Wise> I'm worried about Woody. 
He's been working awfully hard lately, and I think he needs a pick-me-up... 
You know, I'd really like to get one of those special <Alohaha> energy drinks! 
0Eradicate the 3 viruses spotted in <Spica.Mall>. 
0There have been reports of a suspicious looking person having been sighted in 
{19}{E5}. Could you go and investigate? 
<Candy.Bar> 
0There's a security camera in the eye of the dragon statue in <Alohaha>. 
But for some reason, the only thing being filmed is girls in bathing suits. 
Could it be a malfunction? 
<Prez> Lately there's been a rumor going around at school 
that is frightening the students. 
They say that if you knock on the door of the girls restroom at 
<Spica.Mall> and say some special chant... 
A ghost will appear! 
Of course I don't believe in things like that, but, as class president, 
I can't ignore the fact that something is scaring students at our school. 
Geo, since you are our resident hero, 
I want you to go and get to the bottom of this rumor for me! 
<Zack> All of the electronics in my room, like my computer 
and my game systems are on the fritz! 
Could you come over and have a look!? 
+When I was young I was a carpenter. I actually 
helped build the Echo Ridge Elementary school building. 
I was so happy that the construction was complete, 
that I wrote graffiti on a certain part of the building. 
The thing is, now that I'm old, I'm having trouble remembering where it is. 
But I want to remove it. 
These days, my legs hurt, and I just don't have it in me to look for it. 
Could you find where it is and remove it for me? 
3Could I get you to go and buy some ice cream for me to eat on my break? 
An ice cream cone from that {BE}{E4} that just opened up would be great! 
<I just ordered lunch for the staff, but I don't have time to go and pick it up. 
If you could pick up the order and make sure the 
staff gets their lunches, I'd really appreciate it. 
By the way, the place I ordered from is 
Echo Ridge Elementary's school store. 
<Mr.Boreal> Geo, you wouldn't happen to have a Battle Card called "{6A}{E7}", would you? 
Would you mind trading it for my "{28}{E8}"? 
