<Game> The act of deleting EM viruses. 
<Game> A self-aware program that operates inside of electronic devices like Hunter-VGs etc. 
As EM Beings, Wizards can also materialize into actual physical forms. 
<Game> A portable device that fits in the palm of your hand. This all-in-one communication device has become an indispensible part of everyday life. 
<Game> Entities whose bodies are made up of EM waves. 
<Game> A device used by Geo's father, Kelvin, to see EM bodies. 
<Game> EM bodies which are generally considered harmful by humans, which cause damage to electronic devices and EM technology. 
<Game> The central-most part of an electronic device. 
Normally EM bodies can enter Cyber Cores, but some Cyber Cores are access-restricted because of maintenance, etc. 
<Game> When a human merges with a Wizard and takes on an EM form. 
Only a handful of humans are known to be able to do it, but those who are exhibit awesome battle capabilities. 
<Game> A system that manages EM technology over a wide area. They also function as information services for the general public. 
<Game> A road created from the EM wave radiation emitted from electronic devices which allow EM bodies to travel from place to place at high speed. 
<Game> To move from the interior of a Cyber Core back to the Wave Road. 
<Game> To move from the interior of a Cyber Core or from the Wave Road back to the Real World. 
Note that moving from the interior of a Cyber Core back to the Wave Road is known as Transing Out. 
<Game> A common goal shared by friends as a function of the Hunter-VG. 
<Game> A group of Brothers who share the same Purpose. 
<Game> A person who becomes part of another's inner circle of friends bound by a very tight bond 
known as a Brother Band. This is a function of the Hunter-VG. 
<Game> An area putting off abnormal EM waves known as Noise. 
<Game> The name for the latest mobile terminal. In addition to having virus busting capabilities, it also features a data capture function. 
<Game> WAZA An organization that oversees space technology. It was formerly known as NAZA. 
<Game> An organization set up to crack down on sophisticated EM crimes. The elite group is made up of top specialists from every field. 
<Game> The southernmost island in Electopia. Visitors flock to this resort paradise during the summer months. 
<Game> An ancient, yet highly advanced civilization that is now extinct. Mu technology was made use of extensively by Dr. Vega. 
<Game> Omega-Xis An alien from outer space who is now Geo's Wizard. 
<Game> Luna Platz Geo's friend who, though a bit snobbish, is actually quite kindhearted. 
<Game> Bud Bison Geo's friend who has a voracious appetite, along with a seldom seen caring side. 
<Game> Zack Temple Geo's friend who is a bookworm and dislikes physical activity. 
<Game> Sonia Strumm Geo's friend who is a vivacious and outgoing teen idol. 
<Game> Sonia Strumm's Wizard. Like Omega-Xis, she is an alien from outer space. 
<Game> Aaron Boreal A close friend of Geo's father and a brilliant scientist. 
<Game> Tom Dubius Aaron Boreal's colleague and passionate inventor. 
<Game> Damian Wolfe An at times belligerent gardener, but can also be dependable. 
<Game> A descendent of Mu, Solo Wave Changes into Rogue, Mega Man's archrival. He loathes friendship, bonds, and the like. 
<Game> Kelvin Stelar Geo's father. He went missing after an accident in space 3 years ago. 
<Game> Owner of a shop in Echo Ridge known as {B6}{E4}. 
<Game> The three great EM beings from the Planet AM who once managed all of Earth's Brother Bands and waves, and 
aided in the development of EM civilization. 
<Game> Once deceived by his followers into invading Planet Earth. He learned the importance of bonds after fighting Mega Man. 
<Game> Omega-Xis's home planet that once had close ties to Planet FM before it was invaded. Reconstruction of Planet FM is currently underway. 
<Game> The planet that Geo's father, Kelvin, was able to successfully make contact with, and also 
the planet on which Omega-Xis lived before coming to Earth. 
<Game> Bob Copper A detective on the Satella Police force, 
who at one time, was investigating Geo, who was hiding the fact that he was actually Mega Man. 
<Game> A person who uses or owns a Wizard. 
<Game> A set of 4 all white, very useful cards found only at Wave Stations. 
<Game> One Standard Class Card from your folder that you designate to be your Default Card and which 
always will appear first on your Custom Screen. To make a card a Default Card, select it 
with the cursor and press the Y Button. 
<Game> To enter a Cyber Core as an EM body. 
<Game> A delicious snack that comes in many flavors that only costs 10 Zennys. 
<Game> An adapter that allows you to install Wizards on your Hunter-VG. 
Just plug it into the slot to control multiple Wizards on your Hunter-VG. 
<Game> This all-in-one communication device has become an indispensible part of everyday life. 
<Game> This all-in-one communication device has become an indispensible part of everyday life. 
<Game> This all-in-one communication device has become an indispensible part of everyday life. 
<Game> This all-in-one communication device has become an indispensible part of everyday life. 
<Game> This all-in-one communication device has become an indispensible part of everyday life. 
<Game> This all-in-one communication device has become an indispensible part of everyday life. 
