<Pedia> I'm not very good at battling, but when it comes to research and analysis, 
leave it to me! I enable Zack to always make the right moves! 
{09}{E1}{00}{00}{A1}{06}{5A}{07}l{09}{E1}{00}{00}{B2}{07}{02}{08}l
<Coil> As Woody's Wizard, I help him out a lot with his experiments. 
I'm not very agile when it comes to battling and such, 
but I can manipulate magnetism! 
By the way, that Wizard piloting the rocket is my older brother, Magnes! 
<Magnes> Yup! I'll be the brains and the pilot of a rocket going into outer space! Blast off! 
<Acid> I am a superior Battle Wizard, a product of the Satella Police Department. 
It is an honor for me to serve as Ace's Wizard. 
<Lyra> Hee hee... I merge with Sonia so that she can Wave Change 
into Harp Note! I help her compose songs, 
and make sure that she always looks her best! 
<Vogue> I find trendy spots for Luna to go to that keep her looking fabulous! 
And let's not forget that my memory capabilities are state of the art! 
But battling is not my forte. It's just terrifying... 
<Taurus> I am Taurus, the Wizard of flame! 
I'm always down to get my battle on! 
<Wolf.Woods> I don't have anything to say to strangers! 
<Virgo> Go away and don't bother me! Kyahahahaha!! 
{B1}{00}{13}{EC}..... 
{9C}{00}Like have fun shopping at Big Wave! 
There may even be like a special service for the cuties! 
<Ice> As Belle's manager, I pledge to make her a big star and a top teen idol! 
No one knows more about her talents and abilities than I do! 
{88}{00}I often speak on Tom's behalf because he isn't very 
keen on speaking for himself. 
Another duty of mine is to help him with his inventions. 
{AF}{00}Helping Damian with his daily regimen of combat training is my responsibility. 
Grr! My blood is boiling! 
<Game> SECRET 
<Game> SECRET 
<Game> SECRET 
{A8}{00}Mr. Copper actually gets around quite a lot. 
He likes solving cases the good ol' fashioned way, 
with down and dirty detective work. 
Since he solves all of the cases himself I don't really get to do much... 
{90}{00}They say that there are some Battle Wizards that can do lock-on attacks. 
This allows them to close in on an enemy that's locked-on almost instantly. 
There are also several types of search patterns and ranges. 
{91}{00}Here's a tip! 
The FlashStrk Battle Card is very handy because it blinds enemies. 
For Wizards that aren't so strong like me to win, 
it's important that we know how to blind and confuse enemies! 
{92}{00}My operator is getting up there in age, but recently it looks like he has taken a 
liking to Clarice from the gate ball club. But let's keep that between 
me and you. 
{93}{00}My operator won't take me virus busting because 
she says she doesn't want me to get damaged. 
She's very good to me! I'll make sure to protect her no matter what! 
{93}{00}I know my operator loves me sooo much! 
I'm so lucky to have an operator like him! 
{91}{00}Hello! I am a Tutor Wizard. I work hard to help my 
operator with her studies so that she can raise her grades! 
{92}{00}My operator is very good at hide and seek! 
You should play it with him someday. How about it? 
{91}{00}My operator is always getting lost. 
It's a good thing that I have navigation capabilities... 
{9D}{00}My operator hates to lose. He's a real competitor. 
So when things get a little hairy, I can't afford to lose my edge! 
{92}{00}As you can see, my operator is the school principal. 
I really think he is starting to rub off on me. 
{93}{00}I love virus busting! But, since my HP is low, 
I rely heavily on Recovery Cards in battle. 
{96}{00}My operator is gung-ho about everything he does, but sometimes he overdoes 
it and gives himself a stomach ache. 
{90}{00}My operator is huge fan of Sonia Strumm's. 
He's always spending his allowance on Sonia Strumm goods. 
What am I going to do with him? 
{91}{00}My operator always keeps her folder filled with Fire Elemental Cards. 
With all that fire, it seems a waste not to have at least one {D0}{E7} Card... 
Her battles would just be so much cooler if she did. 
{90}{00}My operator isn't very good at battling, but recently he's 
been learning various techniques. 
I must say, he is becoming quite an operator. 
{96}{00}My operator is a huge quiz fan. Sometimes I sit down with her and we think 
about quizzes together. Would you like a crack at one of our quizzes? 
{91}{00}Lately my operator is really into that new teen idol, Belle! 
Once you get her started talking about her, she just won't stop. 
{93}{00}My operator's Purpose... It's so not cool. 
{91}{00}I'm not a Battle Wizard, so battling is not my thing. 
But the other day, while my operator and I were virus busting, 
I converted 3 Cannon Cards into a super powerful card! 
I deleted those viruses with a Busting Level of S! 
{92}{00}My operator is the Echo Ridge Elementary School janitor. 
Not to change the subject, but do you know about screen-dimming cards? 
The moment you use them time stops, and the screen goes dark. 
There must be a good use for this kind of phenomenon. 
{9D}{00}One {60}{E3} isn't very scary, but when 
they're in a group, you can't let your guard down. 
{91}{00}I just barely managed to win a battle I was in not long ago. I didn't get any Zennys, 
Battle Cards, or anything like that, but I did get an HP recovery ball. 
And, boy did I need it! 
{90}{00}As you can see, my operator is the most 
important person in <Spica.Mall>! 
I do various support jobs, like help him manage his schedule! 
{94}{00}I wonder what I can do to improve my Busting Level? 
Once, just once, I want to get a Busting Level of S. 
{90}{00}These high Noise levels are making me feel a little sick... 
{A8}{00}With the spread of technology, crimes are 
becoming more and more complex. Nowadays we're 
fighting much more than just viruses. 
{93}{00}My operator is very very rich! 
Did I mention how wealthy my operator is!? 
{A8}{00}Deleting all enemies quickly will definitely earn you a high Busting Level, 
but there are other ways as well. 
For example, deleting two or three enemies at a time could do the trick. 
There may even be other ways to raise your Busting Level. 
{A8}{00}Your Busting Level is an indicator of your battle skills. 
Quickly eliminating all enemies, and deleting two or three enemies at a time 
can all increase your Busting Level, 
but there may be other ways as well. 
{96}{00}I'm calculating the best game strategy for my operator. Hmmm... 
Yep, he's going to need to keep pressing that button until he clears the game. 
{96}{00}My operator is crazy about sweets... 
I have to do what I can to insure he doesn't get too fat. 
{90}{00}Sometimes I see viruses just roaming around town. 
I wonder if I could get something for taking them out? 
{96}{00}I handle all of the studio equipment maintenance! 
I can fix any piece of equipment, no matter how complex. 
{93}{00}Keeping a Wizard well-equipped is very important! 
It doesn't make any sense to get an item and not equip it. 
{92}{00}I hear that in <Studi.WBG> Wizards and people work together to make programs. 
My operator says that he wants to work there someday. 
{90}{00}Hitting your opponent with a strong attack card after paralyzing them with a 
shot from you PlasmaGun is an old-school battle tactic! 
{9D}{00}My operator loves trading Battle Cards. 
If you wouldn't mind, please trade with him if you get the chance. 
{90}{00}I make sets together with my operator. 
Real Waves are fine and all, but nothing beats the look of a handmade set. 
{97}{00}I'm a real beast when it comes to editing film. 
Don't even think about talking to me when I'm at work in the cutting room. 
You could get hurt. 
{91}{00}When it comes to making TV stars look good, I am 
the best. Just give me a face and see what I can do! 
{93}{00}In a battle, you've got to know when to hold 'em and 
know when to fold 'em. Sometimes it's OK to run away. 
{94}{00}Noise is scary... I wonder if it's what causes machines to go out of 
control. They say that we Wizards give off Noise too, 
so, in a way, I feel partially responsible... 
{93}{00}My operator is an actor. I help him remember his lines and motions. 
{90}{00}My operator is an action stuntman! 
A stuntman's body is his bread and butter! 
Everyday I manage his workout routine, and meal schedule! 
{94}{00}You know how sometimes in a battle you get hit with something that leaves you 
dazed and confused? And you try to put up your shield, but you can't? 
I HATE that! 
{90}{00}Not long ago, I used a Battle Card called SharkAtk in a battle. These sharks 
lined up side-by-side and then went swimming across the screen. 
What was that all about? 
{90}{00}The other day I ran into this enormous virus! 
That was crazy scary! 
{9D}{00}Ever notice that a lot of the Battle Cards on the Custom Screen are 
duplicates? Cards are selected at random, but the more of the same cards 
you have, the more likely it is that duplicates will pop up. 
I wish my operator would put a little more thought into 
what cards he puts in his folder. 
{91}{00}My operator is a little heartbroken right now over a failed relationship. 
Honestly, though, I don't think that guy was worth it. 
{90}{00}My operator is Brothers with his girlfriend. I got to make plans for their next date! 
Ii looks like he's going to pop the big question to her at the very end of it! 
{91}{00}My operator and her boyfriend are sooo in love! 
They might even be thinking about getting married! 
{94}{00}My operator loves to swim. 
It's a good thing that I know CPR, so I can help 
him if he ever starts to drown! 
{96}{00}Sword-type Battle Cards work best when they're locked-on to their target. 
But of course you probably knew that already, right? 
{9D}{00}<Alohaha> has been the site of many movies and dramas. 
Sonia Strumm recently even did a photo shoot there. 
{A8}{00}One good use of the {54}{E7} is to dodge 
an oncoming enemy attack, and then slash them with it! 
{A8}{00}We Satella Police Wizards have advanced, powerful, battle capabilities. 
We don't lose to the likes of viruses. 
{A8}{00}As a Satella Police Wizard, I have devoted myself to the fight for peace! 
{A8}{00}When you get hit with attacks that make you dazed and confused, and you 
can't fight like you want to, just try and stay calm! 
{98}{00}Satella Police Wizards are specialized for battle, and 
WAZA Wizards are specialized for brainwork. 
{A8}{00}We Satella Police Wizards were created to prevent crimes from happening... 
For the sake of peace, we are not afraid to use delete force. 
{98}{00}The Environmental System you see here was created by all of us at WAZA! 
Not too shabby if I do say so myself. 
{98}{00}You can make good use of cards you thought were 
unusable depending on how you combine them. 
It might be a good idea to put some of those cards 
you removed from you folder back in there. 
{93}{00}I'm working as a Guide Wizard here in Alohaha My operator just moved 
here, so I've been quite busy showing her the sights. 
{A8}{00}To keep peace in the world, that is what we were made for. That is our purpose. 
{A8}{00}We're counting on you, Omega... And Mega Man! 
{A8}{00}Stay sharp, Mega Man Star Force! 
{98}{00}It's in your hands now! 
{98}{00}Don't let all of those lives that were lost be in vain! 
Please make it back in one piece! 
{A8}{00}Your Wizard, Omega-Xis, is one rock'em sock'em Battle Wizard! 
{A8}{00}A particular kind of Battle Card like the {C9}{E7} card 
will allow you to hit enemies even when they are flashing. 
Acid once used that technique to achieve a truly splendid combo! 
{A8}{00}Do you know what Guard Null Panels are? They are panels that don't 
allow the use of shields while you are standing on them... 
I once got into quite a bit of trouble with those. 
You should be careful. 
{A8}{00}You probably know that the {B7}{E7} card places 2 stones on the battlefield, 
but did you know that there is a way to control the placement of the stones? 
A Satella Police study of that is currently underway. 
{A8}{00}Are you using any White Cards? Did you know that they are distributed by 
the Satella Police Department via Wave Stations? 
{A8}{00}Using Default Cards is fundamental to winning battles. To set a default 
card, highlight a card with the cursor and press the Y Button. 
You remember, don't you? 
{98}{00}Battle Cards can become stronger depending on how you combine them. 
Look for some good combinations. 
{98}{00}The more of the same card you put in your folder, the 
more likely it is that you'll see that card on the Custom Screen. 
Be careful. 
{98}{00}To raise your Busting Level, it's just as important to to delete all enemies 
speedily as it is to delete multiple enemies at once. 
{98}{00}Be careful if you ever run into a "ghost" of a Wizard 
that has gone out of control. 
{98}{00}When you hit a frozen enemy with a break-enabled attack, 
you'll inflict twice the damage. 
It wouldn't hurt to remember that. 
{98}{00}When you see the "WARNING" Pop-up, beware! This Pop-up warns 
you that a powerful enemy is approaching. 
{98}{00}Crystallized Noise, Crimson, is a very dangerous substance... 
{A8}{00}The shield. The most fundamental of fundamentals, is very 
important. To use it, just press the Y Button in battle. You knew that, right? 
{A8}{00}EM Wave Change ID "003" Mega Man Star Force! You may be our last hope! 
{A8}{00}I have been watching you all of this time. 
It is an honor to finally meet you like this. 
{A8}{00}I will risk everything to fight for world peace! 
{A8}{00}Before, it seemed like we were going to lose this battle, but Dr. Goodall 
turned all of that around! She truly is a remarkable woman. 
{A8}{00}Your father, Kelvin, is a kind and extremely distinguished human being. 
It is an honor to know his son. 
{98}{00}Noise Cards are something even we haven't been able to get our heads around. 
{9D}{00}I can't believe that boy is wasting all of his money... Maybe I'll have to intervene. 
<Pedia> Support for Prez is now {20}{E1}{03}{00}%! 
