<Ace> Welcome to the Satella Police Network! 
<Ace> You can battle your Friends and make Brothers!
<Ace> Battle Friends and make Brothers using Nintendo Wi-Fi Connection.
<Ace> You can face off with Friends!
<Ace> After a match, invite your opponent to be Brothers!
<Ace> After a match, invite your opponent to be your Battle Mate!
<Ace> You can exchange Battle Cards with your Friends!
<Ace> You can exchange the latest data with up to 6 Brothers!
<Ace> Disconnect from the other party.
<Ace> Do you want to disconnect? {10}{EC}{00}{00}Yes {10}{EC}{01}{00}No {0F}{EC}{00}{00}{00}{00}{02}{00}{00}{00}
<Ace> Disconnecting...
<Ace> Oops, it looks like the other party disconnected.{01}{E1}
<Ace> Set up a session as the Host and let others connect.
<Ace> Join a session as a Client and search for a Host.
<Ace> Enter a 2 digit number to find a specific person.
<Ace> Waiting for a Client to join...
<Ace> Waiting for a Client to join... (A Button: Stop accepting clients)
<Ace> Looking for a Host...
<Ace> Initiate a connection? {10}{EC}{00}{00}Yes {10}{EC}{01}{00}No {0F}{EC}{00}{00}{00}{00}{02}{00}{00}{00}
<Ace> It looks like the Host canceled the connection. 
Do you want to search again for a new host? {10}{EC}{00}{00}Yes {10}{EC}{01}{00}No {0F}{EC}{00}{00}{00}{00}{02}{00}{00}{00}
<Ace> Negotiating with Host... Hold on for a second.
<Ace> It looks like the Client canceled the connection. 
Do you want to restart the session and wait for a new Client to connect? {10}{EC}{00}{00}Yes {10}{EC}{01}{00}No {0F}{EC}{00}{00}{00}{00}{02}{00}{00}{00}
<Ace> No Host was found. 
<Ace> 1 battle showdown determines the winner. Results are unaffected.
<Ace> Best 2 out of 3 battles is the winner. Results are unaffected.
<Ace> 1 battle showdown determines the winner. Winner gets Illegal data!
<Ace> Best 2 out of 3 battles is the winner. Winner gets Illegal data!
<Ace> Decide the number of turns for this match. {10}{EC}{00}{00}15 Turns {10}{EC}{01}{00}10 Turns {10}{EC}{02}{00}5 Turns {10}{EC}{03}{00}3 Turns {0F}{EC}{03}{00}{00}{00}{00}{00}{00}{00}
<Ace> Face off against Brothers and Battle Mates from around the globe.
<Ace> Become Brothers with friends far away by entering a friend code.
<Ace> Become Battle Mates with friends far away by entering a friend code.
<Ace> Update your Brothers' information.
<Ace> Prepare to connect to Nintendo Wi-Fi Connection.
<Ace> Oops... It looks like both of you chose different modes.{34}{EC}
<Ace> Please wait while the other party wraps things up...
<Ace> Battle Mates on standby who have already been registered were removed from standby.
<Game> Battle opponents with card-based Power Ups. Star Server use allowed.
<Game> Battle opponents without card-based Power Ups. Star Server use not allowed.
<Game> Battle opponents regardless of strength.
<Game> Battle opponents with similar strength.
<Game> Battle opponents who have their Wave Battle Attack Stars ON.
<Game> Battle opponents who do not have their Wave Battle Attack Stars ON.
<Ace> Use these criteria to search for an opponent?
<Game> Searching for an opponent. Depending on criteria, an opponent may not be found.
<Game> Do you want to cancel your search for a Wi-Fi opponent? {10}{EC}{00}{00}Yes {10}{EC}{01}{00}No {0F}{EC}{00}{00}{00}{00}{02}{00}{00}{00}
<Ace> You have to save before you enter this menu. Do you want to save? {10}{EC}{00}{00}Yes {10}{EC}{01}{00}No {0F}{EC}{00}{00}{00}{00}{02}{00}{00}{00}
<Game> OK to disconnect from Nintendo Wi-Fi Connection? {10}{EC}{00}{00}Yes {10}{EC}{01}{00}No {0F}{EC}{01}{00}{00}{00}{02}{00}{00}{00}
<Game> Disconnecting from Nintendo Wi-Fi Connection.
<Game> Disconnected from Nintendo Wi-Fi Connection.
<Ace> The other party canceled the match.
<Ace> 1 battle showdown determines the winner.
<Ace> Best 2 out of 3 battles is the winner.
<Ace> Send a short message to your opponent.
<Ace> The other party canceled the match. 
Search for a new opponent? {10}{EC}{00}{00}Opponent search {10}{EC}{01}{00}Opponent list {10}{EC}{02}{00}Disconnect {0F}{EC}{02}{00}{00}{00}{00}{00}{00}{00}
<Ace> The other party canceled the match. 
Search for a new opponent? {10}{EC}{00}{00}Opponent list {10}{EC}{01}{00}Disconnect {0F}{EC}{01}{00}{00}{00}{00}{00}{00}{00}
<Game> Searching for an opponent. Depending on the criteria, an opponent may not be found.
<Ace> Use the +Control Pad to choose a message. Use the A Button to send.
<Ace> You can only have up to 8 Opponent Noises. Choose an Opponent Noise to overwrite.{01}{E1}
<Game> Do you want to abandon this Opponent Noise? {10}{EC}{00}{00}Yes {10}{EC}{01}{00}No {0F}{EC}{01}{00}{00}{00}{00}{00}{00}{00}
<Ace> You have abandoned this Opponent Noise.{01}{E1}
<Ace> Time is up. You have no choice but to abandon this Opponent Noise.{01}{E1}
<Game> Overwrite this one? {10}{EC}{00}{00}Yes {10}{EC}{01}{00}No {0F}{EC}{01}{00}{00}{00}{00}{00}{00}{00}
<Ace> Codename: {2C}{E1} Type: {2D}{E1}
<Ace> Abandon and delete this Opponent Noise?
<Ace> Opponent Noise overwrite has been completed.{01}{E1}
<Ace> The other party is saving Opponent Noise. Let's wait for them to finish up.
<Ace> That Opponent Noise has already been registered. 
Do you want to unregister it and overwrite it? {10}{EC}{00}{00}Yes {10}{EC}{01}{00}No {0F}{EC}{01}{00}{00}{00}{00}{00}{00}{00}
<Game> Connecting to other party...
