<Mr.King> It appears your card input was successful. 
Oh? What's this...? 
Contained within this card is some VERY powerful noise. 
It seems you have obtained something very valuable. 
Be careful how you use it. 
<Mr.King> This card has been entered already. 
<Mr.King> Only one card bearing the Star Force logo can be 
entered automatically at a time. 
Do you wish to overwrite this card data? 
{10}{EC}{00}{00}Yes {10}{EC}{01}{00}No {0F}{EC}{00}{00}{00}{00}{02}{00}{00}{00}
<Mr.King> What a pity... The number of cards you can register is limited to five. 
If you want to enter a new card you'll have to delete an old one. 
Would you like to delete a card? 
{10}{EC}{00}{00}Yes {10}{EC}{01}{00}No {0F}{EC}{00}{00}{00}{00}{02}{00}{00}{00}
<Mr.King> Do you want to enter a new card or cancel? {10}{EC}{00}{00}Enter {10}{EC}{01}{00}Cancel {0F}{EC}{00}{00}{00}{00}{02}{00}{00}{00}
<Mr.King> You cannot enter cards of the same suit and number at the same time. 
Do you want to overwrite the previous card? 
{10}{EC}{00}{00}Yes {10}{EC}{01}{00}No {0F}{EC}{00}{00}{00}{00}{02}{00}{00}{00}
<Mr.King> Very well... Your card data will be overwritten. 
<Mr.King> Card data overwrite has been canceled... 
<Mr.King> Your customized data will be overwritten. 
<Mr.King> Your customized data has been changed successfully. 
<Mr.King> Ho ho... This card combination "Noise Band" is a very 
special card combination. 
<Mr.King> Two pair. Not bad. I see you are learning to use 
card combinations to control Noise. 
<Mr.King> Three of a kind. Not bad. I see you are learning to 
use card combinations to control Noise. 
<Mr.King> Ho ho... This combination is a Straight. 
{06}{E1}<Prez>
<Mr.King> What a surprise! A Heart Flush. 
{06}{E1}<Prez>
<Mr.King> What a surprise! A Diamond Flush. 
{06}{E1}<Prez>
<Mr.King> What a surprise! A Spade Flush. 
{06}{E1}<Prez>
<Mr.King> What a surprise! A Club Flush. 
{06}{E1}<Bud>
<Mr.King> Impressive! A Full House. 
{06}{E1}<Prez>
<Mr.King> Very impressive! Four of a Kind. 
{06}{E1}<Prez>
<Mr.King> My my, a Straight Flush! Someone like you would be 
a valuable asset to my organization. 
{06}{E1}<Bud>
<Mr.King> What's this? A Royal Flush! Most impressive. 
I could use someone like you to lead my organization... 
{06}{E1}<Prez>
<Mr.King> Oh... Five of a Kind, your ferocity is equal to that of Meteor G.... 
{06}{E1}<Prez>
<Mr.King> Hmm? It seems you've gotten {2C}{E1} as an additional bonus... 
You've gotten very good at using card combinations to control Noise! 
<Mr.King> Hmm? It seems you've gotten {2C}{E1} and {2D}{E1}  as an additional bonus... 
You've gotten very good at using card combinations to control Noise! 
<Mr.King> What a pity... It seems that by updating this 
card you have lost your Noise Band. 
<Mr.King> It seems that Noise is eating away at your body... 
In battle you should use caution. 
<Mr.King> Do you really wish to delete this card data? {10}{EC}{00}{00}Yes {10}{EC}{01}{00}No {0F}{EC}{00}{00}{01}{00}{02}{00}{00}{00}
<Mr.King> Card data has been deleted. 
