<Dr.Goodall> ...... 
Oh, my. It looks like you turned off the power in the middle of a 
Wi-Fi head-to-head match.  {2C}{E1}, that was very unsporting of you. 
Turning off the power like that will cause the other party to get 
a communication error. Don't you know that? 
Wave Battlers must fight fairly all the way till the end, no matter what. 
What's that you say? 
You didn't do it on purpose? It was an accident? 
Well, I suppose things like that can happen now and again. 
I apologize for accusing you of playing unfairly. 
But did you know that even when you turn the power off in the middle 
of a Wi-Fi head-to-head match, even accidentally, 
it is counted in the Wi-Fi battle results record as a Null Battle? 
If you get too many null battles, people will think of you as a person 
who always turns the power off when you are losing. 
And we wouldn't want that now, would we? 
So from now on, please be very careful. 
Oh, dear. There I go again running off at the mouth. 
You know how Arthur gets when I just ramble on and on. 
...... 
So move on, get back out there and have some Wave Battle fun! 
<Dr.Goodall> It's a shame that we have to meet back here like this, {2C}{E1}. 
I don't like to have to come here and lecture you, you know. 
So, where should I begin? Oh, I know. Have you ever been in love? 
Well I may not look it now, but when I was your age, I was a very popular girl. 
I couldn't take 10 steps on <Alohaha> Beach without some boy cat-calling me. 
*chuckle* But that's a whole 'nother story. What I want to tell you is 
there's a difference between infatuation and love. 
To be infatuated with someone is easy. 
Your heart goes pit-a-pat when you see that person, but it isn't 
necessary to get to know how they feel. 
It's a one-way emotion. 
But love, on the other hand, is different. 
When you love someone, you care about how that person feels; what makes them 
happy as well as what makes them sad. 
It takes effort to love, and it's not something you do alone. 
I know now that those boys on the beach were infatuated with me, 
but probably weren't in love with me. 
They were just children. And so it is with Wave Battling. 
Turning off the power when you are going to lose... That's a very 
mean and quite frankly, selfish thing to do. 
Great Wave Battlers think about the feelings of their opponents. 
Even when we lose, we must be thankful for the mere opportunity to have battled. 
Do you understand? 
If we battle fair and square, we create an atmosphere where everyone has fun. 
I think you've got the message, so I'll cut my lecture short this time. 
Thank you for paying attention. 
OK, get back out there and do your best! 
<Dr.Goodall> ...... 
...... ...... 
Why.... you little! Get your act together right this instant! ......  
*chuckle* I bet I gave you a scare, didn't I? 
I was once asked if I would be an actress. 
But never mind that now. 
Once again, you turned off the power in the 
middle of a Wi-Fi head-to-head match. 
And this time I can't just stand by and look the other way. 
This time there will be consequences. {2C}{E1}, I'll give you a choice. 
I can take away your right to get Illegal Cards. 
That means that all Illegal Cards that you get will have to be 
surrendered to WAZA and the Satella Police Department. Or, 
I can confiscate all the Battle Cards currently in your possession. 
Which is it going to be? {10}{EC}{00}{00}Give up right to Illegal Cards {10}{EC}{01}{00}Give up all Battle Cards {10}{EC}{02}{00}Apologize profusely {0F}{EC}{02}{00}{00}{00}{00}{00}{00}{00}{1B}{EC}{00}{00}{03}{00}{1B}{EC}{03}{00}{04}{00}{04}{EC} 
<Dr.Goodall> {2C}{E1}, that isn't an answer to my question. {0F}{EC}{01}{00}{00}{00}{00}{00}{00}{00}{1B}{EC}{00}{00}{03}{00}{06}{E1}{04}{00}
<Game> You have given up your right to Illegal Cards! 
<Game> All of your Battle Cards have been confiscated! 
<Dr.Goodall> This should help you stop making the same mistake over and over again. 
Well, I guess I'm done here. 
Good-b... What's that you say? 
If you're really sorry, will I undo your punishment? 
That's going to be a little tough, youngin'. 
The world has rules so that order is preserved, 
and punishments for those who break them. 
You're sorry from the bottom of your heart? 
Well I don't know... 
...... 
...... 
...... 
OK, but I want to be sure that you are genuinely sorry. 
So, I'm going to give you some time to think about what you have done 
and do some soul-searching. 
Understand? 
OK, start! 
<Game> Soul-searching... {00}{E1}{10}{0E}{10}{E2}{1C}{02}
<Dr.Goodall> OK. You did very well, {2C}{E1}. I'll let you off this time without any penalty. 
<Game> Your right to get Illegal Cards has been restored! 
<Game> All of your Battle Cards have been restored! 
<Dr.Goodall> I'm only going to do you this favor once. 
So move on, get back out there and have some Wave Battle fun! 
<Dr.Goodall> ...... 
There's nothing else I can say to you. Take a two- 
minute time out and think about what you've done. 
<Game> Soul-searching... {00}{E1}{20}{1C}{10}{E2}{1C}{02}
<Dr.Goodall> OK, that's enough. 
So move on, get back out there and have some Wave Battle fun! 
