<Game> You can become Brothers with Friends close by 
using the wireless communications capabilities of your Nintendo DS.{15}{E1} 
<Game> From the Network menu, select "DS Wireless Play"... 
<Game> Here, if you select "Wave Battle" or "Brother Invitation", you 
can become Brothers after you've had a head-to-head Wave Battle with your Friend. 
<Game> But if you want to become Brothers with a friend who is far away, 
you can do it via Nintendo Wi-Fi Connection. 
<Game> Select "Nintendo Wi-Fi  Connection" from the Network Menu.{15}{E1} 
<Game> Here, select "Friend Code Invt" and follow the on-screen instructions. 
If you're not sure about your Online Setup, you  should ask an adult for help. 
If you become Real Brothers with someone in your Brother Band, 
you'll be able to view their personal profile. 
<Game> This is {2E}{EC}'s Profile Screen. 
You can access this screen by touching your icon on the Brother Screen or by 
touching the Mega Man icon on the Mega Man Screen. 
This screen is where you can check your personal information and details. 
<Game> Your Codename, Message and Link Power are displayed on in that order. Your 
message is the first thing a Real Brother sees when they look at your profile. 
Why don't you try writing a message to your Brothers now? 
<Game> Well, did your message come out the way you wanted it to? Your Link Power should 
go up after you become Brothers with Luna, Bud, and Zack. 
<Game> White Cards can be downloaded when at Wave Stations. 
They come in sets of 4. Since they're white, they're easy to select. 
Be sure to go and check out a Wave Station and download a set. 
<Game> Your Team Name, Team Logo, and Purpose are generally filled in automatically. 
But one day, when you fulfill your Purpose, 
you'll be able to freely edit your Team Name, Team Logo, and Purpose. 
Real Brothers can become part of the same Team by 
choosing the same Team Name. 
<Game> This screen displays online battle results and other battle-related information. 
<Game> For "Favorites", you can either choose your favorite 
Battle Card from a list or enter them manually. 
Why don't you go ahead and set up your "Favorites" now? 
<Game> That was a nice set up. 
As you can see, by taking a look at this screen you can 
learn some pretty interesting things about your friends. 
This concludes the explanation of Brother Bands and Profiles. 
<Prez> OK, so let's you and I form a Brother Band right here and now. 
{10}{E2}{43}{02} 
<Game> Geo became Brothers with {A3}{E2}. 
Geo's Link Power has increased by 60! 
<Prez> I look forward to being your Brother for many years to come. 
Oh, and don't forget to form a Brother Band with Zack and Bud as well. 
