<Harry.Sasoon> I'm looking for people that want to trade Sonia Cards! 
<Harry.Sasoon> Everyone is so into trading Battle Cards... 
But I think Sonia Cards are way cooler. 
<Geo> Umm... 
Is something wrong? 
<Harry.Sasoon> Yes, in fact, there is! I'm a HUGE, HUGE Sonia fan. 
Have you ever heard of Sonia Cards? 
I've been collecting them since Sonia first hit it big. 
But I've never been able to get my hands on the "Little Devil Sonia" card. 
I wish there was someone who would trade one to me for my "Sonia Wink" card. 
{17}{EC}{00}{00} 
<Game> Help this person? {05}{EC}{00}{00}{04}{00}  {06}{EC}Yes   {09}{EC}No 
{17}{EC}{02}{00}{11}{EC}{00}{00}{05}{00}{11}{EC}{03}{00}{06}{00}
<Geo> If you'd like, I could go find someone who wants to trade Sonia Cards with you. 
<Harry.Sasoon> Really!? That would be so great! 
I'll let you take the "Sonia Wink" card with you. 
{0A}{E1}{47}{16}{82}{E1}<Zack> {01}{00}{A1}{E1} 
<Game> {35}{EC} got: "{89}{E5}"! 
<Harry.Sasoon> I think there are other Sonia Card fans at school. 
{0A}{E1}{00}{16}{20}{EC}{D0}{10}
<Harry.Sasoon> Maybe I should give up... 
{0B}{E1}{2F}{16}
<Harry.Sasoon> Did you already find a "Little Devil Sonia" card? 
{17}{EC}{00}{00} 
<Game> Cancel this request? {05}{EC}{00}{00}{04}{00}  {06}{EC}Yes   {09}{EC}No 
{17}{EC}{02}{00}{11}{EC}{00}{00}{08}{00}{11}{EC}{03}{00}{09}{00}
<Harry.Sasoon> I see... Let me know if you change your mind. 
{0B}{E1}{2F}{16}{0B}{E1}{00}{16}{0B}{E1}{01}{16}{0B}{E1}{47}{16}{0B}{E1}{49}{16}{0B}{E1}{48}{16}{0B}{E1}{4A}{16}{82}{E1}<Zack> {FF}{FF}{82}{E1}<Sonia> {FF}{FF}{82}{E1}<Solo> {FF}{FF}{82}{E1}<Mr.King-2> {FF}{FF}{21}{EC}{D0}{10}
<Harry.Sasoon> Tell me when you find it! 
<Harry.Sasoon> Awesome! 
I've been looking for a "Little Devil Sonia" card for forever! 
Sweet, I finally completed my set! Thank you! 
Would you mind being my Brother? 
<Geo> I'd love to! 
{6E}{E1}{00}{00}<Chery.Blosom> 
<Game> Geo and {E0}{E2} formed a Brother Band! 
Geo's Link Power went up by 40. 
<Geo> Thanks. 
<Harry.Sasoon> Sweet... My set is finally complete! Thank you, thank you! 
<Jack.Flask> Hey... Is that Sonia Card a "Sonia Wink" card!? 
I've been looking for that card for a long time! 
Would you trade it to me for my "Tennis Outfit Sonia" card!? 
<Geo> Hmm... What should I do? 
<Mega> Maybe if you trade around with a bunch of people, you'll 
eventually get the one you want. 
<Geo> Good point. I'll do it. 
{0A}{E1}{48}{16}{82}{E1}<Zack> {FF}{FF}{82}{E1}<Sonia> {01}{00}{A1}{E1} 
<Game> {35}{EC} got: "{8A}{E5}"! 
<Jack.Flask> This is so awesome! 
Did you say that you don't know any other Sonia Card traders? 
Why don't you check <Echo.Ridge>? 
<Mary.McLovin> I really enjoy collecting Sonia Cards. 
It looks like you don't have the card I need. 
<Mary.McLovin> Wait a minute... 
Is that the "Tennis Outfit Sonia" card? 
She's so cute in it! Sonia is just the greatest, isn't she!? 
Will you trade it to me for this "Sonia the Acrobat" card!? 
<Geo> Sure! 
{0A}{E1}{49}{16}{82}{E1}<Sonia> {FF}{FF}{82}{E1}<Solo> {01}{00}{A1}{E1} 
<Game> {35}{EC} got: "{8B}{E5}"! 
<Mary.McLovin> This is really awesome of you! Thanks! 
You want to know where other Sonia Card fans are? 
Sorry, but I don't know of any close by. 
)Collecting Sonia Cards is my biggest hobby! 
It's too bad you don't have the card I want. 
)Hey, you! 
Is that card in your hand a "Sonia the Acrobat"!? 
That's pretty rare and hard to find. 
If you don't mind... 
Can I trade you this "Little Devil Sonia" for it? 
<Geo> Whoa! That's the card I need. 
I'll definitely trade with you! 
{0A}{E1}{4A}{16}{82}{E1}<Solo> {FF}{FF}{82}{E1}<Mr.King-2> {01}{00}{A1}{E1} 
<Game> {35}{EC} got: "{8C}{E5}"! 
<Geo> Let's go take this card to to its new owner. 
)That was such a sweet trade. 
