<Angel.Wise> I really want Belle's autograph!! 
<Angel.Wise> Are you a Sonia fan? Or maybe a Belle fan? 
I'm like such a huge fan of Belle! 
<Geo> Umm... Are you really that big of a Belle fan? 
<Angel.Wise> Maybe the biggest in the world! 
Everyone is always going on and on about Sonia, but Belle 
has this special quality and charm to her. 
By the way, do you really know Belle? I heard that you met her before! 
<Geo> Well, yeah... 
<Angel.Wise> Then I'm begging you!! 
Would you please ask for her autograph for me? 
{17}{EC}{00}{00} 
<Game> Get the autograph for her? {05}{EC}{00}{00}{04}{00}  {06}{EC}Yes   {09}{EC}No 
{17}{EC}{02}{00}{11}{EC}{00}{00}{05}{00}{11}{EC}{03}{00}{06}{00}
<Angel.Wise> Really!? 
This is so great! I can't believe it! 
I'm too excited to move! 
{0A}{E1}{04}{16}{0A}{E1}{4F}{16}{20}{EC}{D2}{10}
<Angel.Wise> I guess it was too much to ask of you... 
{0B}{E1}{31}{16}
<Angel.Wise> Belle's autograph... This is so exciting! 
{17}{EC}{00}{00} 
<Game> Cancel this request? {05}{EC}{00}{00}{04}{00}  {06}{EC}Yes   {09}{EC}No 
{17}{EC}{02}{00}{11}{EC}{00}{00}{08}{00}{11}{EC}{03}{00}{09}{00}
<Angel.Wise> Huh!? You can't get it? That really stinks. 
{0B}{E1}{31}{16}{0B}{E1}{04}{16}{0B}{E1}{05}{16}{0B}{E1}{4F}{16}{0B}{E1}{50}{16}{0B}{E1}{51}{16}{0B}{E1}{52}{16}{82}{E1}<(Queen)Tia> {FF}{FF}{82}{E1}<Joker> {FF}{FF}{21}{EC}{D2}{10}
<Angel.Wise> I'll be waiting! 
<Geo> I'm back. 
And I brought Belle's autograph. 
<Angel.Wise> Oh.{16}{E1} My.{16}{E1} Goodness!{16}{E1} 
This really is Belle's autograph!! This is so sweet! 
Thank you so much, Geo! Please become my Brother! 
<Geo> Sure, sounds good. 
{6E}{E1}{00}{00}: 
<Game> Geo and {DA}{E2} formed a Brother Band! 
Geo's Link Power went up by 40. 
<Angel.Wise> What...? Umm, it says "To Geo" above the signature... 
<Geo> Darn it! 
<Angel.Wise> I'll never stop being Belle's biggest fan! 
<Belle> Oh...! 
You're a friend of Sonia's, right!? 
<Geo> Yeah! Nice to meet you! 
<Belle> Nice to meet you, too! Your name is Geo, right? 
<Geo> Whoa! You know my name? 
<Belle> Y-Yep. 
{13}{EC}(Sonia is always talking  about you, so it wasn't  very hard to remember.) 
By the way, what are you up to over here today? 
<Geo> Well, you see.. Hmm, I don't know how to put this, but... 
I need your autograph. 
<Belle> ... 
<Geo> *heart pounding* {13}{EC}(Was that too  out of the blue?) 
<Belle> Sure, no problem! 
I'm more than happy to help a friend of Sonia's! 
<Geo> Great. 
<Belle> However... 
<Geo> Yeah? 
<Belle> I have something that I'd like to ask of you too. 
<Mega> {13}{EC}(I wasn't expecting this.) 
<Belle> Mega Man saved Ice from a really bad situation, recently. 
And now I'm a really big fan of his! 
So I was hoping that I could get Mega Man's autograph... 
<Geo> {13}{EC}(Hmm...  Does she know  that I'm Mega Man!?) 
<Belle> Sonia hinted to me that you might be able to help. 
<Geo> Haha... I see. {13}{EC}(Sonia...!) 
<Belle> Do you mind doing this for me? 
<Geo> Not at all... 
<Mega> (All you have to do is  sign a piece of paper  or something, right?) 
<Geo> Sit tight here for a while. I'll contact Mega Man, but it could take a little while. 
<Belle> Awesome! 
But Ice is starting to rub off on me. I can't believe I asked so straightforwardly. 
<Geo> {13}{EC}(What should I do?) 
{13}{EC}(If I sign something how I  am now, it will just be a  Geo Stelar autograph...) 
{0A}{E1}{50}{16}
<Belle> I'm really sorry that I asked so much of you. 
<Geo> Here you go. 
<Belle> Wow! 
You really got Mega Man's autograph! 
Let me give you my autograph in return! 
<Game> *scribble* 
<Mega> (She must have to sign  a ton of these things...) 
{82}{E1}<Joker> {01}{00}{A1}{E1} 
<Game> {35}{EC} got: "{8F}{E5}"! 
<Geo> Thanks a bunch. I know you have a busy schedule! 
<Belle> No worries. Anything for a friend of Sonia's! 
{0A}{E1}{52}{16}{82}{E1}<(Queen)Tia> {FF}{FF}
<Belle> Let's always be there for Sonia when she needs us. 
<Geo> I've never signed an autograph before. 
<Mega> Heh heh... Let me do it! 
<Geo> Not a chance. 
Even I can make it look better than your scribble. 
<Geo> Nice, all done! 
<Mega> It's a little shaky looking, don't you think? 
<Geo> This is the best that I can do! Let's just get it back to Belle. 
{0A}{E1}{51}{16}{82}{E1}<(Queen)Tia> {01}{00}{A1}{E1} 
<Game> {35}{EC} got: "{8E}{E5}"! 
<Mega> A picture might have been better than white paper... 
