=I wonder if anyone knows a beautiful beach location to film the show? 
=I've been up for two nights in a row with overtime work. I'm so exhausted... 
<Geo> Umm... 
I know a nice place or two. 
=Really!? 
I absolutely must find a fantastic spot to film the new TV show. 
But I just haven't had the time to look thoroughly. 
I know I shouldn't expect this of you... 
But would you please go take a picture of a beautiful beach area that you know? 
{17}{EC}{00}{00} 
<Game> Accept her request? {05}{EC}{00}{00}{04}{00}  {06}{EC}Yes   {09}{EC}No 
{17}{EC}{02}{00}{11}{EC}{00}{00}{05}{00}{11}{EC}{03}{00}{06}{00}
=Really!? Honestly!? In that case... 
While you're doing that, could you take a picture of 
a building that would make a good setting, too? 
<Geo> Sure thing! 
<Mega> (If you're looking for the  perfect beach area, then 
 over there is the only  place worth going, huh?) 
{0A}{E1}{54}{16}{82}{E1}<Heartless> {01}{00}{A1}{E1} 
<Game> {35}{EC} got: "{90}{E5}"! 
{0A}{E1}{06}{16}{20}{EC}{D3}{10}
=I'm so sorry to bother you! 
{0B}{E1}{32}{16}
=Oh, did you get the picture already? 
{17}{EC}{00}{00} 
<Game> Cancel this request? {05}{EC}{00}{00}{04}{00}  {06}{EC}Yes   {09}{EC}No 
{17}{EC}{02}{00}{11}{EC}{00}{00}{08}{00}{11}{EC}{03}{00}{09}{00}
=Oh, I see. I'll just have to get it done myself... 
{0B}{E1}{32}{16}{0B}{E1}{06}{16}{0B}{E1}{07}{16}{0B}{E1}{54}{16}{0B}{E1}{55}{16}{0B}{E1}{56}{16}{82}{E1}<Heartless> {FF}{FF}{82}{E1}!{FF}{FF}{82}{E1}"{FF}{FF}{21}{EC}{D3}{10}
=The picture needs to be of the perfect spot! 
<Geo> I took the pictures for you! 
=Really!? Thank you! 
Let me see, let me see. 
It's beautiful! Kid, you've got what it takes to be a professional! 
I'm definitely going to have the TV show filmed here! 
I'd be in so much trouble without your help. Thank you. 
Would you mind being my Brother? 
<Geo> Is that OK with you? 
=Definitely. You're one of the staff members, now. 
{6E}{E1}{00}{00}z 
<Game> Geo and {1A}{E3} formed a Brother Band! 
Geo's Link Power went up by 40. 
=Don't miss even one episode! 
=The next TV series is going to be filmed in <Alohaha>. 
ODoesn't the ocean look so beautiful from here!? 
<Mega> (This is the place to take  a picture, kid! Press the  A Button to snap a shot!) 
ODoesn't the ocean look so beautiful from here!? 
<Geo> Alright, let's take the picture from here! 
<Game> *snap* 
<Geo> I think I got a good shot. The water is so clear, huh? 
Once we have a picture of both the beach and a building, let's go back to <Studi.WBG>. 
{82}{E1}!{01}{00}{A1}{E1} 
<Game> {35}{EC} got: "{91}{E5}"! 
+Isn't the sight of <Castello.Alohaha> from here just amazing? 
<Mega> (That's the perfect building,  kid! Press the A Button  to take a picture!) 
+Isn't the sight of <Castello.Alohaha> from here just amazing? 
<Geo> OK! Let's take the picture from here! 
<Game> *snap* 
<Geo> That's a sweet shot! That was the perfect angle to take of <Castello.Alohaha>. 
Once we have a picture of both the beach and a building, let's go back to <Studi.WBG>. 
{82}{E1}"{01}{00}{A1}{E1} 
<Game> {35}{EC} got: "{92}{E5}"! 
