<Prez> Have you heard the rumors about <Spica.Mall>? 
<Prez> 
<Geo> Umm... What's going on in <Spica.Mall>? Something bad? 
<Prez> {13}{EC}(Ugh...  Just talking about it  makes me feel sick.) 
Everyone is talking about it. 
If you knock three times on the door of the girls' bathroom, then chant a spell... 
<Geo> Yeah...? 
<Prez> A ghost will appear! 
<Geo> A ghost!? 
Haha... 
You don't believe that, do you, Prez? 
<Prez> Who do you think I am!? 
I would never believe in that kind of childish stuff! 
{13}{EC}(Actually, I can't even  sleep at night anymore.) 
<Geo> Then I guess there's no reason to go check it out. 
<Prez> W-W-Wait a second! 
I'm fine, but some students are really scared. I can't let this go unchecked! 
Since you're a hero, Geo... Go check it out for me, please. 
{17}{EC}{00}{00} 
<Game> Accept her request? {05}{EC}{00}{00}{04}{00}  {06}{EC}Yes   {09}{EC}No 
{17}{EC}{02}{00}{11}{EC}{00}{00}{05}{00}{11}{EC}{03}{00}{06}{00}
<Geo> If it's really that big of a deal, then I'll do it. 
<Prez> Thanks, Geo. 
<Geo> So you knock on the door of the girls' bathroom, then chant a spell... 
What's the spell? 
{A0}{E1}{04}{00} 
<Prez> I have no clue! 
Even if you find out what it is, don't you dare say it in front of me. 
I'll stop being your Brother! 
<Mega> {13}{EC}(She's the one that's  actually scared, isn't she?) 
<Geo> Fine. I'll have to ask someone at school... 
{0A}{E1}{14}{16}{0A}{E1}{7D}{16}{20}{EC}{DA}{10}
<Prez> I thought you were a man!? 
Geez... 
Well, if you change your mind, let me know! 
{0B}{E1}{39}{16}
<Prez> Did you find out the truth behind the ghost? 
{17}{EC}{00}{00} 
<Game> Cancel this request? {05}{EC}{00}{00}{04}{00}  {06}{EC}Yes   {09}{EC}No 
{17}{EC}{02}{00}{11}{EC}{00}{00}{08}{00}{11}{EC}{03}{00}{09}{00}
<Prez> A real man would never take back his word! 
{0B}{E1}{39}{16}{0B}{E1}{14}{16}{0B}{E1}{15}{16}{0B}{E1}{7D}{16}{0B}{E1}{7E}{16}{0B}{E1}{7F}{16}{0B}{E1}{80}{16}{0B}{E1}{81}{16}{82}{E1}){FF}{FF}{21}{EC}{DA}{10}
<Prez> Thanks, Geo. 
<Prez> It was a prank by viruses? 
{13}{EC}(Phew...) 
I figured it had to be something like that! 
At any rate, thanks so much for helping, Geo. 
Here's something for helping. 
{87}{E1}{4B}{01}{01}{00}{A1}{E1} 
<Game> {35}{EC} got: "{57}{E6}{D2}{E6}"! 
<Game> Geo's Link Power went up by 40. 
<Prez> {13}{EC}(Geo is such  a reliable guy.) 
<Geo> Do you know anything about the rumors about the girls' bathroom in <Spica.Mall>? 
<Mary.McLovin> !! 
Actually... I heard a voice in the girls' bathroom in <Spica.Mall>! 
<Geo> A-A voice? 
{13}{EC}(This is getting creepy.) 
<Mary.McLovin> It felt like it was following me around! I was so scared! 
<Geo> If you happen to know the necessary spell, would you please teach it to me? 
<Mary.McLovin> This is what you should say... 
{0A}{E1}{7E}{16}{82}{E1}){01}{00}{A1}{E1} 
<Game> {35}{EC} got: "{99}{E5}"! 
<Mary.McLovin> I'm not taking any responsibility for what happens to you! 
<Mega> It looks like the viruses were having fun scaring a bunch of humans. 
There's no way ghosts exist on this planet! 
<Geo> How do you know? You're not from Earth! 
Let's go back to Luna. 
