+I want to make up for what I did back in the day... 
+What year did they build Echo Ridge Elementary? Hmm... 
I grabbed the little bit of money that I had, then left 
my home to become a carpenter. 
Those were the days. 
<Geo> Umm... Is something wrong? 
+Why hello there. 
I used to be a carpenter when I was a young man. 
I actually helped build Echo Ridge Elementary... 
I was so happy to finish the building that I put graffiti up on one of the walls. 
I wrote "The school is done! Yahoo!". 
<Geo> Graffiti can get you into a lot of trouble... 
<Mega> Hey, kid... Let's blow this popsicle stand. He's boring me. 
+W-Wait a minute! 
Now that I'm this old, I'm really sorry for what I did as a young man. 
I would like to remove the graffiti I drew, but I don't remember where it is. 
And my legs hurt, too... 
Would you please find and delete the graffiti for me? 
{17}{EC}{00}{00} 
<Game> Help this person? {05}{EC}{00}{00}{04}{00}  {06}{EC}Yes   {09}{EC}No 
{17}{EC}{02}{00}{11}{EC}{00}{00}{05}{00}{11}{EC}{03}{00}{06}{00}
<Geo> Sure. I'll get right to it. 
+Well aren't you a nice boy. Thank you. 
{82}{E1}*{01}{00}{A1}{E1} 
<Game> {35}{EC} got: "{9A}{E5}"! 
+I could swear that the graffiti is on the roof somewhere. 
<Geo> Understood! I'll head right there! 
{0A}{E1}{87}{16}{0A}{E1}{18}{16}{20}{EC}{DC}{10}
+*sigh* What should I do? 
{0B}{E1}{3B}{16}
+Oh, did you remove the graffiti for me? 
{17}{EC}{00}{00} 
<Game> Cancel this request? {05}{EC}{00}{00}{04}{00}  {06}{EC}Yes   {09}{EC}No 
{17}{EC}{02}{00}{11}{EC}{00}{00}{08}{00}{11}{EC}{03}{00}{09}{00}
+Oh, I was really counting on you... 
{0B}{E1}{3B}{16}{0B}{E1}{18}{16}{0B}{E1}{19}{16}{0B}{E1}{87}{16}{0B}{E1}{88}{16}{0B}{E1}{89}{16}{0B}{E1}{8A}{16}{0B}{E1}{AB}{16}{0B}{E1}{AC}{16}{0B}{E1}{AD}{16}{82}{E1}*{FF}{FF}{21}{EC}{DC}{10}
+Thank you, sonny. 
+Thank you for helping me to make up for what I did oh so long ago... 
{85}{E1}{01}{00}{01}{00}{A1}{E1} 
<Game> {35}{EC} got: "{E1}{E5}"! 
HP capacity has been increased! 
+Now I have finally made up for what I did. 
<Mega> You do realize someone else did all the work for you? 
<Geo> I'm sure you still have a lot of life left to live. 
+Would you be my Brother? You're such a reliable young man. 
{6E}{E1}{00}{00}$ 
<Game> Geo and {C4}{E2} formed a Brother Band! 
Geo's Link Power went up by 40. 
+This is a great new start for me. 
+Actually, I also left graffiti around <Spica.Mall> when that was built, too. 
<Geo> Really!? You can't be serious!! 
+I'm fairly certain that I did it near a Wave Station... 
I wish I could go remove it by myself, but I think I might have a cold. 
So please do it for me. 
<Geo> Unbelievable... 
+Sorry, but I also left graffiti in <Castello.Alohaha>. 
<Mega> Give us a break, old man! 
+I'm really sorry for all the trouble. 
I want to take care of it by myself, but... 
My head kind of hurts. 
Well, more like the right side of my head hurts. 
If it's too much for you, then I'll do it! 
But if I collapse from the stress, I might never be the same again. 
So thanks for helping. 
<Geo> We might as well finish the job that we started... 
