3I so want to eat that! It's cold and sweet, and it reminds me of my childhood. 
<Geo> Darn... Time's up. 
<Mega> It melted everywhere. 
<Geo> Looks like I failed... 
Time to get psyched up and try it one more time! Let's go buy another ice cream! 
3My job is to issue {A5}{E5}s. 
If you have one of these, you can ride the Wave 
Liner to WAZA. Something ordinary people can't do. 
<Geo> Can you issue one for me? 
3Code Number 003 Geo Stelar 
Requesting ID, correct? 
<Geo> Yes! 
3Understood. However, it will take a some time to issue. 
{06}{E1}{04}{00}
<Mega> (Why don't we help out  that lady while we wait  for the ID to be issued?) 
<Mega> (It looks like you have that  lady's HELP pop-up. It  would be a great way to 
 use our time while we wait  for the ID to be issued. 
 But you are already helping  a different person with a  request at the moment...) 
<Geo> Yeah, but I'd kind of like to get that {A5}{E5} 
as soon as possible. 
<Mega> Good point. Then let's cancel the other request! 
<Geo> OK. We'll have to go back to the person who made the request to cancel it. 
<Geo> Umm... 
Is something wrong? 
3There's nothing really wrong, but... 
I absolutely love to have my mid-afternoon snack. 
Snacks eaten at work are so much more delicious than when eaten at home! 
But today I forgot to bring any snacks to work... 
Life without snacks is like french fries without ketchup! 
Well, more like cake without icing... 
<Mega> What are you craving today? 
3Without a doubt, ice cream! 
More specifically, ice cream from the {BE}{E4} in <Spica.Mall>. 
{17}{EC}{00}{00} 
<Game> Go buy her ice cream? {05}{EC}{00}{00}{04}{00}  {06}{EC}Yes   {09}{EC}No 
{17}{EC}{02}{00}{11}{EC}{00}{00}<Jack> {11}{EC}{03}{00}<(Queen)Tia>
3You will? That's fantastic! 
I'll work on getting your ID issued while you're away. 
{0A}{E1}{1A}{16}{0A}{E1}{8C}{16}{20}{EC}{DD}{10}
<Geo> Maybe I'll help another time... 
{0B}{E1}{3C}{16}
3Wow, that was fast. 
{17}{EC}{00}{00} 
<Game> Cancel this request? {05}{EC}{00}{00}{04}{00}  {06}{EC}Yes   {09}{EC}No 
{17}{EC}{02}{00}{11}{EC}{00}{00}<Heartless> {11}{EC}{03}{00}!
3*depressed* My... ice cream...! 
{0B}{E1}{3C}{16}{0B}{E1}{1A}{16}{0B}{E1}{1B}{16}{0B}{E1}{8C}{16}{0B}{E1}{8D}{16}{82}{E1}+{FF}{FF}{21}{EC}{DD}{10}
3I'll work on getting your ID issued. 
<Geo> *huff, huff* I brought the ice cream! 
3That's my favorite type of {9B}{E5}! 
You're something else, kid. 
Here's something to show you my thanks. 
{81}{E1}{E8}{03}{A1}{E1} 
<Game> {35}{EC} got: "1000 Zennys"! 
3And here is your brand new {A5}{E5}, as promised. 
With this, you can travel to and from WAZA via the Wave Liner. 
{82}{E1}5{01}{00}{A1}{E1} 
<Game> {35}{EC} got: "{A5}{E5}"! 
3I'll be able to finish the work day strong now. 
