<Chery.Blosom> I'm looking for people who want to take my quiz! 
<Chery.Blosom> Hee hee hee... I made a really great quiz. 
<Geo> I'll take your quiz! 
<Chery.Blosom> Hee hee hee... My quiz is really hard! 
{17}{EC}{00}{00} 
<Game> Take the quiz? {05}{EC}{00}{00}{04}{00}  {06}{EC}Yes   {09}{EC}No 
{17}{EC}{02}{00}{11}{EC}{00}{00}{05}{00}{11}{EC}{03}{00}{06}{00}
<Chery.Blosom> Get ready for question #1. 
Gearoid ran the 400 meter relay for his track team. 
He ran his hardest, and was able to squeeze past the person in second place. 
What place did Gearoid finish in? 
Please answer with a number. 
{7B}{E1}{01}{00}{02}{00}{08}{00}{06}{E1}{07}{00}
<Geo> I don't want to do this anymore! 
{0B}{E1}{24}{16}{0B}{E1}{41}{16}
<Chery.Blosom> That's correct! 
When the person in 3rd place passes the person in 2nd, he is now in 2nd place. 
The next question will be much harder. 
Here we go, question #2. A hot dog eating contest was held with ten people. 
Ben finished the contest 6th from the bottom. 
What place did Ben finish in? 
Please answer with a number. 
{7B}{E1}{01}{00}{05}{00} {06}{E1}{09}{00}
<Chery.Blosom> I'm sorry, that's incorrect! Please try again. 
<Chery.Blosom> That's correct! 
10 minus 6 equals 4. 
And now for the final and toughest question. 
A marathon with ten people was held on a track around a playing field. 
Greg just managed to pass the person in last place right before the finish line. 
Greg was the only person to pass the runner in last place. 
What place did Greg finish in? 
Please answer with a number. 
{7B}{E1}{01}{00}{01}{00}{0C}{00}{06}{E1}{0B}{00}
<Chery.Blosom> I'm sorry, that's incorrect! Please try again. 
<Chery.Blosom> That's correct! 
Hee hee hee... 
The first person that is capable of passing the runner in last place is the 
person in 1st place. This is called lapping a person. 
You're really smart. 
No one else has ever answered all of my questions correctly. 
I'd love to be Brothers with someone that's so smart. 
Would you mind being Brothers with me? 
<Geo> Not at all! 
{6E}{E1}{00}{00}9 
<Game> Geo and {D9}{E2} formed a Brother Band! 
Geo's Link Power went up by 40. 
<Chery.Blosom> You'll definitely have to take my next quiz once it's ready. 
<Chery.Blosom> I'm so sorry. Please try again. 
<Chery.Blosom> You'll definitely have to take my next quiz once it's ready. 
