<Bud> Go on an adventure to solve the mystery of the missing ginger beef! 
<Bud> 
<Geo> Umm... Is something wrong? 
<Bud> Geo... My ginger beef disappeared... 
<Geo> ...? 
What do you mean? 
<Bud> Well, I went to have my daily ginger beef snack... 
<Geo> Ginger beef for a snack!? 
<Bud> When I went to take a bite, I noticed that I never put any spices on top! 
So I went to the fridge to get the spices, and when I came back... 
"Noooooo!" 
My ginger beef was gone!! 
<Geo> I see... 
Maybe you actually ate it before you got the ginger? 
<Bud> I don't care how much of an eater I am, that's just not possible! It really disappeared! 
{17}{EC}{00}{00} 
<Game> Help Bud? {05}{EC}{00}{00}{04}{00}  {06}{EC}Yes   {09}{EC}No 
{17}{EC}{02}{00}{11}{EC}{00}{00}{05}{00}{11}{EC}{03}{00}{06}{00}
<Geo> This event should not be taken lightly, Budicus! 
<Bud> Who are you calling "Budicus"!? 
<Mega> This is definitely strange, though... 
Tell him you'll help, kid. This could be kind of fun. 
<Geo> True. 
OK, I'll investigate this tragedy for you, Bud. 
<Bud> Nice! Thanks, Geo! 
Oh, by the way... 
Take this. It might help in your investigation. 
{A1}{E1} 
<Game> {35}{EC} got: "{A0}{E5}"! 
<Geo> I've never seen someone carry ginger beef with them... 
<Bud> It's a microwaveable meal, but it's still pretty good! 
Go to the middle of my room and set it there as bait. 
{0A}{E1}{26}{16}{0A}{E1}{9E}{16}{82}{E1}0{01}{00}{20}{EC}{E3}{10}
<Bud> I'm counting on you, buddy. 
{0B}{E1}{42}{16}
<Bud> Did you find out what happened, Geo? 
{17}{EC}{00}{00} 
<Game> Cancel this request? {05}{EC}{00}{00}{04}{00}  {06}{EC}Yes   {09}{EC}No 
{17}{EC}{02}{00}{11}{EC}{00}{00}{08}{00}{11}{EC}{03}{00}{09}{00}
<Bud> I'm counting on you, buddy. 
{0B}{E1}{42}{16}{0B}{E1}{26}{16}{0B}{E1}{27}{16}{0B}{E1}{9E}{16}{0B}{E1}{9F}{16}{0B}{E1}{A0}{16}{0B}{E1}{A1}{16}{82}{E1}0{FF}{FF}{82}{E1}1{FF}{FF}{21}{EC}{E3}{10}
<Bud> I hope you find it! 
<Geo> I found out what happened. 
<Bud> Taurus took it!? 
Why that sneaky little... 
I'd be more than happy to make him some if he wanted! 
The more people eating ginger beef, the merrier! It even tastes better then! 
I'll surprise him with some sometime. He'll like that. 
Thanks a lot, Geo. This is for helping me! 
{A1}{E1}{87}{E1}n{01}{00} 
<Game> {35}{EC} got: "{9E}{E6}{D0}{E6}"! 
<Game> Geo's Link Power went up by 40. 
<Bud> 
<Geo> I'll set the ginger beef down here as bait. 
<Game> Geo set the ginger beef down. 
<Game> That ginger beef looks good! 
<Geo> Whoa! It disappeared! 
<Mega> Weird. 
<Geo> I wonder what is going on? 
<Taurus> Ginger beef? 
I have no clue what you are talking about. 
Mmmrrrgh! 
<Geo> No eye-witnesses, huh? 
Let's look around the room some more. 
<Taurus> S-So spicy! My mouth is on fire! 
<Geo> Taurus! So you're the thief! 
<Taurus> ...Forgive me. 
I watch Bud eat ginger beef everyday, and it just looks so good... 
I just had to try it. 
And now I'm completely hooked... 
<Mega> You must really love eating if you're willing to go that far to eat human food! 
<Taurus> Mmmrrrgh... 
What are you going to do? Are you going to tell Bud? 
<Geo> Actually, I think you should personally apologize to Bud. 
I know he'll forgive you. 
I'll let him know you want to apologize. 
<Taurus> Thanks. I'll apologize once I work up some courage. 
I hope he forgives me... 
<Geo> I'll set the ginger beef down here as bait. Hmm, should I put some spices on it? 
{17}{EC}{00}{00}{05}{EC}{00}{00}{00}{00}{3F}{FF}{3F}{FF}{06}{EC}Don't put any on {3F}{FF}{3F}{FF}{09}{EC}Put a little on {3F}{FF}{3F}{FF}{0C}{EC}Pile it on 
{17}{EC}{02}{00}{1B}{EC}{06}{00}<Geo> 
<Geo> This should be good. 
<Game> Geo set the ginger beef down. 
<Geo> This should be good. 
<Game> Geo set the ginger beef down. 
<Game> Hooooooly coooooow! 
<Taurus> That's sp-sp-spicy!! Ginger beef shouldn't taste anything like this! 
