<Candy.Bar> My Hunter-VG isn't working right! I wonder if it could be a side-effect of Noise? 
<Candy.Bar> My name's Gian Luigi! 
Virus busting is my favorite hobby. 
<Geo> Umm... Is something wrong? 
<Candy.Bar> My Hunter-VG started to go haywire while I was doing some virus busting. 
It might be broken. 
{17}{EC}{00}{00} 
<Game> Help this person? {05}{EC}{00}{00}{04}{00}  {06}{EC}Yes   {09}{EC}No 
{17}{EC}{02}{00}{11}{EC}{00}{00}{05}{00}{11}{EC}{03}{00}{06}{00}
<Geo> I know someone who's really good with electronics. I could take it to be repaired... 
<Candy.Bar> Would you really!? I don't know what to say! 
Here, take my Hunter-VG. Please be careful with it. 
{82}{E1}2{01}{00}{A1}{E1} 
<Game> {35}{EC} got: "{A2}{E5}"! 
{0A}{E1}{2C}{16}{20}{EC}{E6}{10}
<Candy.Bar> I can't do any virus busting now... 
{0B}{E1}{45}{16}
<Candy.Bar> Ah, is my Hunter-VG fixed already? 
{17}{EC}{00}{00} 
<Game> Cancel this request? {05}{EC}{00}{00}{04}{00}  {06}{EC}Yes   {09}{EC}No 
{17}{EC}{02}{00}{11}{EC}{00}{00}{08}{00}{11}{EC}{03}{00}{09}{00}
<Candy.Bar> I can't do any virus busting now... 
{0B}{E1}{45}{16}{0B}{E1}{2C}{16}{0B}{E1}{2D}{16}{0B}{E1}{A8}{16}{82}{E1}2{FF}{FF}{21}{EC}{E6}{10}
<Candy.Bar> I hope you can get it fixed! 
<Geo> Hey, I got it repaired. 
<Candy.Bar> Holy baloney! Thanks!! 
Now I can whoop some more virus butt! 
I train as much as possible. I want to get really good someday! 
<Geo> The stronger the virus you fight, the stronger the effect Noise will have. 
So don't overdo it, OK? 
<Candy.Bar> Ah, that's a good point. Thanks for the advice! 
You sound like you know a lot about battling. 
Maybe we could be Brothers? 
<Geo> Of course! 
{6E}{E1}{00}{00}d 
<Game> Geo and {04}{E3} formed a Brother Band! 
Geo's Link Power went up by 40. 
<Geo> We should exchange battle tactics and information when we have a chance! 
<Candy.Bar> I'd like to try battling with you one of these days. 
I wonder who will win!? 
<Mr.Boreal> You want me to fix a broken Hunter-VG for one of your friends? 
I think I can handle that! 
Hmm... 
The damage appears to have been caused by contact with high levels of Noise. 
Fighting strong viruses will have this sort of effect. 
Sometimes running away is the best strategy. 
Here you go, all fixed! 
<Geo> Thank you, Mr. Boreal! 
I'm going to go give it back to its owner now. 
<Mr.Boreal> Feel free to come to me for repairs anytime, Geo. 
