<Megaman> Let's go!! 
0We're right behind you, Mega Man!! 
Activate Battle Wizards!! 
<Mega> It's time to go buck wild! 
The mission: tear 'em up!! 
3The RW Shield is under fire! Come back, Mega Man!{16}{E1} 
3The RW Shield is down to 50% strength!!{16}{E1} 
3Mega Man! Please hurry back! We can't take anymore!{16}{E1} 
<Acid> The enemy's numbers are starting to thin out... 
Keep it up, Mega Man.{16}{E1} 
<Ace> Are you OK, Mega Man? 
This is the decisive moment! Hang in there! 
<Acid> The enemy's numbers have decreased even more.{16}{E1} 
<Ace> Great! Do your thing and take them out, Mega Man! 
<Megaman> Bring it on!! 
0Activate Battle Wizards!! 
<Mega> Here we go! 
The mission: tear 'em up!! 
1The CPU has been damaged! But it's still operational!!{16}{E1} 
150% of the CPU has been destroyed!! At this rate...{16}{E1} 
1The CPU is too heavily damaged! If it takes any more hits, it will...{16}{E1} 
4Can you hear me, Mega Man!?{16}{E1} 
The program will be complete very shortly! 
Please buy us the time we need! You can do this! 
{98}{00}The enemy's numbers are down by half, Chief!{16}{E1} 
4*nods* We can do this! I know it! 
{98}{00}The enemy's numbers are down even more! Keep up the good work!{16}{E1} 
<Megaman> We can't let them get by! 
0Activate Battle Wizards!! 
1Part of the elevator has been destroyed! Please take proper action!!{16}{E1} 
150% of the elevator has been destroyed! This can't continue! 
1The damage is too great!! Please hold out, Mega Man!{16}{E1} 
4...! I can't believe the number of enemies that are attacking!{16}{E1} 
4The enemy's numbers are down by 50%. Keep the pressure on, Mega Man!{16}{E1} 
4Just one last push! There's barely any of them left now! 
<Megaman> I won't let them pass, no matter what it takes!! 
0Activate Battle Wizards!! 
1The computer has been hit!! Please respond accordingly!{16}{E1} 
350% of the computer has been destroyed!!{16}{E1} 
3It's taken too much damage! Any more and it will be destroyed!{16}{E1} 
4The main computer must be protected, no matter the cost!{16}{E1} 
{98}{00}The program will be complete at any moment now! Never give up!{16}{E1} 
4A bit more... Just a bit more!!{16}{E1} 
3Get back! It's too dangerous!!{16}{E1} 
0Battle Wizards, move out!{16}{E1} 
{A8}{00}The fate of WAZA... Is in your hands!! Aaarrrgh!!{16}{E1} 
{A8}{00}Farewell... Mega Man.{16}{E1} 
{A8}{00}I apologize... I wasn't strong enough...{16}{E1} 
{A8}{00}Just what is going on!?{16}{E1} 
{A8}{00}Satella Police forever! Aaarrrgh...!!{16}{E1} 
<Acid> Ace, the enemy's numbers are rising again.{16}{E1} 
<Ace> Yeah, I've noticed. Be on your guard, Mega Man! 
{98}{00}The enemy is everywhere! There's too many to count!{16}{E1} 
4...! It's up to you, Mega Man. Hold strong! 
<Mega> Keep your head in the fight! They'll get you if you lose your cool!{16}{E1} Stay frosty, kid! 
<Mega> This is no time to cancel your EM Wave Change!!{16}{E1} 
1The enemy has changed its target! 
Please protect the computer at the top of the stairs!!{16}{E1} 
1The enemy has changed its target! 
Please protect the computer at the bottom of the stairs!!{16}{E1} 
