<Game> A Few Days Later... 
<Zack> ...It appears that most of WAZA is in a state of ruin... 
<Geo-2> Yeah... 
Not much other than the main computer is left... 
<Bud> And now that the Satella Police can't rely on WAZA for support at all, I don't 
really know what else they can do... 
<Geo-2> Yeah, they're not in a very strong position, right now... 
...H{16}{E1}-Huh? 
<Zack> {13}{EC}... 
<Geo-2> {13}{EC}... 
<Bud> {13}{EC}...? 
<Bud> W-What's up with you two!? 
Why are you so quiet!? 
<Geo> W-Well... You know... 
Right, Zack...? 
<Zack> Y-Yes... 
This must be a so-called "once in a lifetime event"! 
It's unbelievable! 
Bud{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
{A0}{E1}{03}{00}<(Queen)Tia> 
<Zack> You haven't mentioned food at all...!! 
{12}{E2}<Zack> {00}{00} 
<Bud> Gee,{15}{E1} that is a pretty rare event...! 
I can hardly believe this! 
Actually, I haven't been all that hungry, lately... 
<Bud> ...So...{16}{E1} What about that is such a big deal!? 
Are you saying that all I ever do is talk about food!? 
<Zack> ...Are you saying you don't? 
<Bud> ...I mean, I do, but... 
<Bud> B-But...! 
There comes a time in every man's life where priorities have to change! 
<Taurus> Mmmrrrggg! 
<Bud> Now that Taurus is with me... 
I've been thinking about a lot of different things...! 
<Geo> W-We were just joking, Bud... Don't take it so seriously. 
<Zack> Actually, Geo... I was being serious! 
<Geo> Z-Zack... 
<Zack> On top of that, I do believe that there is a secret brewing in our midst. 
<Geo> Huh? 
<Bud> ...Eep. 
<Zack> {13}{EC}Aha! 
Bud just cringed a bit when I mentioned something about a secret. 
<Bud> T-T-That{15}{E1} must be just your imagination! 
I'm not really someone who cringes very often. 
<Mega> He's as easy to read as a pop-up book... 
<Geo> Bud... You do seem like you're trying to hide something... 
{A0}{E1}{03}{00}<(Queen)Tia> 
<Zack> Tell us the truth! 
Are you really hiding something from us, Bud!? 
<Pedia> There is a 96% chance that he is hiding something. 
<Bud> Ack! 
<Geo> So it is true! 
That's really not cool that you are lying to us. 
But, what could you possibly be hiding? 
<Zack> Teeheehee... 
I think I already know... 
We have known each other for a long time, after all. 
<Bud> *cringe* 
<Zack> Aha! 
What Bud is hiding is...!! 
<Geo-2> ...Is...? 
<Zack> That he's on a diet!! 
<Pedia> And that he is aiming for 20% body fat! 
<Bud> {13}{EC}.... 
<Geo-2> {13}{EC}.... 
On a{15}{E1}.{15}{E1}.{15}{E1}.{15}{E1} diet...? 
<Zack> Precisely! 
If one talks about food, then they think about it and grow hungry. 
And if you try to think about other things, especially 
things that are hard to grasp, then food will never come to mind! 
That's what you've been doing, Bud... Right!? 
<Geo-2> R-Really, Bud!? 
<Bud> {13}{EC}.... 
Yeah... 
<Bud> You got me! 
I've been on a diet for a few days now! 
{12}{E2}<Mr.King-2> {01}{00} 
<Bud> I guess you caught me. I thought I could get away with it, for a bit there. 
<Geo> Way to go, Zack! 
You must have been working on your detective skills, lately! 
<Zack> Teeheehee...{15}{E1} Sherlock Zack is always first on the scene! 
<Bud> {13}{EC}... 
{13}{EC}(...Phew!  {13}{EC} Got out of that one safe!) 
<Game> ...Guys... 
<Prez> What are you all worked up about? 
<Zack> Prez! Listen to this! 
It turns out that... 
<Prez> ...I know already, Zack. 
<Zack> ...Really? 
<Prez> Bud has been doing something very sneaky, lately. 
{A0}{E1}{03}{00}<(Queen)Tia> 
<Bud> ...!? 
<Zack> E-Exactly! 
But... How do you know about it!? 
<Prez> Hehehe... 
Didn't you know that I can see right through all of you! 
<Zack> A-Amazing, Prez...{15}{E1} You're full of surprises! 
<Prez> So...! 
Let's hear what it is that you've been up to, Bud! 
<Zack> You...{14}{E1} You don't know!? 
{A0}{E1}{04}{00}<(Queen)Tia> 
<Bud> Uhhh!! 
<Bud> S-Sorry, Prez! 
I just remembered I have an appointment! Really sorry! 
Later, guys! 
<Geo> ...He took off... 
<Zack> Y-Yeah... 
<Prez> Hmph! He's so shy sometimes! 
<Geo> {15}{E1}...Shy? 
<Zack> Well... Dieting can be embarrassing... 
<Prez> What did you say? 
<Prez> ...Dieting? 
Why are you talking about dieting? 
What does that have to do with anything? 
<Geo> Well...{15}{E1} I mean... 
<Zack> Bud has been secretly dieting for a bit now... 
<Prez> ...What? 
<Prez> You morons! 
<Geo> Whoa! 
<Zack> Egads! 
<Prez> Geez... 
What part about Bud would lead you to the conclusion that he is on a diet!? 
<Geo> W-Well, you see... 
Sherlock Zack used his peerless skills to figure everything out. 
...Well, he was supposed to... 
<Zack> My reputation is ruined... 
<Geo> But if Bud isn't on a diet, then what is he doing that 
he feels he has to keep a secret from us? 
<Prez> Duh!{15}{E1} It's pretty easy to figure out once you think about what day tomorrow is! 
<Geo> ...Tomorrow! 
<Geo> (What's tomorrow, Zack?) 
<Zack> (I-I don't know...) 
(But it appears that  there is some kind of  very important event.{14}{E1}.{14}{E1}.{14}{E1}) 
<Mega> (...Grrr!  Sometimes these guys...!) 
(Hey, boys!  Why don't you try  looking at your Purpose!?) 
<Geo> (Huh? Our Purpose?) 
<Geo> Ahhhhhh! 
<Zack> "Luna for SBPrez"! 
Oh no! Tomorrow is the student body election! 
<Geo> T-That's right! 
I completely forgot about it with all the commotion lately. 
<Zack> M-Me too... 
Especially with what happened to her... 
<Geo> ...Huh!? 
<Prez> {13}{EC}... 
I hope I didn't just hear what I think I did... 
<Geo> (This is no good!  What should we do, Zack!?) 
<Zack> (For...{14}{E1} For now, let's  just apologize to her!) 
<Geo> (O-OK...!) 
Sorry...{14}{E1} Sorry, Prez! 
I can't believe that we forgot such an important day... 
We are so stupid...!! 
<Zack> I'm so sorry, Prez!! 
I've never made such a big mistake in my life! 
I trust you to judge how I should be punished!! 
<Prez> I think you guys are going a little overboard here... 
I think I'll let this mistake slide for now... 
I did cause a lot of trouble for you guys, lately... 
I still don't really remember exactly what happened... 
<Geo> (...Phew!) 
<Zack> (...Thank goodness!.) 
<Prez> Anyway... 
I want you guys to go on one last campaign run for me! 
<Geo> Campaign run? 
<Prez> Yeah! Go around one last time and secure votes for me! 
<Zack> Ah... I see. 
It's the final chance to appeal to the public, right? 
<Prez> That's right! 
And if we work very hard today, then I'm sure to win... 
And we will also fulfill our Team's Purpose!! 
<Geo> T{14}{E1}-That's true!{15}{E1} Right, Zack!? 
<Zack> R{14}{E1}-Right, Geo! 
<Prez> Alright, it's time for Team "Luna 4 Prez" to get down to business! 
...I'll do what a leader does, and wait here looking good! 
<Geo> Nice. We escaped with our lives... 
<Zack> Yeah, we were in rough waters there for a minute...! 
<Geo> But, actually... 
We never found out what Bud is really hiding from us. 
<Zack> You still don't know, Geo? 
<Geo> N-Nope... 
<Zack> Boy, Geo... 
It's quite amazing that a person as simple as you has come this far in the world! 
I don't know how else to say it. 
<Geo> Thanks, but you don't have... 
<Mega> {13}{EC}(He's not {13}{EC} complimenting you, kid!) 
{A0}{E1}{03}{00}<(Queen)Tia> 
<Zack> Aha! I figured it out! 
Bud has been acquiring votes for Prez, secretly behind our backs! 
<Geo> ...You think? Acquiring votes? 
<Zack> Definitely... 
You see, Bud didn't forget the fact that tomorrow is election day... 
And he realized that we had both forgotten about it...! 
<Geo> *gulp* 
<Zack> There is no doubt that Bud has been doing campaign runs all by himself! 
<Geo> You think!? 
<Zack> We have been completely hoodwinked, Geo... 
Prez probably knows what he has been up to. 
Prez is going to appreciate him more than us...! 
<Zack> However! 
We are still in the game! 
Let's give it our best shot! 
<Geo> Y-Yeah...{15}{E1} Sounds good... 
{13}{EC}(I'm not so sure if that's {13}{EC} the true story with Bud...) 
{13}{EC}(But either way, we {13}{EC} better do a good job {13}{EC} on the campaign run!) 
Alright, let's do this! 
Let's talk to the students and teachers that are still at school! 
<Zack> We'll cover more ground if we split up! 
Leave the students to me! 
And you take care of the teachers! 
<Geo> Roger! 
<Mega> {13}{EC}(...For cryin' out loud!) 
{13}{EC}(You guys sure are {13}{EC} feeling energetic, even 
{13}{EC} after everything we've {13}{EC} been through lately...!) 
{13}{EC}(But I guess that's what  makes you guys so fun!) 
