<Game> Several Days Earlier... 
<Jack> Hey, King! 
What the heck are you up to!? 
<Mr.King-2> Why, whatever do you mean, my dear Jack? 
<Jack> Don't play dumb with me! 
When are you going to save Sis!? 
And you better not say you don't have anything planned! 
<Mr.King-2> Now now, try not to get all flustered, Jack... 
I am currently considering what to do about your sister...! 
After all, she is my precious daughter{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
I would be a horrible father if I didn't rescue her! 
<Jack> So then... 
{A0}{E1}{03}{00}<(Queen)Tia> 
<Mr.King-2> However!! I have determined that this is not the proper time to do so, Jack... 
<Jack> W-What...!? 
<Mr.King-2> While we have struck WAZA a devastating blow... 
And it appears that the world is already in our hands, 
we have not scored a checkmate just yet. 
There's still Mega Man and Eos...{15}{E1} 
And a few other annoying little insects to deal with. 
The tide will turn even more in our favor if our next move is the right one. 
Maybe you should think about it like a strategy you use in a video game...? 
<Jack> ...Argh! 
Then hurry up and give me my next orders! 
I'll take down every last one of them!! 
<Mr.King-2> Oh, Jack... 
I am sorry to let you down, but this time I think I will have Joker go for me. 
You have just been too hot-headed, as of late. 
If this move is not perfectly followed through, then Queen 
Tia could fall into great danger. 
I hope you understand what I am saying, my dear son! 
<Jack> ...!! 
<Mr.King-2> Heartless... 
How are the preparations going? 
<Heartless> Sir... 
The Noise creation program will be completed very soon. 
But the tuning of the Noise Level controller is taking some time. 
The Noise to Real Wave process is not going very smoothly. 
<Mr.King-2> Hmm... 
So the program has proven too much for those simpletons to handle, has it? 
Ho ho ho ho! 
That is fine.{15}{E1} I will complete the program...! 
With these very hands! 
Ho ho ho ho ho ho!! 
<Jack> ...Man!! 
<Jack> That jerk... 
There's no way that he is really worried about Sis! 
I bet that he isn't planning on saving her at all!! 
So that means... 
I'll just have to do it all by myself!! 
I'm going to save you, Sis!! 
...Just hang in there a little while longer for me. 
First, I have a score to settle... 
Mega Man will pay for what he did to you!! 
