<Ace> Satella Police Commandos squad leader, Ace... 
And special members, Geo Stelar, {15}{E1}Sonia Strumm,{15}{E1} and Bud Bison... 
Reporting for duty. 
4At ease... 
Everyone, thank you for coming...! 
I would first like to thank you for helping to defend not only WAZA, but the 
Earth as well, from Dealer's attack. 
We are deeply in your debt. 
<Geo> Y-You don't have to... 
<Bud> Aww! I'm getting embarrassed...! 
<Sonia> You were impressive, Bud! 
I got to see a whole new side of you that I didn't know existed! 
<Bud> R-Really...!? 
*blushes* 
<Geo> Yeah! I was impressed, too! 
And I can hardly believe that you've been training with Ace almost every day... 
But why did you think you had to keep it a secret? 
Prez and Zack totally thought that you were up to something shifty! 
<Bud> W-Well... 
You see...! 
I wanted to train real hard, then surprise everyone with my mad skills! 
Wouldn't that have been really cool!? 
<Geo> For sure! 
Just like a comic book or video game hero! 
<Bud> Right!{15}{E1} Exactly! 
<Ace> Haha! Tell them the truth, Bud! 
The fact is that you really wanted to brag. 
But you were so worn out and tired each day, that you 
thought you would seem uncool. 
{A0}{E1}{04}{00}<(Queen)Tia> 
<Bud> Gaaah! 
<Sonia> Bud... 
Now that is uncool... 
<Bud> What!? 
B-But... 
<Geo> Ahaha! 
4{13}{EC}... 
{15}{E1}...Ahem! 
<Geo> {13}{EC}! 
<Geo-2> E-Excuse us... 
<Dr.Goodall> Hehehe. Don't worry, Geo. 
It's very nice for all of us to hear such joyful voices after so much tragedy. 
...Right, Chief? 
4It sure is... 
By the way, Ace... 
How is getting the last member of the Commandos to join going? 
You have your work cut out for you with that one. 
<Geo-2> {13}{EC}! 
{13}{EC}(The last member...!?) 
{13}{EC}(So there's someone else {13}{EC} who still hasn't joined...) 
<Ace> Well... we did get in contact with him recently. 
But he hasn't given us an answer, yet. 
4...I see. 
Moving on then... 
Geo. 
<Geo> Y-Yes, sir! 
4Sonia. 
<Sonia> Sir! 
4Bud. 
<Bud> Yo! 
...I mean,{15}{E1} Sir! 
4I know that Ace has already spoken to you of this, but... 
I too, would like to request your assistance, on behalf of all of WAZA. 
There is no doubt that without your help, WAZA would have been destroyed. 
Yet, we suffered substantial losses. 
And we are now incapable of performing a number of our standard functions. 
We have managed to maintain enough forces to fight, but 
if another event such as the recent attack from Dealer were to occur... 
Thus, we have no other choice but to rely on you 
three and your ability to EM Wave Change! 
That is why we have asked you to join the Satella Police 
Commandos, as special members. 
It is vital that we can rely on you, so that we can stay in the fight. 
<Geo> You can count on me! 
I'm willing to do anything I can to help! 
<Geo-2> For people like Prez... 
And for Ms. Tia and Jack! 
If Dealer is left to do as it pleases, then countless more people will suffer... 
<Ace> ... 
<Geo-2> Dealer must be stopped! 
And if I can be a part of that, then I'm ready to fight! 
4There is no guarantee for your safety in this fight... 
Your very lives...{15}{E1} could be in jeopardy. 
<Sonia> We are prepared for that! 
...And,{15}{E1} I'm not just saying this lightly. I've thought long and hard about this... 
I want to fight! 
For all the people that listen to my music... 
For this world that has given me the chance to sing 
my songs and have such a wonderful life! 
<Bud> I'm gonna fight, too! 
Sonia's songs have given me hope! 
...And I want to keep on trying great new foods! 
4{13}{EC}... 
Omega-Xis, {15}{E1}Lyra,{15}{E1} Taurus. 
<Mega> Huh? What is it!? 
<Lyra> *sigh* 
Omega-Xis... You could at least try to be a little more respectful... 
{A0}{E1}{04}{00}<(Queen)Tia> 
<Taurus> Mmmrrrggg! 
<Mega> ...I'm better than Mr. Brahma Bull over here... 
4I want to confirm with you three, as well. 
Are you sure you want to be a part of this? 
<Mega> You're asking us this now!? 
I'm not just doing this for you guys. I can't stand those Dealer jerks! 
I'd take 'em out with or without WAZA's help!! 
<Lyra> Yeah... 
I'm not the type to do something that I don't want to do... 
So if I say that I'm in, then I'm in. 
Plus, I'm always there for Sonia! 
{A0}{E1}{04}{00}<(Queen)Tia> 
<Taurus> Mmmrrrggg! 
Let's cut the chit-chat, and get to the fighting! 
Mmmrrrggg! 
4I-I see... 
Understood! 
Thank you, all. 
WAZA is much better off having you as a part of it. 
Let's stop Dealer in order to bring back peace to this great planet! 
<Geo> Yeah!! 
4...Ace. 
I'm counting on you as the leader of such an important Team. 
<Ace> Yes, sir. 
<Ace> Everyone... 
From now on, we are officially a Team. 
Our name... "SP Commandos". 
Our Purpose... 
{A0}{E1}{04}{00}<(Queen)Tia> 
<Ace> To "Crush Dealer"! 
<Geo> Cr{15}{E1}-Crush... 
That sounds kind of... I don't know... 
<Sonia> Y-Yeah... It doesn't have much of a ring to it... Does it? 
<Geo> Can't we change it to like something about protecting the Earth? Or... 
<Ace> It's the same thing. 
<Mega> I like it! Short and to the point! 
<Ace> Right! 
See, Acid? Everyone likes it! 
<Acid> Everyone{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
...Umm, the only people who like the Team name are you and Omega-Xis. 
<Geo> {13}{EC}(It looks like Acid doesn't {13}{EC} like the name, either...) 
<Ace> ... 
...It's no good? 
<Acid> ... 
<Ace> *sigh* Fine,{15}{E1} let's go with something else then! 
How about we use... "Foil Dealer Plan"? 
Anyone have a problem with that? 
<Bud> Wow! That sounds really cool! 
<Geo> That has a much more mature ring to it! 
<Mega> Really? "Crush" sounds way cooler to me... 
<Ace> Agreed! 
See, Acid? I was right. 
<Acid> {15}{E1}*sigh* Anyway, our Purpose has been decided. 
Ace, shall we all form Brother Bands now? 
<Ace> Hum... 
...Sure. 
Let's all be Brothers, guys! 
<Geo-2> F{15}{E1}-Form a Brother Band with Ace...!? 
{A0}{E1}{03}{00}<(Queen)Tia> 
<Geo-2> M{15}{E1}-M{15}{E1}-My pleasure...!! 
<Mega> Why the heck are you so nervous all of a sudden? 
<Bud> This is awesome! Thanks, Ace! 
<Sonia> Yeah, thanks Ace! And you, too, Acid! 
<Game> Geo and Ace formed a Brother Band! 
Geo's Link Power went up by 100! 
<Game> Geo's Team and Purpose have changed! 
<Ace> ...OK, then. For the time being, everyone will remain on active standby. 
Dealer's members could enact their next plans at any time. 
We will respond to them when that happens. 
At the moment, that is our most effective option. 
I know...{15}{E1} It's irritating just waiting around, but... 
<Dr.Goodall> There's nothing else we can do based on the current situation. 
We have to be very careful... 
...And we also need to take care of one other thing. 
Dealer is not our only worry. 
<Geo-2> What...!? 
W{15}{E1}-What do you mean...!? 
<Dr.Goodall> ...Don't you think it is rude to keep secrets from them, Ace? 
<Ace> Hmm, it's really not a big deal for them to not know about it... 
<Dr.Goodall> Haha! They'll find out some way or another! 
Children know there's a problem when adults get agitated and flustered. 
<Bud> W-What is it, Ace!? Don't hold back! 
<Sonia> Yeah, Ace! 
We need to know everything we can, in order to perform our duties the best we can. 
<Ace> I guess there's no avoiding telling you now. 
Well... The world could be destroyed. 
{15}{E1}...There, I said it. See? Not a big deal. 
<Geo-2> T-The whole world...? 
{A0}{E1}{04}{00}<(Queen)Tia> 
<Bud> D-D-D-Destroyed!? 
<Dr.Goodall> Oh, Ace. Don't be so grandiose. 
That is the worst case scenario. 
Recently, we have come upon some new data about Meteor G. 
...In fact, it was Aaron that acquired the data. I'm so proud of that child. 
<Geo> You mean Mr. Boreal? 
<Dr.Goodall> That's right, Geo. 
Aaron is here at WAZA, helping us research not only 
Noise, but also Crimson and Meteor G. 
And faster than Bud couild eat an apple pie, he stumbled upon a great discovery. 
He has discovered that Meteor G is actually a giant Noise cluster! 
<Geo-2> !! 
An asteroid... 
That's completely made of Noise!? 
<Dr.Goodall> That's what the data is telling us. 
It's an absolutely gigantic collection of Noise bound together. 
It is possible that EM Waves that travel to space are all gathering at the same spot... 
Thus, creating Noise, and ultimately Meteor G. 
On top of that, it is being pulled by the Crimson that has collected on the Earth. 
<Geo> Meteor G is being pulled!? 
N-No way...{15}{E1} If the Earth was destroyed... 
<Bud> What do you mean by "if"!? 
<Geo> Well, um... 
What if Meteor G were to hit the planet...!? 
<Sonia> !? 
<Dr.Goodall> Exactly.{15}{E1} That is the worst case scenario. 
The impact of Meteor G hitting the Earth would cause it to break up... 
And the highly concentrated Noise would spread, knocking 
out every piece of EM technology. 
Therefore, our society that we have built upon EM technology would collapse... 
We have relied on EM technology for so long, that I fear that humans would 
lack hope for the future and turn on each other out of confusion and anger. 
<Ace> See? I told you. 
You were better off not knowing! 
Well... 
Like Doc said, the planet being destroyed is the worst case scenario. 
But WAZA is sure to come up with something. 
That's what WAZA is for! 
So we need to do all that we can to help. 
<Geo-2> Y-Yeah... 
<Ace> I think we should end our meeting today, right here... 
0A{15}{E1}-Ace.. 
<Ace> ! 
0Excuse me... 
I ran into some trouble while scouting "him"... 
...! 
1...Take it easy! 
0I-I'm fine. 
Hahaha...{15}{E1} He sure got me good... 
He said he would have no business with weaklings... 
0...But we can't give up! 
We've got to win him over to our side... 
<Ace> ...You did your best. 
<Geo-2> Umm, Ace... 
Who is the last member that you mentioned, anyway? 
1There is an incident occurring in <Echo.Ridge>! 
Viruses have appeared. The point of infection is... 
{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1}What? 
Th-This can't be...{15}{E1} The Real World...!? 
<Dr.Goodall> Oh boy...! 
<Geo-2> How can a virus appear in the Real World...!? 
<Bud> They said <Echo.Ridge>, right? 
We've got to do something!! 
<Ace> OK, everybody. 
<Ace> It looks like we have our first mission. 
We are to get to <Echo.Ridge> ASAP, and then destroy the viruses! 
<Geo-2> Yes, sir! 
<Sonia> Roger! 
<Bud> OK! 
<Dr.Goodall> ...Something very strange must be happening, in order 
for viruses to appear in the Real World. 
Take care of yourselves! 
