<Prez> Satella Police Commandos...!? 
What the heck is that...!? 
<Bud> I-It's... 
Well, we were selected by Ace to fight along with the Satella Police... 
<Zack> Fight against{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} Dealer!? 
I can understand Geo and Sonia, but you too, Bud!? 
<Bud> I told you this before, Zack! 
I'm not the same Bud that I used to be! 
<Geo-2> Ahem... Um... 
Sorry, Prez! 
We didn't mean to skip your speech practice... 
We know that tomorrow is a very big day for you... 
<Prez> Idiots...! 
<Prez> I mean, come on... 
You think that I don't understand that your work is more important!? 
<Zack> Well... 
I suppose there really is no comparing a student body election to saving the world. 
<Prez> E-Exactly...! 
<Bud> Umm... 
I'm sorry that I didn't tell you two earlier. 
I...{16}{E1} Well...{16}{E1} I... 
{A0}{E1}{03}{00}<(Queen)Tia> 
<Prez> Just shut it, Bud! 
<Bud> !? 
I-I'm sorry, Prez! Forgive me!! 
<Prez> Don't. You. Get. It!? 
You don't have to apologize! 
<Bud> Huh...!? 
{12}{E2}<Jack> {01}{00} 
<Prez> I'm not mad at all...! 
Bud... 
You decided to work with the Satella Police all by yourself, right? 
<Bud> Y-Yeah... 
<Prez> Then be the best Satella Police Commando that you can be! 
Be the best Team member that you can be! 
<Bud> P-Prez... 
<Prez> And I mean that also as a member of "Luna 4 Prez". 
I expect you to be a heavily contributing member of both teams! 
There will be no slacking on your part! No excuses! 
<Bud> Prez...! You... You can count on me! 
{A0}{E1}{04}{00}<(Queen)Tia> 
<Bud> Boosh!{16}{E1} "Luna 4 Prez" forever!! 
<Geo> Haha! Good ol' Bud! 
<Prez> What about you, Geo!? 
<Geo-2> Of course!{15}{E1} You can count on me! 
<Prez> Good! 
But... Sonia, can I count on you to look after these two? 
They're always getting in over their heads! 
<Sonia> Hehe! They won't even blink without me knowing! 
<Game> *beep, beep* 
<Geo-2> It's from the Satella Police! 
1This communication is going out to all Commandos who are currently on active duty. 
We have confirmed that a number of viruses have appeared at <Studi.WBG>! 
Please head there immediately! 
We have commandeered the Wave Liner that runs from <Alohaha> to <Studi.WBG>! 
Unfortunately, that is the only Wave Liner we currently have access to... 
Noise has rendered all the others useless. 
Please get to <Alohaha> via the Astro Wave, and take the Wave Liner from there! 
And be careful...! 
Over and out! 
<Sonia> They're attacking <Studi.WBG> now!? 
<Bud> Let's head out, Commandos! 
<Geo> ...We'll be back, guys! 
<Zack> Come back safe! 
I'll make sure Luna's speech practice goes smoothly...! 
<Prez> You better come back in one piece! 
Do anything stupid and you'll have to deal with me! 
<Geo> Got it! 
<Geo-2> Alright! Our first stop is the Astro Wave! 
