<Zack> ...Oh!! 
G{15}{E1}-Geeeo! 
Over here! Over here!! 
<Megaman> Phew... 
<Mega> Is that it!? Come on! 
That Prez girl totally made a mountain out of a mole hill! 
<Prez> Mega Man, watch out! 
Viruses are coming out of there, one after another... 
<Megaman> !! 
<Megaman> N-No way! 
How are viruses popping out like this...!? 
<Mega> Hey, kid! I think there's something over there! 
<Megaman> !! 
...I-Is that where the viruses are... 
<Mega> Possibly! We'll have to ask Ace or someone, later! 
But right now, it's time to whoop some butt! 
<Megaman> Yeah! 
<Ace> ... 
...What do you think, Acid? 
<Acid> ... 
<Acid> There's no doubt. 
It's a portal to a "Noise Wave". 
And it appears to be quite large, too! 
<Megaman> Noise Wave... 
{12}{E2}<(Queen)Tia> {01}{00} 
<Acid> A Noise Wave is a world that is completely made up of Noise. 
It can be seen as a dangerous Cyber Core where 
Noise thrashes around, like the winds of a storm. 
While they are not officially acknowledged, they have been showing up all over the 
world, more and more as the Noise Level around the world has risen. 
<Ace> You guys may have stumbled upon one of them. 
You didn't know, but a Noise Wave detection function was 
installed into your <Hunter>-VG when it was upgraded. 
It was developed based on the fact that Noise Waves 
were predicted to become more common. 
There's still a lot we don't know about them, but what do you think, Geo? 
Do you think it would be worth it to go in and take a look? 
<Acid> ! 
It's too dangerous, Ace. 
We have no idea what is in or what could occur in a Noise Wave of that size. 
Before anything else, WAZA should perform an investi- 
{13}{E2}{02}{00} 
<Mega> Booooooring!! 
You think we're scared of a little Noise!? 
We'll walk right in there and have a look, no problem! We can do anything! 
<Acid> I can't allow that, Omega-Xis. 
I must follow protocols... 
<Mega> I don't remember asking you! Come on, kid!! 
<Megaman> Wh-What!? 
<Ace> I appreciate it, Geo. 
As Omega-Xis has alluded to, no one other than Mega Man 
could possibly be able to move around freely in there. 
If I sent anyone else, there would be very little hope for their return. 
<Acid> ... 
<Ace> But Geo, I know you can handle it. 
You're the world's greatest hero, after all! 
<Megaman> ...Thanks! 
I'll check it out then, Ace! 
{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1}It's OK, right, Acid? 
<Acid> ... 
I expect you to come back with some interesting data. 
...Be careful. 
<Megaman> Always! We'll be back! 
<Mega> Bah! 
