<Megaman> Wh{15}{E1}-What's this...!? 
I didn't know that Noise could get this big! 
<Mega> I-It's definitely not normal...! 
<Game> ...Pfft! 
Don't tell me you're freaking out over something so small... 
<Megaman> !? 
<Megaman> J-Jack...!? 
Is this Noise all your doing!? 
<Jack.Corvus> ...What would you do if I did do it? 
You know{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} I just don't get it...!! 
How could such imbeciles beat Sis!? 
<Megaman> Jack... About Ms. Tia... 
<Jack.Corvus> Shut up... 
<Megaman> Just listen, Jack...! 
{A0}{E1}{04}{00}<(Queen)Tia> 
<Jack.Corvus> I said shut up!! Don't talk to me like you know me!! 
<Jack.Corvus> Man... You two really bug me...!! 
You think I should listen to you!? 
You think I'm an idiot!? 
<Megaman> Not at all...!{15}{E1} I was just... 
<Mega> Just quit it, kid! 
If you want to talk to him, do after we kick his butt! 
<Wolf.Woods> Ha! You sure can talk, can't you, Omega-Xis!? 
Wait, you don't think... 
That you actually gave me some competition in the last battle, do you? 
If so, you must be losing your mind at your old age! 
<Mega> Grrr! 
Shut that flapping beak of yours, and get ready for some pain! 
We'll see who's the old man! 
<Wolf.Woods> {13}{EC}... 
Don't get too carried away, Omega-Xis... 
Jack...{15}{E1} Let's rid the planet of this chump stain...! 
<Jack.Corvus> Shut up!! 
Don't you dare give me orders...!! 
<Megaman> Please, Jack! 
I don't want to fight you...!! 
<Jack.Corvus> {13}{EC}... 
I see...{15}{E1} Well, whatever you say. 
But I came here for a fight, so I'm having one...!! 
<Game> ...So I finally found one of those Dealer scum. 
<Megaman> !? 
<Jack.Corvus> Who's that...!? 
<Jack.Corvus> ...Argh!! Who are you...!? 
<Rogue> My name is Rogue{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} Try not to forget it. 
<Jack.Corvus> Rogue...!? 
The last survivor of Mu? That Rogue...!? 
{13}{EC}(...King mentioned {13}{EC} that he's really dangerous... {13}{EC} So that's him, huh...!?) 
...What do you want? Why are you here!? 
Is there something you want from me!? 
<Rogue> ... 
<Rogue> Not from you... 
I have a question for your Boss. 
<Jack.Corvus> !? 
<Rogue> ...Take me to your leader. 
<Jack.Corvus> Ha...! 
Just who do you think you are!? 
...If you want to see King, then find him yourself! No chance I'm helping you! 
<Jack.Corvus> Man, he really spoiled the mood! 
Next time, Mega Man! 
<Megaman> Jack... 
<Rogue> Hmph... He ran away. 
<Megaman> ! 
<Megaman> W-Wait, Rogue! 
<Rogue> {13}{EC}... 
<Megaman> Umm{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} Th-Thanks... 
<Rogue> {14}{E1}.{14}{E1}.{14}{E1}.{14}{E1}You're as naive as always. 
Do you honestly think that I was helping you out? 
<Megaman> Huh...? 
W-Well, then... 
<Rogue> Hmph... 
You know what, I don't even care what you think. 
You're still on my hit list. 
Nothing has changed. 
<Megaman> {13}{EC}... 
<Rogue> ...However... 
There are others who are of more concern to me at the moment... 
Dealer... I'm taking them down. 
<Megaman> !? 
You're fighting Dealer, too!? 
<Rogue> I'll only say this once. I have no intention of working with you. 
...At the most, you will only be a tool of mine to use. 
Get that message to the Satella Police, too! 
<Megaman> Rogue... I mean <Solo-color>. 
What did Dealer do to make you so angry? 
And why did you leave a message for the Satella Police? 
Do you have a history...? 
<Mega> Hey, kid! Take a look! 
<Megaman> Huh...? 
<Megaman> I-It's gone... 
<Mega> It's finally clear! 
That Jack guy must be behind that weird Noise! 
He made that stuff show up in order to cause a ruckus. 
Which he knew would draw us out! 
<Megaman> Hmm... 
Things certainly are getting more complicated... 
For the time being, let's go see the Satella Police...! 
...It would be great if the Wave Liner was running. 
Getting through that Noise Wave was really rough... 
<Mega> We took care of all that weird Noise he set up, plus 
there aren't anymore viruses running around, so... 
It should be working, right? 
<Megaman> Good point! Let's go check! 
