<Ace> I see. 
So Jack will be coming next... 
<Ace> Jack... 
His emotions often get the best of him, and he just loses control. 
He can be very brutal when in the wrong state of mind. 
...And only his older sister, Queen Tia, can calm him down. 
Yet, at the moment...{15}{E1} His beloved older sister is a little pre-occupied. 
<Geo-2> {13}{EC}... 
<Ace> In short, the kid's a ticking time bomb. 
We've got to catch him the next time he shows up to fight Geo. 
<Bud> I can't believe that he's so dangerous... 
He was really fun to hang out with at the beach. 
Isn't there anything we can do, Geo? 
<Geo-2> I-I hope so... 
{13}{EC}(I really want to {13}{EC} help him, too, Bud...) 
{13}{EC}(But he's not the same {13}{EC} Jack we knew before...) 
{13}{EC}{08}{FF}I'm{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} {13}{EC} I'm responsible for {13}{EC} his sister's capture...) 
<Ace> {13}{EC}... 
Oh, by the way, Geo. 
<Geo-2> Y-Yes...!? 
<Ace> Rogue... 
Solo called Dealer his enemy, right? 
<Geo-2> Yeah, pretty much...{15}{E1} 
He said there are others that are of more concern to him... 
And that he has no intention of working with me or with the Satella Police. 
<Ace> {13}{EC}... 
{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1}Darn. It looks like that idea is out. 
It had so much potential... 
<Geo-2> Umm... 
What does Solo have to do with the Satella Police? 
<Ace> Ah, didn't I tell you? 
Solo was going to be the final special member of the Commandos. 
<Geo-2> Oh{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
{A0}{E1}{03}{00}<(Queen)Tia> 
<Sonia> Really!? 
<Ace> But he turned us down. 
Remember that officer that came back all beaten up? 
He was trying to recruit Solo, but ended up getting attacked by him. 
<Geo-2> So that's what happened... 
<Ace> At the very least, I'm glad to see that he doesn't see the Satella Police as enemies. 
...OK, everyone. 
Great work today. 
You all did well handling Jack and the Noise Wave incident. 
Leave the follow-up work to WAZA, for now! 
You may all go now. 
