<Geo-2> !! 
<Sonia> G{15}{E1}-Geo...! 
<Bud> I-Is that...!? 
<Geo-2> S{15}{E1}-Solo!? 
<Solo> {13}{EC}... 
<Geo> Have you changed your mind about working with the Satella Police...!? 
<Solo> ...Didn't you hear me the first time I said it? 
I have no intention of working with them or you. 
<Geo-2> I see... 
<Bud> S-So... Why are you here then? 
Are you trying to pick a fight!? 
<Solo> {13}{EC}... 
0Solo...! 
0Please, we need to work together! 
Let's fight together in order to protect the world from Dealer!! 
<Solo> {13}{EC}... 
You fools... Do you ever learn? 
And just how long are you going to follow me around? 
0Until you agree to join us... 
The Satella Police need to improve their fighting capabilities... 
Please! Join the Commandos...!! 
<Solo> {13}{EC}... 
...Hmph. Fine... 
0!! 
<Solo> However... 
Only if you can capture me... Right here, right now. 
0...If that's what it will take!! 
0I apologize... But you've given us no other choice! 
All Wizards! Attack! 
<Solo> Hmph...! 
{A8}{00}...Condition red. Damage exceeding acceptable limit. 
Aborting mission. 
<Geo-2> Is that... Really a Wizard!? 
<Mega> ... 
It's definitely not a normal Wizard, I'll tell you that. 
He's different from either me, Taurus, Acid, or Strong...! 
On top of that{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} He's really strong! 
0Argh... We're not done yet! 
<Solo> Hmph... 
If you're not going to come to me, then I'll have to come to you...! 
<Solo> Come, Laplace...! 
0!? 
<Solo> ...Ha!! 
0H-How...!? 
How is it possible to take out so many Wizards in just one attack...!? 
<Solo> ...Game over. 
<Solo> I want nothing to do with such weak cockroaches. 
If you continue to follow me, it'll be game over for you too... permanently. 
0...! 
<Geo-2> H-He did all that without even EM Wave Changing...!? 
<Bud> W-Wow... He's way too strong...!! 
<Solo> {13}{EC}... 
Listen up, Mega Man. 
I'm going to pull my own trump card on Dealer. 
Don't you dare get in my way... Or you'll be next. 
<Geo-2> {13}{EC}... 
Solo... 
Why are you out to get Dealer? 
<Solo> Tawdry fools like Dealer have no right to use the power of Mu. 
<Geo-2> What!? Dealer is using Mu technology!? 
<Solo> ...The whole organization will be destroyed. 
You don't have the right to fight them over this issue. 
It is mine, and mine alone. 
So don't get in my way! 
<Geo-2> Solo... 
