<Jack.Flask> ...Umm. 
And therefore, if I am elected as student body president, I promise to ban 
all Valentine's Day activities on school premises! 
Thank you everyone for your support! 
{A0}{E1}{03}{00}<{16}{EC}{10}{E2}{39}{04} 
<Game> *cheers* 
{16}{EC}{10}{E2}{39}{04} 
<Game> Yaaaay! 
<Harry.Sasoon> ...It is now time for the final candidate. 
Please welcome Luna Platz from the 5th Grade Class A! 
<Prez> H-Hello! 
{13}{EC}(Where is everybody!?) 
{13}{EC}(It's my turn!!) 
<Prez> My name is Luna Platz, and I am the candidate from the 5th Grade Class A. 
{A0}{E1}{03}{00}<{16}{EC}{10}{E2}{39}{04} 
<Game> *cheers* 
{16}{EC}{10}{E2}{39}{04} 
<Game> Woohoo! 
<Woody> Yey, Prez! 
<Angel.Wise> We're here for you, Luna! 
<Prez> Thank you very much for your support, everyone! 
I am so happy to have this opportunity to speak to you today. 
{13}{EC}(Argh... {13}{EC} It's already started, {13}{EC} but they're not here!) 
{13}{EC}(Where is everyone!?) 
{13}{EC}(Bud, Zack, Geo...!) 
<Game> ...Bah! 
<Prez> !! 
<Harry.Sasoon> What's that!? 
.Wh-Wh-Wh-Who are you!? 
<Game> *murmur* 
<Wolf.Woods> ...It doesn't look like he's here. 
What should we do, Jack? 
<Jack.Corvus> If he's not here, then we'll just have to call him... 
If we wreck this place and cause a panic, he'll come racing to their rescue. 
<Wolf.Woods> Ohoho! That sounds great! 
Let's get to it! 
<Jack.Flask> H-Hey, what... 
<Harry.Sasoon> Umm... This can't be good! 
<Game> *chatter* 
<Mr.Shepar> N-No way...! 
<Mr.Shepar> Everyone! It's dangerous over there! 
Get over here, quickly! 
<Harry.Sasoon> O-OK...! 
<Mary.McLovin> Ahhh! 
<Jack.Flask> Help! 
{AF}{00}Oh, this is getting good... 
{AF}{00}Well, if it isn't my fellow FM-ian, Corvus...! 
He was so fierce that no other Wizard could even lay a hand on him in battle! 
<Damian> I see. 
He's not exactly being a good visitor to Earth at the moment! 
If we don't do something to stop him soon, we could have a real problem on our hands! 
{AF}{00}Are you saying you want to fight him, Damian? 
{15}{E1}...We can't beat him. 
<Damian> We just need to buy some time for now! 
Don't forget, a certain kid goes to this school! 
{AF}{00}Hmm... You've changed, haven't you? 
Oh well. I guess we have no choice! 
<Damian> Yeah! 
EM Wave Change! Transcode 011{15}{E1} Wolf Woods! 
<Wolf.Woods> Ohohohohoho! Run away! Run away! 
You never know, someone might come and save you! 
<Prez> Stop this, this instant!! 
<Jack.Corvus> ...! 
<Wolf.Woods> Who the!? 
<Mr.Shepar> Luna! Get away from there!! It's too dangerous! 
<Prez> {13}{EC}... 
<Jack.Corvus> You...! 
Y-You're alive...!? 
B-But that can't be...! 
... 
<Wolf.Woods> Jaaack!! 
<Jack.Corvus> ...!! 
<Wolf.Woods> This is no time for talking! 
Unless you don't mind if Queen Tia... 
<Jack.Corvus> S-Shut up!! 
Hey, girl! What do you think you're doing!? 
<Prez> What do I think I'm doing!? 
I should be asking you that question, don't you think!? 
<Jack.Corvus> {13}{EC}...!! 
<Prez> So... What are you doing here!? 
<Wolf.Woods> Ohohoho! 
Can't you tell? I'm going to turn this whole place into rubble! 
And I'm going to take out you and your little friends! 
<Prez> Shut up!! 
Jack, I'm asking you a question here! 
<Prez> Please, Jack. Answer me...! 
You're not capable of hurting all of these people, are you? 
You wouldn't do something like that, right!? 
<Jack.Corvus> ...Could you be any more annoying...!? 
You want me to answer that question...? 
Fine. 
I'll answer with destruction! 
Everything{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} I'll destroy everything! 
<Prez> W-Why...!? Jack, why!? 
<Jack.Corvus> It doesn't matter... 
I just want to wreck stuff! 
<Prez> Ahhh! 
{13}{EC}(H-He isn't going to stop...! {13}{EC} I can't stop him all alone...!!) 
Mega Man... 
Please hurry...! 
<Game> Grrrrrr...! My blood is boiling! 
<Prez> Who!? 
<Jack.Corvus> !? 
{8C}{00}You said your name is Corvus, right!? 
Well, why don't you try yelling at me, instead of a little girl! 
I'm rip roarin' and ready to go!! 
{AF}{00}...Maybe you haven't really changed, after all... 
{8C}{00}Hey, Geo! Can you hear me over the school intercom!? 
Hurry and get to the roof!! 
We've got someone who wants to see you up here!! 
