<Bud> Darn it. It's no good...! 
<Bud> It just won't open! What's going on!? 
<Geo-2> This one too...! 
What the... 
<Mega> ...Maybe it's the Noise? 
The Noise did get more dense, recently... 
This whole place is probably chock full of Noise! 
<Geo-2> Noise... This must be Jack's doing...! 
We really have to get to the roof quick...! 
<Mega> I don't see the problem! 
Let's just smash down this stupid door! 
<Geo-2> Really!? Isn't that a little too... 
W-Well... I guess we have no choice... 
<Solo> {13}{EC}... 
...Hey you. 
<Zack> Ahh!? 
<Zack> M-M-M{15}{E1}-Me!? 
Y-Y-Y{15}{E1}-Yes!? 
<Solo> ...Where's the Wave Station? 
<Zack> Th-Th-Th{15}{E1}-The Wave Station...!? 
Th-Th-Th{15}{E1}-The first floor! It's on the first floor!! 
<Solo> ...Down, huh? 
<Solo> Laplace...! 
<Zack> Ah{15}{E1}hhhhh! 
<Solo> {13}{EC}... 
<Sonia> Whoa... 
That's a big hole... 
<Bud> G-Geez...! 
<Geo-2> S-Solo...!? 
<Solo> {13}{EC}... 
...Hmph. 
<Geo-2> Argh... What should we do...? 
<Sonia> Hmm... We don't have much choice. 
<Bud> Yeah... 
<Geo-2> I guess... 
We'll just have to use this hole to get to the roof. 
...EM Wave Change! 
<Megaman> OK, let's go! 
<HarpNote> Yeah! 
<Taurus.Fire> Boosh! 
<Megaman> Wait here, Zack! 
We'll come check on you later! 
<Zack> O-OK... 
I think that Solo is headed for the Wave Station on the first floor. 
He asked me about it just a minute ago. 
<Megaman> The Wave Station... So he's going to the roof via the Wave Road! 
<Mega> The elevator probably isn't working because of the Noise, too. 
<Megaman> Yeah. OK, let's follow Solo! 
<Taurus.Fire> Wow! 
So this room is... 
<Megaman> The faculty room... 
<HarpNote> ...Geo. It looks like Solo left from over there... 
<Megaman> ...Y-Yeah... 
That's a nice hole he put in that wall... 
<Taurus.Fire> L-Let's go. 
<Megaman> Right. 
