<Megaman> ...Thanks for waiting, Mr. Wolf! 
{8C}{00}Grrrrrr...! H-He's pretty strong! 
I've completely reached my limit...! 
...Don't even flinch, kid! 
<Megaman> Got it! 
<Mega> Hey, Wolf. Happy to see me? 
{AF}{00}Late as always! 
I'll hand this guy over to you, Omega-Xis! 
<Mega> Thanks! 
And in exchange I'll kick this guy's sorry butt... Free of charge! 
<Wolf.Woods> You think you can actually do that? 
<Wolf.Woods> Come on, Little Mega... 
Do you really think anything you say is going to have an effect on me? 
<Mega> Now that you mention it... You always were kinda thick. 
<Wolf.Woods> Why you... You're going to regret that... 
<Mega> *yawn* Yeah, uhh huh. 
Can we just get to the fighting, already!? Bring it on! 
{A0}{E1}{04}{00}<(Queen)Tia> 
<Wolf.Woods> Argh! I can't wait any longer!! 
Jaaack!! 
<Jack.Corvus> Quit your crying, Corvus! 
I'm sick of hearing you go on and on, too... 
In due time, there won't be enough of them left for a successful data recovery. 
With these hands... I will show them true pain... 
And rid them from the world... 
<Megaman> Jack... 
You've got to stop and think about this!! 
You're our classmate... And our friend, right!? 
We went on our class trip together, and made a lot of great memories. 
Or was that all an act!? 
<Jack.Corvus> You're the one that needs to wake up, Mega Man. 
"Friend"...? 
Give me a break! 
I was just pretending to be friends with you guys. 
You're pathetic{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
You put that much hope into a person who was just lying to you the whole time? 
<Megaman> ...That stuff doesn't matter! 
<Jack.Corvus> ...What? 
<Megaman> Jack... It doesn't matter why you hung out with us. 
But during the trip we spent some time together and had a lot of fun! 
As long as we share those memories, you will always be our friend!! 
<Taurus.Fire> Listen to him, Jack! 
<Taurus.Fire> I also had a super fun time hanging out with you on the class trip! 
I don't care what you say, the guy who we hung out with is our friend!! 
<Jack.Corvus> {13}{EC}... 
{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1}Shut up... 
Just shut up!! 
{A0}{E1}{04}{00}<(Queen)Tia> 
<Jack.Corvus> Shut up! Shut up! Shut up! Shut up! 
You guys are such a pain in the butt! Just! Shut! Up! 
<Jack.Corvus> I'll just delete them... 
I'll just delete all of those worthless memories... 
And you along with them!! 
<Megaman> J-Jack... 
<Mega> Hey, kid! 
<Megaman> Yeah, I know... 
I know, Mega. 
Bud. Sonia. 
I'm sorry, but{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} I have to battle Jack all by myself... 
Please trust me on this one. 
<Taurus.Fire> {13}{EC}... 
...Understood, Geo! 
<HarpNote> We believe in you, Geo! 
<Megaman> Thanks, guys! 
...Jack!! 
You are our friend! 
And that's why... Why I have to stop you!! 
Wave Battle! 
<Megaman> Ride{15}{E1} On!!{30}{EC}
