<Jack.Corvus> A-Arrrgh!! 
<Wolf.Woods> Owaaaa!! 
<Jack.Corvus> M... 
Man... 
<Jack.Corvus> O-Our... Wish... Hasn't come{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} true, yet{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
{13}{EC}... 
<Megaman> Jack... 
<Mega> Ha! How'd you like that, Corvus!? 
So who's stronger after all!? 
{13}{EC}(Phew... It was really {13}{EC} close there for a minute!) 
<HarpNote> Way to go, Geo! 
<Taurus.Fire> That was an awesome battle! 
<HarpNote> I told Ace what happened! 
He's on his way! 
<Taurus.Fire> Hey... What about Jack...? 
<Megaman> He's OK. He just lost consciousness... 
<Taurus.Fire> Oh, OK... Thank goodness! 
Mega Man to the rescue, once again! 
<Megaman> Haha. Thanks Bud...! 
{13}{EC}(That... {13}{EC} That took everything I had. {13}{EC} Any more and I...) 
<Joker> ...Mr. King. 
Jack has been defeated by Mega Man. 
What are your orders? 
<Mr.King-2> So he went off on his own and got himself in a pickle, did he? 
Ho ho ho!! His foolishness is infinite! 
He's worse than his sister. He can't even perform the duty of a worthless pawn! 
<Joker> {13}{EC}... 
<Mr.King-2> Anyway... Return as quickly as you can, Joker. 
We must decide on the next step. 
The step that will bring a conclusive victory to us! 
Ho ho ho ho ho! 
<Joker> Yes, sir! 
<Harry.Sasoon> One...{14}{E1} Two..{14}{E1} Testing, testing... 
Ahem! 
Thank you for waiting. 
I will now announce the election results! 
<Harry.Sasoon> The new student body president of Echo Ridge Elementary is... 
<Geo-2> Ahh, my nerves are going out of control... 
<Mega> Why the heck are you nervous? 
<Bud> *gulp* 
<Zack> Prez. Prez. Prez... 
<Harry.Sasoon> Luna Platz from the 5th Grade Class A!! 
<Prez> ...!! 
<Geo> Alriiight! 
Woo hoo!! 
<Bud> Yeeeah! You did it, Prez!! 
<Zack> Con-con-con... 
Congratulations, Prez... 
*sob* 
{A0}{E1}{04}{00}<{16}{EC}{10}{E2}{39}{04} 
<Game> *cheers* 
{16}{EC}{10}{E2}{39}{04} 
<Game> *applause* 
<Harry.Sasoon> Will the new student body president please come to the podium! 
<Prez> Of course! 
<Prez> All the students of Echo Ridge Elementary! 
I want to express my deepest gratitude for your hard work and support! 
As promised, I will strive to improve the school in all possible ways, so 
that all of you may enjoy an improved education, as 
well as extra-curricular activities. 
Change has come to Echo Ridge Elementary! 
{16}{EC}{10}{E2}{39}{04} 
<Game> *applause* 
<Prez> However... 
That is not something that I can do all by myself! 
With your help, and with the help of the people standing next to you... 
There is one special thing that I would like to do as 
my first act as student body president. 
I would like to get every teacher and student to form 
Brother Bands with each other, form one huge Team, 
and then aim for a Purpose to "Create a School Where Everyone is Happy". 
I would be honored and ecstatic if we could all make that happen! 
We can do it! 
{12}{E2}<Joker> {00}{00}{A0}{E1}{04}{00}x{16}{EC}{10}{E2}{39}{04} 
<Game> *cheers* 
{16}{EC}{10}{E2}{39}{04} 
<Game> *applause* 
<Jack.Flask> I'm in!! 
<Angel.Wise> Me too!! 
<Geo> You're something else, Prez!! 
<Mega> She wants to form one big Team with everyone from the school, huh? 
Is that even possible!? 
<Geo> I didn't even think of that... It could be kind of difficult. 
But... That makes it all the more worthwhile to try! 
<Mega> Good point... 
<Geo> That's what I thought! 
<Bud> {13}{EC}... 
Hey, Geo... 
I need to talk to you later, if that's OK? 
<Geo-2> Sure, but why are you so tense!? 
<Bud> You'll see. 
I'm going to ask Ace and Sonia to join us, too. 
<Geo-2> Umm... Alright... 
<Geo-2> What!? 
You're going to quit the Commandos!? 
<Sonia> I-I can't believe it! What's going on, Bud!? 
You've put so much into the Team, and now you're... 
<Ace> {13}{EC}... 
<Bud> Geo, Sonia, Ace... 
I'm sorry that I'm being so selfish. 
<Bud> But, I... I've realized who I really want to protect... 
And that's Prez! 
Of course, it sounds really cool to fight for world peace and safety! 
But it just doesn't feel right! 
It's just not me, or rather... 
I guess... I'm just not happy if I'm not around Prez! 
...And Zack, too! 
When all three of us aren't together, then I'm just not the real Bud! 
So... 
I'm quitting the Commandos. 
The Satella Police don't really want a pathetic loser like me on their side, anyway... 
<Geo-2> Bud... 
<Sonia> Bud... 
<Bud> Instead of getting upset, be happy! 
Be happy that I'm going to keep Prez safe! 
She'll never be in danger, ever again! 
<Geo> Good point! 
Take care of her, Bud! 
...And Zack, too! 
<Bud> Don't worry. I will! 
<Sonia> Poor Zack! 
I don't know how he can handle the two of you all the time! 
<Geo> Ahahahaha! 
<Ace> {13}{EC}... 
<Geo> Umm, Ace... 
<Bud> Ace... 
<Ace> {13}{EC}... 
Bud Bison! 
<Bud> Y-Yes!? 
<Ace> I'm going to assign you a special task! 
<Geo-2> !? 
<Bud> O-OK...!? 
<Ace> Protect Luna with your life! 
That is all! 
<Bud> !! 
<Geo> Ace...! 
<Sonia> So... 
{12}{E2}<Joker> {00}{00} 
<Ace> The job of the Satella Police is to protect people. 
Therefore, Bud is a shining example of how a Satella Police officer should act. 
As long as he never stops protecting Luna! 
Yet, keeping someone safe is not an easy task, Bud... 
In some cases, it is even more difficult than defending the whole world... 
Make sure you are ready for this, and do the best that you can! 
<Bud> O-OK! 
...I mean... Yes, sir! 
<Geo> I'm sure you'll do great! 
<Sonia> Teeheehee! Don't let us down! 
<Bud> Thanks for understanding, guys! Woooooo! 
I'm there for you, Prez! 
<Game> Prez became the student body president... 
<Game> Purpose fulfilled!! 
