<Megaman> I can't find the exit for this Noise Wave! 
<Mega> On top of that, I'm sensing something really suspicious... 
<Rogue> ...!! 
<Megaman> W-What's wrong, Rogue? 
<Rogue> Here it comes. 
<Megaman> Huh!? 
<Megaman> Is that a virus!? 
No, it can't be... It's got to be Noise! 
<Mega> That's what it looks like! It's completely made up of Noise! 
It's like a Noise cluster that can move around! 
<Rogue> Hmph... Dealer is into some elaborate stuff, it seems. 
<Megaman> !? 
So that means... 
That both this Noise Wave and that Noise monster are Jack's doing. 
It must be a Dealer weapon! 
<Rogue> Exactly. 
I'm going to delete this thing. {15}{E1}...Give me a hand. 
<Megaman> Huh!? 
<Rogue> That thing is in control of this area. 
If we delete it, we will be able to pulse out, and this Noise Wave will be destroyed. 
It's pretty simple. 
<Mega> How the heck do you know this, anyway!? 
<Rogue> Hmph. 
I ran into one of these things before you caught up with me. 
It was actually pretty tough. 
<Megaman> !? 
<Rogue> So listen up. 
It attacks by firing out Noise. 
If you leave the Noise alone, it will explode and hurt you. 
The explosion causes a considerable shock wave. 
My EM shield didn't really have much of an effect, so... 
<Megaman> ... 
<Rogue> So use your Buster to destroy all the Noise that 
it fires out, before it explodes! 
I will time my attacks to its body with your attacks on the Noise. 
Got it? 
<Megaman> OK, let's do this! 
<Game> Controls +Control Pad: Aiming Cursor B Button: Mega Buster 
<Megaman> I'm ready any time, Rogue! 
<Rogue> Hmph. {16}{E1}Go! 
