<Game> It is the year 22XX. 
Humans have improved their way of living with EM wave technology. 
However, the world has recently fallen into great peril twice. 
The first time... Earth was infiltrated by aliens from Planet FM. 
The second time... The evil scientist Vega tried to take over the 
Earth with the power of  the ancient civilization known as Mu. 
But twice, a hero came forth to confront the evil. 
That hero, or shall we say heroes, are the human boy Geo Stelar and the FM-ian 
Omega-Xis, who together form ...Mega Man! 
Thanks to Mega Man, the people of Earth have been 
able to live safely in peace and happiness. 
<Game> *chatter, chatter* 
<Geo> Ahh, I'm so excited! 
<Mega> (Hey, kid...) 
<Geo> (What's up, Mega?) 
(People will hear you, so  you better keep it down.) 
<Mega> (Don't worry!) 
(Everyone's too  excited to hear me!) 
(What's goin' on anyway?) 
<Geo> (Heh, heh, you'll see soon!) 
<Mega> (...?) 
<Mr.Shepar> Does everyone have their mobile terminal ready? 
<Game> Reeeeady! 
<Mr.Shepar> Kids, today we'll be upgrading our operating system, known as our OS. 
Altering such a vital program is quite a big deal. 
OK, I'm sending the upgrade program to everyone now! Here we go! 
<Mega> {13}{EC}!! 
(W-Wait a second!) 
(Upgrade!? What's going to  happen to me!? I'm inside  the OS!) 
<Geo> (Hmm, I wonder...) 
<Mega> (Hey, kid!!) 
(Grrr! There's a ton of  of data coming in!) 
{06}{E2}{00}{00}{10}{E2}{B4}{03}{16}{EC} 
<Game> *beep, beep* Upgrading.{14}{E1}.{14}{E1}.{14}{E1} 
{10}{E2}{B4}{03}{16}{EC} 
<Game> 20%.{14}{E1}.{14}{E1}.{14}{E1} 
{10}{E2}{B4}{03}{16}{EC} 
<Game> 60%.{14}{E1}.{14}{E1}.{14}{E1} 
{10}{E2}{B4}{03}{16}{EC} 
<Game> 100%.{14}{E1}.{14}{E1}.{14}{E1} 
Upgrade complete! 
{06}{E2}{03}{00}
<Game> Wow!! 
<Geo> A-Awesome! 
This is the new <Terminale.Mobile-color> OS! 
The user interface is totally different than before! 
<Mr.Shepar> It looks like you've all finished upgrading successfully! 
So as you can see, your mobile terminal has changed as well. 
It is now called the  "<Hunter-VG-color>"! 
<Geo> <Hunter>-VG{13}{E1}.{13}{E1}.{13}{E1}.{13}{E1} 
Awesome!! 
<Mr.Shepar> As the development of technology has rapidly progressed, the number of 
<Virus-color>-based problems have also increased. 
The <Hunter>-VG has been designed in order to make <Scontro.Virus-color> easier. 
Battle Cards that are used to delete viruses 
have also been made more manageable. 
<Geo> Ahh, that's why it's called the "Hunter". 
<Mr.Shepar> The <Hunter>-VG will now be an essential item in your day to day life. 
It comes with many new functions, so try them out when you have a chance! 
<Game> Yes sir! 
<Mr.Shepar> OK! 
As I said before, the upgrade has formatted your data. 
So you'll have to re-input  everything. 
First, you need a new Codename. 
A Codename is a nickname that you use when accessing a network. 
You can choose any name that you'd like, but nothing naughty, understood!? 
<Geo> Alright! Time to select a Codename! 
