<Geo> Done! 
<Mr.Shepar> Is everyone finished? 
OK, now I'll explain the pop-up system to everyone. 
Please get into small groups. 
<Mr.Shepar> Is everyone ready? 
OK, I'm going to start the explanation now. 
As I'm sure everyone already knows... 
There is a massive amount of information in the world. 
Actually, there is too much information for people to handle. 
<Bud> I so understand that! 
My room is so messy that I can't find my pants in the morning! 
<Zack> It's because your room looks like it got hit by a tornado, <Bud-color>! 
You really need to clean it up big time! 
<Bud> Watch it, <Zack-color>! It's MY room! 
<Mr.Shepar> Haha, actually Bud gave a good example. 
In short... 
When you need to find something quickly, there is no time to waste. 
And it's very hard to find what you need in a huge pile of data. 
The new pop-up system makes finding things much easier. 
<Geo> A-Awesome! 
<Mary.McLovin> Mr. Shepar! 
When is the pop-up system accessible? 
<Mr.Shepar> Why don't you try talking to the people in your group? 
<Mary.McLovin> OK! Geo, can you try saying something to me, please? 
<Geo> Sure. 
<Geo> What's up? 
<Geo> Whoa! Something popped up on the bottom screen! 
<Mr.Shepar> What just appeared on everyone's <Hunter>-VG is called a pop-up. 
As I said earlier, a pop-up shows you important information. 
This pop-up is showing who you're talking to. 
<Geo> Their school emblem even pops up above. 
<Mr.Shepar> Touching the pop-up will make more information about the person appear. 
Why don't you try touching the pop-up? {0A}{E1}{84}{02}
<Geo> Cool! Even if we just met for the first time, I would 
know she is Mary McLovin from Echo Ridge Elementary. 
<Mr.Shepar> There are also many other pop-up types. 
For example, standing in front of an elevator will make choices appear. 
Touch the desired destination to go there automatically. 
The more you try it, the quicker you will get used to it. 
OK, that's everything for now! If you have questions 
about your <Hunter>-VG or EM waves, please feel free to ask. 
<Mr.Shepar> Oh! Before class ends I have one last thing I have to mention. 
<Mr.Shepar> The upgrade deleted your Brother Bands. 
Don't forget to re-form Brother Bands with your close friends! 
Everyone be safe on the way home! 
<Game> OK! 
<Geo> So my Brother Bands have been deleted... 
I better go re-form them with Bud, Zack and <Prez-color>. 
<Mega> (Hey{13}{E1}.{13}{E1}.{13}{E1}. Kid{13}{E1}.{13}{E1}.{13}{E1}.) 
<Geo> {13}{EC}...? 
(What's up, <Mega-color>?) 
<Mega> (Is it OK if I come out  for a bit?) 
<Geo> (What? No way!) 
(People will notice if you  come out here!) 
(It's different now that  people can see you!) 
<Mega> (Well, then get us to a  place where it won't be  a problem!) 
<Geo> (Hmph! What's the big hurry  all of a sudden, anyway?) 
(I have some questions  that I want to ask  Mr. Shepar...) 
<Mega> (Go ahead, but let's get  outta here ASAP!) 
(If you forget anything,  just press the L Button  and I'll help you out!) 
(I'll make sure you know  what you need to do!  Got it!?) 
<Geo> Yeah, I got it... 
(So where's a place I can  go that Mega won't be  noticed...?) 
(Hmm, how about the roof?) 
