<Geo> Sorry for the wait, Mega. You can come out now. 
<Geo> Wizard On! 
<Mega> Roo{15}{E1}aaa{15}{E1}rrr!!! 
<Geo> W-What's wrong!? 
<Mega> Geo! For cryin' out loud! 
Let me know before you ever do something like upgrade your mobile terminal! 
<Geo> Huh? 
Why? 
<Mega> What do you mean why!? You should know! 
Thanks to the recent advancements in wave technology, I've become a 
Wizard, which is basically an <CORPO.EM-color> that is integrated into the mobile terminal! 
<Geo> Yeah, of course I know that much... 
You and the <Hunter>-VG are intimately linked together. 
<Mega> Grr!!! Exactly!!! 
So if you make a change to the system, then you change me, too! 
Do you think it feels nice to have a ton of data shoved down your gullet? 
It was terrible! Ohh... 
I don't feel so good all of a sudden... 
<Geo> S-Sorry! I didn't think of that... 
<Mega> No big deal, kid. Just keep it in mind for the future. 
By the way... 
Have you tried on your <Visualizer-color> since EM wave technology has advanced? 
<Geo> Huh? Now that you mention it... 
<Mega> Well, try them on, kid. 
<Mega> When you put on your <Visualizer>, you are able to 
see the "<Wave.Road>" and even EM bodies. 
Regular people can't see these phenomena. 
So, can you see anything? 
<Geo-Visualizer> Yeah, it works great! 
If my dad hadn't given me this <Visualizer>, you and I wouldn't have met, Mega. 
<Mega> <Kelvin-color>... Your father was a great man, kid... 
And as they say, "like father, like son." 
<Geo-Visualizer> Hey, don't compare me to my dad, OK? 
I need to make my own path in life. 
<Mega> Heh, you sound like you're growin' up, kid. 
Anyway... You should try using the <Visualizer> everywhere. 
Just press the Y Button to use it anytime. 
Also, you won't be able to see people while you're using it. Just EM bodies. 
<Geo-Visualizer> Got it. 
<Mega> Well, you can kind of see people, but it's pretty difficult. 
Just be really careful when walking around with the <Visualizer> on. 
<Geo-Visualizer> Alright. 
<Geo> Ah, a phone call... 
<Game> *beep* 
<Geo> Oh, Prez... What's up? 
<Prez> "What's up?"!? 
Don't give me "What's up?"! I can't believe that you 
just took off like that after class!! 
<Geo> Uhh... I kinda had something... 
<Prez> Yeah, yeah. 
Just come over to the Snack Shop on the 1st Floor, OK? 
<Prez> On{15}{E1} the{15}{E1} double!! 
<Geo> Man, she sure is angry with me today. 
<Mega> You better get over to that Snack Shop before she gets any angrier! 
