<Geo> It's the science club... 
<Woody> Is everybody ready? 
<Jack.Flask> Yes, sir! 
<Angel.Wise> Ready! 
<Woody> Great! Well let's get started, shall we? 
<Woody> We've finally completed this small scale rocket in our lab! 
At last, we can actually perform the flight test! 
<Game> *clak, clak* 
<Woody> Huh? What's that sound? 
<Game> *swooosh* 
<Woody> Ahhh! 
<Angel.Wise> The Sprinkler is out of control! 
<Jack.Flask> I'm reading a virus somewhere in the area! 
...It's inside the Sprinkler <Nucleo.Pro{67}{01}ramma-color> (CC)! 
<Woody> Everyone, stay calm! 
We all have Hunters and Battle Cards just for this very occasion, right? 
Let's take care of the virus together! 
<Jack.Flask> Take this! <Cannone>!! 
<Angel.Wise> <PlasmaGu{6E}{01}>!! <MiniGrnade>!! 
It's no use! 
<Jack.Flask> If only we had Wizards... 
<Angel.Wise> Then we could use Battle Cards more effectively! 
<Woody> Argh! Is science worthless!? 
<Jack.Flask> Sir! 
<Angel.Wise> Woody! 
<Woody> We have to protect the rocket! 
It's the symbol of all of our hard work! 
<Woody> Ahhh! 
<Jack.Flask> Whoaa! 
<Angel.Wise> Aaah! 
<Mega> We gotta help them, kid! 
What do you want to do? 
How about I hop into the Sprinkler Cyber Core and 
go buck wild on the viruses!? 
<Geo-2> Hmm... 
<Geo> No. Let's get them together. 
<Mega> Alright! It's been a while since we've done an "{47}{E2}"! 
Just don't forget to stay frosty, kid! 
<Geo-2> You got it! Let's <Trans.in-color> to the Sprinkler Cyber Core! 
<Geo-2> Take it easy, everyone! I can help! 
<Jack.Flask> What? How can you help? 
<Geo-2> Umm... J-Just don't worry about it. It's under control! 
<Mega> So, kid... About EM Wave Changes... 
Until now we could only EM Wave Change in certain areas. 
But thanks to the recent advancements in EM wave technology... 
We can do it anywhere! 
<Geo> Really? Cool. 
<Mega> Just "Cool"!? Are you even paying attention!? 
Whatever... For now let's just do this thing! 
Time to EM Wave Change into Mega Man!! 
<Geo> Let's do it! 
<Mega> Oh, wait. There's one more thing... 
Take a look at that. 
<Mega> That's the "<Stazione.d'Onda-color>" that controls all the EM waves for the school. 
As Mega Man we can enter the Wave Road with it! 
<Geo> Got it, Mega! 
<Geo> Alright.{14}{E1}.{14}{E1}.{14}{E1} 
It's EM Wave Change time! 
<Geo> {13}{EC}.{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
...Umm? 
<Mega> ...Uh? 
<Geo> I-It's not working, Mega! 
I even yelled and everything.. Man this is so embarrassing! 
<Mega> That's really strange. Yelling makes everything work... 
<Game> *beeeep* 
<Geo> Hmm, there's a message coming through the Hunter. 
<Game> EM Wave Change Detected... 
Satella Police accessing{15}{E1}.{15}{E1}.{15}{E1}.{15}{E1} Authenticating{16}{E1}.{16}{E1}.{16}{E1}.{16}{E1} 
<Geo> What the heck? 
This seems pretty serious! Are we in trouble? 
<Mega> Hmm... 
<Game> Authentication complete... 
Registering Geo Stelar and Omega-Xis as  EM Wave Change ID "003". 
ID card issued. Authentication code... 
"Mega Man". 
<Game> Upon EM Wave Change, authentication code is now required. 
<Geo> What was that? 
<Mega> It looks like we were registered with the {52}{E2}... 
And that we won't be able to EM Wave Change so easily anymore. 
I'm not really sure, but it seems like we need to  
use the code "Mega Man" when we EM Wave Change. 
Don't worry about it too much for now, OK? 
Let's do this thing! Use the R Button to EM Wave Change! 
Then enter the Wave Road through the Wave Station! 
<Geo-2> OK, let's do it! 
