<Woody> Hey! It seems that the Sprinkler is under control! 
<Jack.Flask> Woo hoo! 
<Angel.Wise> But, we're soaking wet! 
<Woody> Yeah, that's true... Unfortunately, I think we should postpone the launch. 
Remember, there's always tomorrow! 
<Jack.Flask> Oh yeah! Now that I think about it... I saw someone! 
I saw a boy wearing blue enter the Sprinkler when it was going out of control! 
<Geo> {13}{EC}Ack! 
<Woody> What!? That had to be Mega Man! 
<Angel.Wise> Amazing! You mean THE Mega Man? As in, our hero!? 
<Woody> Could the rumors that he goes to this school really be true? 
<Geo> {13}{EC}(T-This is bad! I've got to  stop this conversation  before it gets crazy!) 
E-Excuse me! 
<Geo> What kind of experiment were you conducting? 
<Woody> Oh, we were attempting to launch a rocket. 
<Geo> A rocket!? 
<Woody> Yeah, we're building a rocket in the 2nd Floor Sci. Club Room. 
But it's not going so well. 
<Jack.Flask> We thought we'd run some tests on a smaller version 
made from the same materials. 
<Woody> As the Science Club, we have formed a Team with 
the "Purpose" to  "Launch a Rocket". 
<Angel.Wise> I know we will be successful in fulfilling our "Purpose"! 
Right!? 
<Woody> Yeah, let's do our best! 
<Mega> ..."Purpose"? 
What does that mean? 
<Geo> I guess you could say that a Purpose is a "goal". 
<Mega> A "goal"... 
<Geo> The Purpose function is a new function that has evolved the Brother Bands 
that bond friends together. It's becoming pretty common as of late. 
After deciding a goal you want to achieve or a 
dream you want to come true, you can set it as a "<Proposito-color>" and then form 
a "<Squadra-color>" with others who share the same Purpose. 
<Woody> {13}{EC}...? 
Who are you talking to? 
<Geo> Umm, hehe... 
<Woody> Oh yeah, I haven't introduced myself yet. 
My name is Woodrow Boffin. I'm in 6th grade right now. 
People usually call me "Woody". 
<Geo> I'm Geo Stelar. 
<Woody> Geo, eh? Do you have any Purposes at the moment, Geo? 
<Geo> Me? N-Not really... 
<Woody> I see. 
Well I hope that you find a great Purpose and do 
your best to fulfill it with your friends someday! 
We are definitely going to fulfill our Purpose to  "Launch a Rocket"! 
<Geo> I don't know anything about rockets, but I can at least cheer you on! 
Please show me the rocket when it's ready! 
<Woody> You got it! 
<Woody> OK guys, let's get back to the Sci. Club Room. 
<Jack.Flask> Yes, sir! 
<Angel.Wise> OK, Woody! 
<Mega> What's wrong, kid? You look a little depressed. 
<Geo> Talking about the rocket made me think about Dad. 
<Mega> Kelvin, huh? 
<Geo> He's still missing in space even after all this time... 
But Mom and I believe that he is still alive somewhere... 
<Mega> There's no doubt about it, he's still alive, kid... 
The Kelvin I met in space isn't someone who would keel over so easily! 
<Geo> Yeah, you're right! 
<Mega> By the way... Didn't you have something you had to do? 
<Geo> Something to do...? 
{13}{EC}.{13}{E1}.{13}{E1}.{13}{E1}.{13}{E1}.{13}{E1} 
<Geo> Oh, man! 
I was supposed to meet Prez! 
<Mega> At the Snack Shop on the 1st Floor, right? 
You're running pretty late. She's gonna be angry! 
<Geo> I-I-I gotta hurry! 
