<Geo> Ahh! 
<Harry.Sasoon> Ow! 
I scraped my knee... 
<Angel.Wise> Oh, it's the school nurse! 
*What happened? Let's get you back to the Nurse's Office, OK? 
*Wizard On! 
*Can you please take this child to the Nurse's Office? 
{94}{00}Sure thing! I'll just perform some first aid beforehand. 
{10}{E2}{BA}{03} 
{94}{00}Healing Pulse! 
<Harry.Sasoon> .{15}{E1}.{15}{E1}.{15}{E1}It stopped hurting! 
Wizards are great! 
{94}{00}OK, then let's get going! 
{94}{00}Clear the way everyone! 
<Geo> That's a Wizard! 
<Mega> A Wizard, huh? They've become a big part of everyday life lately. 
Meh, big deal. 
<Geo> Don't be like that, Mega. 
You're quite the Wizard yourself! 
Why don't I give you a special explanation about Wizards! 
<Mega> That's not really... 
<Geo> Ahem! Are you ready, Mega? 
{12}{E2}<Mr.King-2> {00}{00} 
<Mega> {13}{EC}(Grrr...  Looks like I lit a fire  under Geo's Wizard-mania...) 
<Geo> Up until now, EM beings couldn't be seen without something like my <Visualizer>. 
However, thanks to EM technology advancements, 
even normal people can see and touch EM beings. 
In short, a Wizard is a  materialized EM being!! 
<Mega> *yawn* Interesting... 
<Geo> A Wizard usually works intimately together with a <Hunter>. 
Just like you, Mega. 
<Mega> Yeah, I guess... 
<Geo> Wizards have been getting really popular lately. 
Just about every person has one! 
Recently, Wizards that manage the running of 
machines have been gaining popularity, as well. 
{13}{E2}{01}{00} 
<Mega> So, I was able to become fully materialized thanks to the improvement of EM 
wave technology and the development of Wizards. 
<Mega> It was such a pain in the butt not being visible to normal humans. 
{11}{E2}{02}{00} 
<Geo> W-Wait a second, Mega! 
I thought I said you can't show yourself at school!? You'll stick out too much! 
<Mega> But it doesn't really matter if I stick out since I'm a Wizard now! 
<Angel.Wise> Cool! Is this your <Wizard-color>? 
<Jack.Flask> He looks so cool! Is he a Battle Wizard? He looks powerful! 
<Mega> Hehe... I am pretty cool-looking and powerful, aren't I? 
<Geo> For crying out loud... 
<Mega> You should be proud, kid! 
You're the <Operatore> of this cool-looking and powerful Wizard after all! 
<Geo> It's not cool to get all into yourself like that... 
