<Prez> You're la{13}{E1}a{13}{E1}a{13}{E1}a{13}{E1}a{13}{E1}a{13}{E1}a{13}{E1}a{13}{E1}a{13}{E1}te!{13}{E1} 
<Prez> Late!!{14}{E1} Late!!{14}{E1} Late!!{14}{E1} 
What could you possibly have been doing!? 
How long do you think it's been since I called you!? 
<Geo> Um... well... 
<Zack> Geo! As you can see, Prez is really angry with you! 
<Bud> I don't want her to take it out on me, so I'm keeping my mouth shut! 
<Geo> Come on, Bud! 
<Zack> I don't want to get caught up in anything either, so 
the best I can do is support you from here! 
<Geo> You too, Zack!? 
{A0}{E1}{04}{00}< 
<Prez> You just keep quiet, Geo! 
<Prez> There wouldn't be a problem if you had come on time, right? 
<Geo> Yeah... I'm sorry... 
<Prez> {13}{EC}... 
...D-Don't look so down or you'll make me look like some evil dictator... 
...I-I mean if there's a reason you were late, I may accept it... 
<Zack> Just tell her, Geo! 
<Geo> Well, I was on the roof and the Sprinkler went out of control and... 
<Prez> Ah... 
<Geo> ...It turned out it was caused by viruses, so I deleted them. 
<Prez> That sounds pretty rough{15}{E1}.{15}{E1}.{15}{E1}.{15}{E1} 
Wait, so that means that you turned into my beloved Mega Man!? 
<Geo> Um... Well, yeah... 
<Prez> If that's the case, then you should have come here as Mega Man! 
Why did you come here as just plain old Geo!? 
<Geo> I-I don't really... 
<Bud> As always, Prez is totally falling head over heels for Mega Man! 
<Prez> I'll say it again, Geo. 
I'm a fan of Mega Man, but I'm not a fan of either you or Omega-Xis. 
How is it possible that Mega Man is so amazing 
and cool, yet you are just a plain old kid? 
<Geo> Ouch, that's pretty mean. 
<Prez> And I can't believe how violent and ill-mannered that 
Wizard you need to become Mega Man is... 
<Mega> Who are you calling ill-mannered? 
<Prez> Ahhhh! 
Omega-Xis! Don't scare me like that! 
<Mega> I'll say this just once for your sake, but I'm originally an alien, not a Wizard. 
An AM-ian that grew up on Planet FM... 
<Prez> O-OK, I understand! 
Just hurry up and go on home back to Geo's <Hunter>! 
<Mega> .{13}{E1}.{13}{E1}.{13}{E1}.{13}{E1}.{13}{E1} 
<Prez> W-What are you looking at? 
J-Just... 
{A0}{E1}{04}{00}< 
<Mega> Rooaaarrr!! 
<Prez> Ahhhh! 
<Mega> Rooaaarrr!! Grrrr!! 
<Prez> Ahhhh! Stop! 
<Bud> And as always, Prez can't get along with Omega-Xis... 
<Zack> Get along? She's terrible with him! 
<Prez> G-G-G-G-Geo! He's your Wizard, right!? Do something about him! 
<Mega> Rooaaarrr!! Grrrr!! 
<Zack> Geo! It looks like Prez is going to start crying! 
<Bud> Shouldn't you put him back? 
<Geo> Alright, that's enough, Mega. 
Wizard Off! 
<Prez> *huff, huff* 
I can't *huff* believe Geo and *puff* his stupid *huff* Wizard... 
<Geo> Um, Prez... Wasn't there something you called me about? 
<Prez> ...Oh yeah!! 
<Prez> Listen very carefully! 
All four of us are going to{13}{E1}.{13}{E1}.{13}{E1}. form a Team and fulfill a new Purpose! 
<Geo> We are!? 
<Bud> Does that mean we get to try porpoise? 
I've never eaten porpoise before! 
<Zack> Purpose, Bud! Not porpoise! 
<Prez> It's just not in fashion to be <Brother-color>s and not have a Purpose. 
So I've decided we are going to fulfill our own Purpose! 
<Geo> So, what kind of Purpose are we going to fulfill? 
<Prez> Heeheehee... Think reeaally hard. 
What really big event is going to take place here at school soon?  
<Geo> .{14}{E1}.{14}{E1}.{14}{E1}Umm? 
<Zack> I know there was definitely something. 
<Bud> Oh! There's gonna be pizza on next week's lunch menu! 
<Geo> That's true... 
So, are you considering fulfilling a Purpose related to pizza, Prez? 
<Mega> Ohh... Form a Team around pizza... 
<Prez> Wrong, you imbeciles! 
Soon there's going to be an election for student body president! 
<Geo> A student body president election, huh? 
Wait, Prez... You mean...? 
<Prez> Exactly!!! 
I, Luna Platz, am going to run for student body president! 
<Zack> So you're aiming to move even higher up in the 
world, from class president to student body president? 
<Prez> That's correct. I believe that I am  perfect for the position. 
<Bud> Wow! 
It'll be so fun to have Prez be student body president! 
I support you 100%! 
<Geo> Yeah, I guess there really isn't anyone else that 
could do the job as well as Prez could. 
<Prez> Then it's settled! 
However, first we have to re-form our "Brother 
Bands" before we can set our Purpose. 
<Geo> Oh, yeah. 
Our Brothers were deleted during the last class... 
<Prez> That's right! 
Geo and I will re-form our Brother Band first! 
<Prez> So, Geo, shall I explain Brother Bands to you? 
{05}{EC}{00}{00}{02}{00}   {06}{EC}Yes   {07}{EC}No 
{11}{EC}{00}{00}{0F}{00}{11}{EC}{01}{00}{13}{00}
<Prez> Brother Bands are a way to connect oneself to 
close and trusted friends through EM waves. 
Even if separated by great distances, anyone 
can stay aware of their Brother's current state. 
Even if not friends, one can become a Brother with anyone they care about. 
For example, family members can become Brothers. 
My mother and father are my Brothers. So when they are both busy at work, 
we keep each other updated via the Brother Band system. 
No matter how much technology advances, 
and no matter how convenient it becomes, 
one's connection to others will always be the most important thing. 
From those connections the mysterious power called Link Power is born. 
Link Power displays the strength of a link via a number. 
The more one is trusted by their Brother, the more 
Link Power one gains from that Brother. 
Helping out one another and forming a deeper link will also raise Link Power. 
Once Link Power reaches a certain level, Abilities can be equipped. 
I'm not an expert, but it seems that Link Power is 
connected to one's strength as well. 
You can check how much Link Power someone is giving you by talking to 
them and touching the Brother Band pop-up. 
By the way, one can also form Brother Bands with 
real life friends. They are called Real Brothers. 
{06}{E1}{12}{00}
<Prez> Do you need an  explanation on how to form Real Brother Bands? 
{05}{EC}{00}{00}{02}{00}   {06}{EC}Yes   {07}{EC}No 
{11}{EC}{00}{00}{0F}{00}{11}{EC}{01}{00}{13}{00}
<Prez> OK, I'll explain how to fill in one's profile. This is 
extremely important to the Brother Band system. 
