<Geo> We've finally re-formed our Brother Bands! 
<Prez> Now we can form our Team and set our Purpose! 
<Geo> But before that don't we need some kind of Team name or something? 
<Bud> How about "Team Tortellini"? 
<Zack> Since our Purpose is "Luna for SBPrez", the 
Team name should be related to that. 
<Bud> Fine! Just ignore me! 
<Prez> There's no need to worry everyone! 
I've already come up with a Team name! 
<Zack> Prez is always on top of things like this! 
<Prez> I couldn't sleep at all last night thinking about it! 
But I, of course, was able to come up with a brilliant Team name! 
<Geo> Well, let's hear it! 
{13}{E2}{00}{00} 
<Prez> Listen well and be amazed! 
The Team name is.{15}{E1}.{15}{E1}.{15}{E1} 
{10}{E2}{35}{03}{16}{EC} 
<Prez> "Luna 4 Prez"! 
<Geo> I'm kind of speechless... 
<Bud> She stayed up all night to come up with that? 
<Zack> To be honest, Prez never was good at coming up with names. 
I once had her think of a name for my first pet. ...Poor Catnip. 
<Geo> Catnip because he's a cat... 
<Zack> No. 
Catnip is a dog... *sigh* 
<Prez> What is everyone muttering about? 
<Geo> N-Nothing at all! 
<Bud> It's a great name! 
<Zack> Luna for school body president! 
<Prez> Great. I'm glad everyone is in agreement. 
OK, let's set our Purpose and Team name into our Hunters! 
{04}{E2}{01}{00} 
<Game> Geo's Team and Purpose have been set! 
<Geo> Looks like it's set. 
Setting your first Team and Purpose is kind of moving. 
<Prez> Well, it's time to get started working as Team "Luna 4 Prez"! 
<Bud> But what can we do to help Prez become the student body president? 
<Zack> Hmm, good point. What should we do, Prez? 
<Prez> First, we should find kids here in the school who 
are having trouble and then help them out. 
Of course, I will do all of the helping. 
Then my approval rating will skyrocket! 
Zack! 
You have a Wizard that is great with numbers, right? 
He's going to keep track of my approval rating, OK!? 
<Zack> Understood, Prez! 
<Zack> Wizard On! 
<Pedia> Thank you for calling me out, Zack! 
Everyone, my name is Pedia! You can leave any calculating to me! 
<Zack> We're an even stronger Team with Pedia around! 
<Pedia> My database is filled with a vast amount of facts! 
Plus, I can calculate any and all rankings and 
percentages possible, with ease! 
There is truly no figure I cannot calculate! 
<Bud> Wow! 
<Prez> You'll be very useful, Pedia! 
I really want to get my own Wizard ASAP! 
<Bud> Wow! I'm really jealous, Zack! 
<Zack> Don't say that, Bud... 
<Mega> *sigh* 
<Geo> Don't be like that, Mega! 
This school will be really fun with Prez as student body president! 
<Mega> You're such a sucker, kid... 
<Geo> Alright! Let's go find kids that are in trouble! 
<Zack> Yeah! 
<Bud> Let's go! 
