<Harry.Sasoon> *sigh* 
<Jack.Flask> *sigh* 
<Geo> They look pretty down. I wonder what's wrong? 
<Mega> Don't worry about them. 
Why don't you put on your <Visualizer>, instead? 
<Geo> Huh? What's up? 
<Geo> Oh! 
<Mega> Everything looks completely different, doesn't it? 
<Geo> Yeah... When looking at the world 
this way, I can see that the tree is a "Real Wave". 
<Mega> These things are popping up everywhere, lately. 
Real Waves are things that are made from materialized EM waves, right? 
I'm pretty sure Battle Cards are also Real Waves. 
<Geo> That's right. And nowadays, EM waves are being used 
to make everything from cars to buildings. 
<Harry.Sasoon> There's just no way, huh? 
<Jack.Flask> That's how it seems, eh? 
<Prez> Here you are, Geo. Have you found anyone? 
<Geo> Well, umm... 
<Harry.Sasoon> *sigh* 
<Jack.Flask> *sigh* 
<Prez> Oh, those two look like they are having some trouble. 
Hey, you two! Is there anything I can help you with!? 
<Harry.Sasoon> Well, you see... 
We want to give our friend, Stey, a birthday present. 
<Prez> My, isn't that touching! 
<Jack.Flask> Both of Stey's parents have to work today, so she's all alone. 
So, we want her to have a really memorable birthday. 
<Harry.Sasoon> We were thinking we could use this Real Wave tree. 
The plan is to overwrite the tree's program to make it bloom full of 
beautiful flowers, and then show it to Stey. 
<Geo> That's a great idea. She'll be really happy! 
<Harry.Sasoon> Yeah, but it seems that the tree's program has a 
mega lock put on it by a teacher. 
<Mega> Yeah? 
<Geo> Not you, "Mega". It has a "mega lock" on it. 
<Geo> So... Why don't you just ask the teacher in charge? 
<Jack.Flask> Well we want to, but... 
The teacher in charge is incredibly scary. 
<Harry.Sasoon> We're too scared to go up to him... Yeah... 
<Geo> A scary teacher, huh? 
<Prez> There's definitely a mega lock on this. Nothing will work for me. 
<Prez> You should do something for them, Geo! 
<Geo> M-Me!? B-But they said the teacher is scary... 
<Prez> That's probably because he's an adult. That's no reason to be scared! 
Remember, this is for our Purpose! 
<Geo> I guess I have no choice. (No excuse I use is going  to work on her...) 
That scary teacher should still be at school, so let's search around here first. 
<Mega> You're a tough one, kid. 
