<Geo> The e-mail you sent was stuck on the Wave Road, 
but I found it and it'll be delivered properly! 
<Angel.Wise> Really!? Thank you so much! 
I still haven't received a response yet, though. 
<Mary.McLovin> Heeey! 
<Mary.McLovin> I read your e-mail! I'm sorry, too! 
<Angel.Wise> No, no, no. It's all my fault... 
<Mary.McLovin> Either way, let's never fight again! Ever! 
<Angel.Wise> Yeah, best friends forever! 
<Geo> Sweet... Another problem solved. 
<Mega> Hehe. Feels pretty good to help out, doesn't it? 
<Angel.Wise> It's all thanks to you! Thank you, again! 
<Geo> There's no need to thank me, really... 
{13}{E2}{01}{00} 
<Prez> Isn't friendship just the most wonderful thing!? 
<Mega> What a surprise... 
<Prez> Geo Stelar over here is a member of my Team, "Luna 4 Prez"! 
I'm the Team leader, Luna Platz! 
I'm actually running for student body president in the upcoming election. 
I would be honored to have your support for student body president! 
<Mary.McLovin> Thank you very much, Luna! 
<Angel.Wise> You got my vote for the upcoming election! 
<Prez> Thanks! I won't let you down! 
<Prez> Thanks a lot, Geo! You're doing pretty good! 
<Geo> Yeah, but are there any more people that need help around here? 
<Geo> Ah, a phone call... 
<Geo> What's up, Zack? 
<Zack> Oh, is Prez with you, too? That's perfect. 
Can the both of you please come to the Sci. Club Room? 
There's a situation here. 
<Geo> Got it! We'll be right there! 
<Prez> The Sci. Club Room, right? Let's go, Geo! 
<Geo> The Sci. Club Room...? 
<Mega> Wasn't the Science Club doing an experiment on the roof before? 
<Geo> Yeah, that's them. 
The Sci. Club Room is on the 2nd Floor. Let's head over there. 
