<Geo> Sorry for the wait, Prez. 
<Prez> Thank you for coming, Geo. 
Let me introduce everyone. This is the head of the Science Club, Woody. 
<Woody> Hey. Nice to see you again. 
<Prez> Oh, you know each other? 
<Geo> Yeah, we met on the roof earlier today. 
Their club's Purpose is "Launch a Rocket". 
<Prez> If you're already familiar, then I can explain very quickly. 
Geo! Bud! Zack! 
Team "Luna 4 Prez" is going to manage the construction of the rocket! 
<Zack> Interesting... 
By "manage" you mean oversee and help with all things in general, right? 
<Bud> But Prez! That's impossible! 
We don't know anything about this kind of stuff! 
<Woody> It's true that construction of a rocket is very 
complicated, but this rocket is just about finished. 
<Woody> All we need to complete the process is a Giga Energy Card. 
If we just had that we could perform the launch. 
<Geo> A Giga Energy Card? 
<Woody> Yes. I think we should have Magnes explain. 
Come on out, Magnes! 
<Magnes> Yup! I'm Magnes! 
<Prez> Are you a Wizard? 
<Magnes> Yup! I'm a Wizard! 
<Geo> Awesome! I didn't know there were rocket specialist Wizards! 
<Magnes> Yup! 
I'm going to act as the brain and pilot of the rocket for its space flight! 
But, as Woody said, we still need one more item to complete the rocket. 
<Geo> A Giga Energy Card, right? 
<Magnes> Yup... 
<Magnes> We are going to use both fuel and my magnetic 
abilities to launch the rocket. But that's still not enough. 
A Giga Energy Card would give us the power needed to successfully launch. 
<Geo> So you can't move on without it... 
<Magnes> Yup... 
<Woody> Giga Energy Cards are used mainly by police and the government. 
Most civilians have never even seen one. 
<Prez> How much do they cost? 
<Woody> .{15}{E1}.{15}{E1}.{15}{E1}What? 
<Prez> Tell me how much money it would take to buy one. 
I'll send you the proper amount of EM money right to your <Hunter>. 
<Geo> P-Prez! That's no good! 
<Zack> We have to run a clean campaign! 
<Bud> What's the matter? 
<Geo> Everyone will see it as bribery! 
<Woody> I'm very thankful, but one can't simply buy a Giga Energy Card. 
They are too powerful to be legally sold to civilians. 
<Bud> Saying elementary school students are going to use it for a school club won't... 
<Woody> Totally impossible... 
<Prez> I see. Well, that's that, then. 
<Geo> There has to be some other way, right? 
<Pedia> Unfortunately, there is only a one percent chance of acquiring one. 
<Zack> Unless a miracle occurs... 
<Geo> We can't just give up after they've come so far. 
<Prez> Geo is right. 
<Game> *beep, beep* 
<Prez> What's that? 
<Geo> Ah, sorry. That's my <Hunter>. 
<Mega> It's a pop-up from school. Take a look at it. 
<Bud> What is it, Geo? 
<Geo> It says there's somebody here to see me on the 1st Floor. 
Who could it be? I'll go and see. 
