<Geo> Hmm, there's no one here... 
<Mega> Is this the right place? 
<Geo> It should be. 
<Prez> Where is your visitor? 
<Geo> I'm not really sure... 
{13}{E2}{01}{00} 
<Game> Ah, my bad. Over here. 
<Mega> Who's that? 
<Geo> No clue... 
<Ace> Since all schools have a Snack Shop, I took a look around and found yours. 
Bought me a ton of cheap candy. 
<Bud> Oh, wow! That's a "{6A}{E2}"!! 
They're so good even though they only cost 10 zennys each!! 
<Ace> Oooh, sounds like I made a good decision. 
Let me give one a shot. 
<Game> *munch, munch* 
<Bud> They're great, right? 
<Ace> Yeah, man that's good! Not a bad deal for only 10 zennys. 
<Geo> Umm... Are you the person who... 
<Ace> Yep, that's me. 
I was here when you were running all around, but you probably didn't notice, eh? 
<Geo> {13}{EC}(Maybe I did see him...) 
<Ace> My name is Eos. A.C. Eos. But people usually just call me "Ace". 
Nice to meet you. You're Geo Stelar, right? 
<Geo> Yes, but... 
How did you know... 
<Ace> Your name is well known in my line of work... 
And Mega Man, too. 
{13}{E2}{00}{00}
<Geo-2> {13}{EC}(How could he...!?) 
<Prez> {13}{EC}(This man...) 
<Bud> {13}{EC}(He knows...) 
<Zack> {13}{EC}(Mega Man's true identity!?) 
<Ace> Don't freak out, guys. I'm not your enemy. 
<Geo-2> So then who are you? 
<Ace> I can't really say at the moment, but the time will come when I can. 
For the time being, I want you to come to <Spica.Mall> tomorrow. 
<Geo-2> <Spica.Mall>...? 
<Prez> It's a new mall that just opened. It takes about 10 minutes by train. 
<Ace> The world famous "Wave Battle Tournament" will be taking place there. 
I want you to participate in the tournament. 
<Zack> You don't have to listen to this guy, Geo! 
<Prez> I agree! This guy's creepy! Something isn't right here! 
<Ace> Hey, let's be nice now. 
<Prez> Well, our Team is just a little bit busy trying to 
get our hands on a Giga Energy Card right now. 
<Ace> A Giga Energy Card, eh? 
<Ace> You need a Giga Energy Card? 
<Geo-2> Yeah... 
<Ace> Alright, I'll get you one. 
<Geo-2> W-What do you mean!? 
<Ace> Well, if you guys really need it, I'm just saying that I can get you one. 
<Prez> B-But that's... 
We heard that Giga Energy Cards aren't something just anyone can get. 
<Ace> I can get you one. 
But you'll have to take part in the 
"Wave Battle Tournament" at <Spica.Mall> to earn it. 
<Prez> You have to do it, Geo! 
<Geo> What!? 
<Ace> Then it's decided. 
<Ace> I'll see you tomorrow afternoon at <Spica.Mall>'s {BD}{E4}. 
As long as you show up you'll get that Giga Energy Card. 
<Ace> I'm looking forward to tomorrow, Geo... 
I mean, Mega Man. 
<Geo-2> {13}{EC}... 
<Geo-2> Who the heck is that guy? 
<Mega> He seems similar... 
<Geo> Huh? Similar to who? 
<Mega> To you, kid. 
<Geo> I'm not that cool. 
<Mega> Not really similar by looks, kid. More like your vibe. 
<Prez> Anyway, we're all going to <Spica.Mall> tomorrow! 
<Zack> Maybe we can find out who that Ace guy really is. 
<Geo> That's true... 
I'm really interested in how he knows that I'm Mega Man. 
And we also really need that Giga Energy Card. 
<Mega> Then we're definitely going. 
<Prez> Everyone should go home and get some sleep. 
We'll meet at the Echo Ridge Wicket tomorrow. 
<Geo> OK! 
<Mega> ...I'm beat after all that happened today. 
Let's get back home, kid. 
