*Alriiiiight! 
The winner of this year's Wave Battle Tournament 
is A.C. Eos and his battle wizard, Acid! 
I've never seen so many veterans beat so easily! What a performance! 
<Ace> It wasn't anything at all! 
No one can take on Acid and I! 
<Geo> I-It's over already!? 
<Prez> We were only ten minutes late! What's up with that!? 
<Zack> Let me check with Pedia on the results! 
<Pedia> You can count on me! Just give me a second! 
{13}{EC}.{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1}.{14}{E1} 
I don't believe it! 
<Zack> What is it, Pedia? 
<Pedia> That Eos guy's Wizard... 
He defeated 60 Wizards in a row! 
On top of that... 
Not only did he receive an S Busting Level, but he 
won each match in less than five seconds! 
<Prez> N-No way... How is that possible? 
<Geo-2> That's no normal Wizard... 
<Mega> They said the Wizard's name was "Acid", right? 
Who the heck does he think he is!? I'll take him any time, any place!! 
*Ladies and gentlemen... It's now time for the main event! 
This year's champion will go up against the planet's greatest hero... 
Mega Man! 
<Game> The same Mega Man who has saved the Earth twice now? 
<Game> No way! He's here? 
{16}{EC}{10}{E2}{3B}{03} 
<Game> Go Go Mega Man! 
*Umm... He's really coming, right? 
<Ace> Oh, he'll show up... 
And with the crowd this excited there's no way he 
can back down. Isn't that right, Geo Stelar? 
<Game> *munch, munch* 
<Mega> He hasn't given us any way out of this one... He's pretty good! 
<Prez> What do you think, Geo? 
<Geo> I have no choice really. 
Whether I win or lose, if this is what it takes to 
get the Giga Energy Card, then I'll do it. 
<Prez> If you think you're going to lose, get out of here. 
We really need that Giga Energy Card but... 
It's not worth you getting hurt over it... 
<Geo> Don't worry, I'll be fine... Probably. 
<Mega> Don't even think for a second that we can lose to that guy! 
<Game> Transcode!{01}{E1} Mega Man! 
