{90}{00}{13}{EC}*zzt, zzt* 
<Megaman> *huff, huff* It looks like he's gone back to normal. 
<Mega> He was pretty tough, huh? 
<Megaman> But why did he go out of control...? 
I've never heard of such a thing before. 
{10}{E2}{3E}{03}{16}{EC} 
{90}{00}{13}{EC}*zzt, zzt* 
{99}{00}Ergaaaaaah! 
<Megaman> W-What!? 
<Mega> He's coming back for more! 
{13}{E2}{00}{00} 
<Ace> Don't worry, Mega Man. 
<Megaman> Get back, Ace! It's too dangerous! 
<Ace> Don't underestimate me Mega Man! 
My Wizard is no slouch, trust me. 
{99}{00}Ergaaaaaah! 
<Ace> Let's go, Acid! 
<Ace> Wizard On! 
<Mega> He... 
<Megaman> Acid...!! 
<Acid> Target captured... 
Sentencing... 
<Acid> Guilty Slash!!! 
{90}{00}{13}{EC}*zzt* 
<Acid> Mission complete, Ace. 
<Ace> Nice job, Acid. Situation resolved, eh? 
<Megaman> {13}{EC}(That was so quick...  I couldn't see a thing.) 
<Ace> Huh? 
<Megaman> Is that a playing card? 
<Mega> It came from the Wizard that was out of control... 
<Ace> This card... 
They've finally played their hand, eh? 
<Acid> So it would seem... 
<Megaman> They...? 
<Ace> Some dangerous people... 
{16}{EC}{10}{E2}{30}{03} 
{94}{00}*siren, siren* 
<Acid> It's a shame that we didn't get to have our battle today, Mega Man. 
I was looking forward to it. 
<Mega> Who do you think you are? 
You think you can talk like that just because you won 
some tournament full of scrubs!? 
<Acid> I was only expressing my regret. 
I suppose it doesn't really matter, as I would have won anyway. 
<Mega> You can't talk like that to me!! 
Let's do this thing! Right here, right now!! 
Come on, kid!! We're gonna teach this guy a lesson! 
<Megaman> Please ignore him, Ace. He's a little aggressive for a Wizard. 
<Mega> Why are you so calm!? 
<Ace> Acid, you should try and cool off, as well, OK? 
I understand you want a bit of competition, but 
now's not the time to stir things up. 
<Acid> ...I'm sorry, Ace. 
I just can't help but tease a straight shooter like Omega-Xis over here. 
<Mega> *roar* 
Now you're just asking for a world of pain! 
<Ace> Oh, yeah. As I promised, here's the Giga Energy Card. 
{02}{E2}{04}{00}{A1}{E1} 
<Game> Mega Man got: "{E4}{E6}"! 
{01}{E2}{04}{00} 
<Ace> I have a feeling we'll be seeing each other again soon. Until then... 
<Acid> I look forward to our next encounter, Omega-Xis. 
<Mega> Just shut up already and get out of my face!! 
<Megaman> I wonder who they are... 
<Mega> *growl* At least we got what we wanted! 
Let's get back to Prez and the guys! 
<Megaman> Sounds good. 
