<Geo> We got the Giga Energy Card, Prez. Here you go. 
<Prez> Wow, you did it, Geo! 
Since we couldn't have gotten it without you, I 
think you should be the one to give it to the Science Club. 
<Geo> Sure, sounds good. 
<Bud> Woohoo! Let's get back to school! 
<Zack> The Science Club members are going to be so happy! 
<Geo> Are those people... 
<Zack> They're Satella Police Commandos! 
<Geo> Whoa! So it really is them! 
I've never seen them in person before! 
<Zack> Wow, those guys are just soooo cool! 
<Bud> What are you guys so excited about? 
<Prez> What are those guys up to? 
<Geo> You don't know!? They're Satella Police Commandos! 
<Prez> I have no clue what that even means. 
<Zack> They're an organization directly under the control of {51}{E2}. 
They deal with the EM wave related crimes that 
have risen along with the spread of Wizards and Real Waves. 
Only the most skilled and experienced members can even think of joining. 
<Bud> Wow! They sound really elite! 
<Geo> They're so cool... 
<Prez> Boys really like that kind of stuff, don't they? I couldn't care less, really. 
<Geo> You couldn't care less? 
We need to get you to care if you want to be our esteemed Team leader! 
<Zack> Geo's right... 
Would you like to hear a complete history of the Satella Police? 
<Prez> No, that's OK! 
It's hard, but I'll do my best to restrain my enthusiasm... 
They don't really have much to do with our Team anyway. 
<Geo> Really, it's fine! 
<Zack> Yeah, I just know you'll be moved by the great story of the Satella Police! 
<Prez> But it'll take way too long to tell with the both of you so crazy about it! 
<Mega> Ain't that the truth... 
0Are you OK, Eos? Sorry we're late. 
<Ace> No worries. 
More importantly, the Wizard that went out of control 
dropped one of those cards. It looks like they've started to move. 
0That's how it looks, huh? 
That Wizard going out of control made the Noise Level spike quite high. 
<Ace> That was their intent from the beginning. We were completely fooled. 
The same thing will probably occur somewhere else sooner or later. 
0Oh, yeah. Did you get to fight Mega Man, Eos? 
<Ace> No. We were about to when the incident occurred. 
0Ah, no big deal I suppose. 
For now, let's maintain our watch on Geo Stelar. 
