<Geo> We got the Giga Energy Card, Woody! 
<Woody> Y-You really got one!? 
<Jack.Flask> It's a miracle! 
<Angel.Wise> Thank you so much!! 
<Geo> Hmm... I gotta touch the Giga Energy Card to give it to Woody.{13}{EC} {03}{E2}{04}{00}{04}{EC} 
<Game> Geo gave the "{E4}{E6}" to Woody! 
<Woody> I don't even know what to say! 
<Prez> You don't have to say anything at all. 
But I would be honored to have your vote in the upcoming election! 
<Woody> That doesn't seem enough to show our appreciation, 
but if it means that much to you, we'll do it! 
<Woody> Well, everyone! 
Now that we have the card, all we have to do is install it! Let's do it! 
<Jack.Flask> Alright! 
<Angel.Wise> OK, Woody! 
<Woody> It's{13}{E1}.{13}{E1}.{13}{E1}.{13}{E1} It's.{13}{E1}.{13}{E1}.{13}{E1} 
It's done! 
At long last... Our rocket is complete! 
Yeeeaaah! 
<Jack.Flask> Woody! 
<Angel.Wise> Don't cry, Woody! 
U{13}{E1}.{13}{E1}.{13}{E1}.{13}{E1}waaa{13}{E1}.{13}{E1}.{13}{E1}.{13}{E1}aaa! 
<Jack.Flask> I'm so happy! 
<Woody> I'm so proud of everyone. You make me so happy. 
You guys believed in me all the way to the very end. 
The Science Club is the greatest team ever! 
<Jack.Flask> Of course we did, Woody! 
<Angel.Wise> You're the best! 
<Prez> *sniffle* Everything turned out so perfect... 
<Geo> Their sacrifice paid off... 
<Geo> I'm really glad I joined the team, Prez! 
<Bud> "Luna 4 Prez" is the best! 
<Zack> This is what a Purpose is all about! 
<Woody> We couldn't have done it without you all. 
Thank you so much. 
<Woody> Magnes! Come out and thank them! 
<Magnes> Yup! You guys were great! Thanks for everything! 
Now I'll be able to contact the Science Club from space. 
My dream is going to come true! 
<Woody> I can't wait! 
<Magnes> Yup! 
<Woody> It's really all thanks to "Luna 4 Prez". 
If you don't mind, I'd like to form a Brother Band 
with the people who worked so hard along with me. 
<Prez> Of course we don't mind! Right, Geo? 
<Geo> Yeah! 
{6E}{E1}{00}{00}{11}{00} 
<Game> Geo and Woody formed a Brother Band! 
Geo's Link Power went up by 40. 
<Prez> How about us, too? 
<Woody> What do you mean? 
<Prez> Would it be alright if our Team set the same Purpose as the Science 
Club, until the rocket is successfully launched? 
<Woody> Eh!? Really? 
<Prez> I want to be there until the end. 
Now that Woody is our Brother, it's a great idea, isn't it? 
<Geo> Of course! 
<Woody> Thank you... 
Two Teams working together is great. 
But both Teams having the same Purpose is absolutely amazing. 
<Game> Geo's Purpose has changed! 
<Woody> I'm planning to have the launch ceremony tomorrow. 
I would be honored to have the "Luna 4 Prez" members join as producers. 
<Prez> We would love to! 
<Geo> I can't wait! 
<Bud> Do your best, Magnes! 
<Magnes> Yup! 
<Zack> So, let's all meet tomorrow on the roof! 
<Prez> Good idea. Everyone try and get to bed early, tonight! 
<Zack> Understood! 
<Bud> OK, see you tomorrow! 
<Geo> Let's go home, Mega. 
<Mega> Sounds good. Tomorrow should be a blast! 
