<Woody> Thank you for coming out today, everyone! 
It's finally time for the Science Club to launch the rocket we constructed! 
<Game> Woohoo! Yay! Right on! 
<Woody> But first I would like to introduce the Team that acted as producer for us. 
I give you the leader of "Luna 4 Prez", Luna Platz, and the other members! 
<Game> Woo! Go Luna! Yeah! 
<Prez> What a wonderful feeling to have everyone cheer for me! 
<Pedia> Zack, Prez's approval rating is skyrocketing! 
<Zack> If the rocket launches successfully, there's no 
doubt her approval rating will go over 40%! 
<Woody> At long last... Let's launch the rocket! 
Magnes, please start the launch preparations! 
<Game> *dum* {13}{E1}*dum* {13}{E1}*dum* {13}{E1}*dum*{13}{E1}.{13}{E1}.{13}{E1}. 
<Geo> {13}{EC}*badump, badump* 
<Game> *boom* *bzzt... bzzt!* 
<Geo> W-What's going on? 
<Prez> Something must be wrong! 
<Woody> What the heck? The controls aren't working! 
Magnes!? Magnes, respond! 
<Spade-Magnes> Raaaaaarrrrrrrr! 
<Woody> M-Magnes!? What's wrong!? What happened to you!? 
<Spade-Magnes> Uwaaaa! I'm invincible! Invincible!!! 
<Woody> What the... 
<Jack.Flask> Woody! 
<Angel.Wise> The energy output won't stop increasing! 
<Woody> W-What!? 
<Geo-2> What does that mean? 
<Woody> It's going to explode! 
<Game> Run! 
Everyone, run! 
,Ahhh! It's pulling me in! 
*It's too powerful! I can't get away! 
<Woody> Magnes' magnetic force is out of control! 
It's using the metallic items they have on them to pull them in! 
<Bud> Forget about that! What do we do if it explodes!? 
<Woody> If the Giga Energy Card's energy suddenly fires out... It's too terrible to say...! 
<Pedia> Zack! 
<Pedia> The magnetic force is still rapidly rising due to the Wizard being out of control! 
<Woody> Magnes is out of control...? 
<Zack> What are the damage estimates!? 
<Pedia> If the rocket explodes, Echo Ridge Elementary will be completely destroyed! 
<Geo-2> {13}{EC}!! 
<Pedia> There will be considerable damage to <Echo.Ridge>, too! 
<Bud> That can't happen... 
<Woody> Why... 
Why is this happening!? 
<Geo-2> This is just like what happened at <Spica.Mall>... 
<Mega> That's true. So, kid, then that means... 
<Geo-2> Yeah, let's stop it! 
<Prez> You can't turn into Mega Man and try to stop it! 
It might explode! It's too dangerous! 
<Geo> But, we're the only ones that can do it. 
And I can't stand around and watch the school be destroyed. 
<Zack> Geo... 
<Bud> Geo... 
<Prez> You're always like this... 
...Fine. 
If you're going, then I'm not leaving until you come back. 
<Geo-2> W-What are you saying!? 
<Prez> Our Team shares the same Purpose, right? And I'm the leader! 
I wouldn't dare leave a teammate behind! 
<Geo-2> Prez... 
<Bud> I'm gonna wait, too! 
<Zack> Same here! 
<Geo-2> Bud! Zack! 
<Prez> Get going, Geo... 
"Luna 4 Prez" won't move an inch until you get back. 
<Woody> Umm... 
I didn't really hear the whole conversation, but I'm staying, too! 
<Woody> After all, we're responsible for the rocket! 
<Mega> Heh heh... None of this talk matters unless we stop the rocket! 
<Geo-2> Right! Let's rock, Mega! 
