<Game> *rumble, rumble* 
<Jack.Flask> Energy levels are nominal! Woody! 
<Angel.Wise> All systems are green! Woody! 
<Woody> At long last... launch time! 
<Magnes> Yup! Woody! Everyone! 
I'm off to space! 
<Woody> Be safe, Magnes! 
Make sure you contact us once you've made it! 
<Magnes> Yuuuup! 
<Woody> We did it! We did it! It's a complete success! 
<Jack.Flask> I'm so happy, Woody! 
<Angel.Wise> This is so great, Woody! 
<Bud> Wow! I can feel the power! 
<Zack> It's really amazing! 
<Prez> What a great memory to share with everyone! 
<Geo> It's like a dream! 
<Geo> Outer space... 
<Geo> Hey, Mega... You know how Dad is still alive up there in space? 
<Mega> Yeah, of course. 
<Geo> I was just thinking... Maybe Magnes will bump into him up there. 
<Mega> Anything is possible... I hope he has good news for us in his report. 
<Game> Purpose fulfilled! 
<Ace> EM Wave Change ID003... 
Transcode "Mega Man"... 
Just as I expected, it was Mega Man. 
His power is vital to stopping the disaster that will strike the Earth... 
<Acid> You were reckless. 
If Mega Man would have failed just now, we would 
have been swallowed up in the explosion. 
<Ace> Hmph... I believed in him 100%. 
<Ace> So a large quantity of Noise was created from 
the Wizard going out of control... 
<Acid> And it looks like some of the Noise that crystallized was taken by someone... 
Maybe it was "them"... 
<Ace> It's up to us to figure that out. 
<Acid> Of course... 
<Ace> We've got to get our heads in the game... 
But for now, let's have a snack in celebration of the successful rocket launch! 
<Game> *munch, munch* 
<Acid> You don't suppose you're eating too many of those, do you, Ace? 
