<Game> Wow! The rocket took off! 
What a success! 
<Jack> Argh! We failed! 
Everything was going according to plan... What went wrong!? 
<(Queen)Tia> {13}{EC}... 
Maybe a pest got through our traps... 
I really wanted to see that school go up in smoke... 
What a waste... 
<Jack> But, Sis... 
At least our test using the Noise Card to make 
the Wizard go out of control was a success. 
And we got the stuff that we wanted. 
<(Queen)Tia> That's right... We did pretty well... 
Let's perform an even bigger test next time. 
<Jack> Yeah! Let's make Electopia a total mess! 
<Game> *beep, beep* 
<(Queen)Tia> It's the phone... 
<Jack> I figured we'd be getting a call sooner or later. 
<Jack> Ha... 
It'll probably be something boring again. 
<(Queen)Tia> This is Queen Tia, Mr. King. 
<Mr.King> I have discovered that one of our targets, Mega Man, 
is at Echo Ridge Elementary. 
<(Queen)Tia> Mega Man... 
<Jack> Mega Man is there... 
<(Queen)Tia> So that means Mega Man is the one who stopped the rocket from exploding? 
<Mr.King> That is correct. 
The both of you, listen very carefully. 
You are to infiltrate the school and investigate Mega Man. 
You will find the secret of his power, as well as his weaknesses. 
<Jack> Instead of doing all that boring stuff, why don't we just take him out? 
He's our enemy after all, isn't he? 
<Mr.King> I am not considering taking him down at the moment. 
Mega Man will prove to be quite the interesting test subject for me. 
As a scientist, I am interested in learning more about him. 
<Jack> Ha! I thought I'd get the chance to have some fun for once! 
<(Queen)Tia> Cool it, Jack... 
<(Queen)Tia> Understood, Mr. King. We live to serve you. 
<Mr.King> I am sending some data. Read it over thoroughly. 
I will only repeat myself one more time. I will not accept failures of any kind. 
It is your duty to act as my arms and legs. 
<(Queen)Tia> Understood... 
<Game> *beep* 
<Jack> I can't stand small time stuff like investigating and researching! 
<Jack> Hey, Sis! 
Why don't we take out Mega Man without telling Mr. King!? 
<(Queen)Tia> We can't go against his orders, Jack. 
<Jack> For cryin' out loud! 
<Game> *beep* 
<Jack> What is it now!? 
<(Queen)Tia> Cool it, Jack... 
It's the data from Mr. King... 
<(Queen)Tia> Echo Ridge Elementary... Class 5-A... Geo Stelar... 
<Jack> Geo... Stelar... 
<Jack> He's{16}{E1}.{16}{E1}.{16}{E1}.{16}{E1} Mega Man. 
